### 2015-03-24 contents/implementation.tex
Init

\section{Deformable Model without Landmarks}

\begin{figure}[h!]
    \centering
        \includegraphics[width=0.5\textwidth]{resources/architecture}
    \caption{Training Architecture}
    \label{fig:archi}
\end{figure}

Deformable models is wildly used for object detection, localization, recognition and tracking while training a deformable model with good generalisation requires tremendous amount of carefully annotated data, which is extremely time consuming. Even more, annotated data normally requires same numbers of landmarks for one object category in every training data that exacerbated the cost of manual annotation.

In addition, in contrast with sparse landmarks, dense shape reveals more nuanced structure. However, there is, to the best of our knowledge, no available densely annotated data set.

Our research proposed an architecture of accepting various annotations and structuring deformable model without using landmarks. Moreover, we proposed a new method of annotating data which is drawing. The architecture contains two major modules. The first modules handles inconsistent annotation set by converting to landmark independent shape discriminator. While the other module produces shape flow on object discriminators to generate dense flow transformations in shape space following by robust PCA\cite{?} to generate deformable model. In this section, we present the entire architectures, design decision and algorithms.

\subsection{Sparse Landmarks Pre-Processing}
The first module is to bridge the gap that training data has to have consistent number of landmarks. Currently existing annotated databases contains large variety on landmarking, which largely restricted model training to stick to one data set also make evaluation challenging on using distinct data set. We proposed an algorithm that utilizes a combination of Iterative Closest Point and Support Vector Shape for pre-processing before building the model.

\subsubsection{Model Invariance}
The model built should only captures deformations that specific to the object, transformations thus rotation, translation and scaling are processed to be invariant to the model\cite{?}. ICP is applied to align sparse landmarks. ICP is a perfect choice to align various point clouds with no restriction on shape dimension or quantity.

\subsubsection{Landmark Inconsistency}
Ordinarily, construction of deformable model requires training data set having consistent number of landmarks. But unavoidable changes has to be made before applying same algorithm on diverse annotated data set.

We proposed a method based on Support Vector Shape (SVS)\cite{?}, which is a decision function trained on shapes using v-SVM with RBF kernel. There are several advantages of representing shapes as classifier: general enough to apply on 2D or 3D data, depending on only sparse points and robust against noise, missing data and artifacts.

Assuming input training images are all differently annotated of same object category. Initially, negative points get randomly sampled around sparse landmarks while annotated landmarks are positive points. Since the number of positive points are far less that the that of negative samples, landmarks are assigned considerably larger weight that $N_p \times W_p=N_n \times W_n$ where $N_p, N_n$ are number of positive/negative points and $W_p, W_n$ are weights of positive/negative samples.

SVM with RBF kernel function maps any numbers of data points onto an infinite-dimensional space where positive and negative points are linearly separable, hence classification boundary on 2D space represents the actual shape. The decision function for SVM shown below:
\begin{equation} \label{eq:decisionfunc}
    d(x)=\sum_i\alpha k(x_i^*,x)
\end{equation}
where $x_i^*$ are support vectors and $k(x_i^*,x)$ are Gaussian Radial Basis Function kernel $k(x_i^*,x)=exp(-\lambda \|x_i^*,x\|^2)$.

Figure~\ref{fig:build_svs} demonstrate trained shape descriptor using SVM and the final result is irrelevant to landmark amount. Figure~\ref{svs} displays the visualization of the decision function where brighter colour means corresponding pixels belongs to original shape with higher possibility. It is a very generalized shape discriminator that blends inconsistent landmark annotations into decision functions.

\begin{figure}[h!]
    \centering
    \begin{subfigure}[b]{0.15\textwidth}
            \includegraphics[width=\textwidth]{resources/landmark}
        \caption{Spare landmarks}
    \end{subfigure}
    ~~~~~~~~~
    \begin{subfigure}[b]{0.15\textwidth}
            \includegraphics[width=\textwidth]{resources/svs}
        \caption{Visualise decision function trained}
        \label{fig:svs}
    \end{subfigure}
    \caption{Decision function trained on sparse landmarks}
    \label{fig:build_svs}
\end{figure}

% ---------------------------------------------------------------------------------------------------------------------------------------------------

\subsection{Shape Flow}

With decision functions built from training data, the second module designed to register all decision functions to mean shape, we named it Shape Flow. Shape Flow is introduced based on optical flow, which generate pixel-wise correspondences for video sequences. Optical flow works for video sequences based on assumptions e.g. brightness constancy and motion smoothness. However, in terms of shapes, neither constant illumination nor continuous motion exists in sequence of shapes as all training data are independent. Thus we proposed shape flow with subspace constrains introduced from trajectories.

\subsubsection{Trajectory Basis} \label{sec:trabasis}
Since shapes from training data set having completely no motion smoothness, it is of importance to contain constrains in optimization on how pixels moves from one shape frame to another. We constrain the optimization on trajectory subspace.
We supervise trajectories from sparse landmarks. To begin with, Non-rigid Iterative Closest Point (NICP)\cite{?} applied on sparse annotated points. NICP deforms target points to fit the template iteratively until all points on target deformed to match points on template. Performs the algorithm for all training data will get an implicit point correlation between sparse shapes.

Since optical flow pixel-wise frame registration, the trajectory basis build should also matches the dimension, which is dense on shapes with trajectory length depends on number of training data. With correspondences produced after applying NICP, Thin-Plate Spline (TPS)\cite{?} transformations are utilized to warp every shape planes to template plane thereby generates an implicit dense shape registering. For all dense transformations $\bm{u_n}(\bm{x}), n \in {1,...,F}$, where $F$ is number of data and $\bm{x}$ is vector of pixels, Principle Component Analysis (PCA) is performed on trajectory to obtain low rank trajectory basis:
\begin{equation}
    \begin{bmatrix}
        \bm{u_1}(\bm{x}) \\
        \vdots \\
        \bm{u_F}(\bm{x})
    \end{bmatrix}
    =
    \begin{bmatrix}
        \bm{q_1}(1) & \cdots & \bm{q_R}(1) \\
        \vdots      & \ddots & \vdots  \\
        \bm{q_1}(F) & \cdots & \bm{q_R}(F)
    \end{bmatrix}
    \times
    \begin{bmatrix}
        \bm{v_1}(x) \\
        \vdots \\
        \bm{v_R}(x)
    \end{bmatrix}
\end{equation}
where $\bm{q_i}(n)$ are low rank components with $R \ll 2F$ and $\bm{v_i}(x)$ weighted each component with dependencies on $x$. Simpler expression shown below:
\begin{equation}
    \bm{u_n}(\bm{x})=\sum_{i=1}^R\bm{q_i}(n)\bm{v_i}(x)+\bm{\varepsilon_n}(\bm{x})
\end{equation}
Although optical flow on shapes made under the assumption that objects motion are smooth, the low rank constrain on trajectory basis recovered the hypothesis.

\subsubsection{Algorithm}
To register all decision functions to template shape, decision function $d_i(\bm{x}), i \in {1,...,F}$ are grouped into one sequence before applying flow algorithm. The objective cost function we would like to minimise is:
\begin{align}
    E[\bm{u_n}(\bm{x}), \bm{v}]&=\alpha \int_{\Omega}\sum_{n=1}^F|\bm{d_n}(x+\bm{u_n}(x))-\bm{d_0}(x)\| dx  \label{eq:costfunc}\\
    &+ \beta \int_{\Omega}\sum_{n=1}^F\|\bm{u_n}(x)-\sum_{i=1}^R\bm{q_i}(n)\bm{v_i}(x)\|^2 dx \label{eq:lowrank}\\
    &+ \sum[\bm{TV}(Qv)]  + v^T.L.v
\end{align}
where $d_n(x)$ is the decision function from~\eqref{eq:decisionfunc}, which returns possibilities of given coordinate classified as shape compunent. $TV(Qv)$ is total variation as regularization on low rank subspace, $Q$ is trajectory basis and $v^T.L.v$ is low rank spacial constrains.

Term~\eqref{eq:costfunc} state the shape constancy where points having similar classification probability are from same object.
Part~\eqref{eq:lowrank} applies constrain on low rank trajectory basis states in section~\ref{sec:trabasis}.
The objective cost function has two free parameters $u$ and $v$, so we performs alternating minimisation. The equation can be solved using thresholding scheme as used in \cite{?} after linearisation of image functions. The minimisation can be speed up by paralleling the minimisation for every spatial-temporal point $(x;n), x \in \Omega, n \in {1,...F}$ independently.

After solving the equation, $\bm{u_n}(\bm{x}), x \in \Omega$ gives a group of dense deformations that registering every decision functions in the shape sequence to reference frame e.g. $\bm{u_1}(\bm{x})$ registers decision function $\bm{d_1}(\bm{x})$ to the reference frame. Applying PCA on deformations gives dense deformable shape model.

\subsubsection{Computational Complexity?}

\clearpage

### 2015-03-24 contents/introduction.tex
Init

Uses Introductions from Nondas' paper "Automatic Construction of Deformable Models In-The-Wild" as place holder

Many deformable objects exist everywhere around us.
Some examples are the human face and body, animals, vehicles
such as cars and motorcycles and objects of everyday
use like tables, chairs etc. Most of these objects consist of
different parts and appear in instances with great variance
in shape and appearance. Thus, the concept of a deformable
object refers to the deformation of both shape and appearance
of an object. For example cars have parts (i.e. doors,
windows, tires etc.) with significant changes in shape, size
and texture. Furthermore, faces consist of parts (i.e. nose,
eyes, mouth etc.) which not only vary with respect to shape
and appearance, but can demonstrate a number of expressions
due to muscles. Recently, we have witnessed a great
progress in object detection, alignment and recognition.
In order to train deformable models with good generalization
ability, a large amount of carefully annotated data
is needed. Developing useful datasets and benchmarks that
can contribute in the progress of an application domain is
a highly time consuming and costly procedure. It requires
both careful selection of the images, so that they can model
the vast amount of an object’s variability, and careful annotation
of the various parts of the object (or landmarks).
The amount of annotation that is required depends on both
the object and the application. In faces, for example, where
many landmark points are needed in tasks such as facial expression
analysis, motion capture and expression transfer,
usually more than 60 points are annotated \cite{?}.
To illustrate how much time consuming careful face annotation
is, according to our experience, a trained annotator
may need an average of 8 minutes per image for the manual
annotation of 68 landmarks1. This means that the annotation
of 1000 images requires a total of about 130 hours2.
Furthermore, fatigue can cause errors on the accuracy and
consistency of annotations and they may require correction.
In this paper, we deal with the problem of automatically
constructing a robust deformable model using (1) a simple
bounding box object detector and (2) a shape by means of
a Point Distribution Model (PDM). The detector can be as
simple as the Viola-Jones object detector \cite{?}
3 which returns
only a bounding box of a detected object. Such detectors
are widely employed in commercial products (e.g.
even the cheapest digital camera has a robust face detector).
Other detectors that can be used are efficient subwindow
search \cite{?}. The
annotations that are needed to train the object detector can
be acquired very quickly, since only a bounding box containing the object is required. Specifically, after selecting
the images that are going to be used, the annotation procedure
takes a couple of seconds per image. The statistical
shape model can be created by using only 40-50 shape examples,
which can be produced by either drawing possible
shape variations of the 2D shape of the object or projecting
3D CAD model instances of the object on the 2D camera
plane (such an example is shown in \cite{?} for cars). Even
the annotation of the shape examples is not a time consuming
task, due to their small number. Furthermore, there are
unsupervised techniques to learn the shape prior (model) directly
from images \cite{?}.
Due to the fact that manual annotation is a rather costly
and labour-intensive procedure, unsupervised and semisupervised
learning of models for the tasks of alignment,
landmark localization, tracking and recognition has attracted
considerable attention \cite{?}. In this paper, we
propose a method to automatically construct deformable
models for object alignment and the most related works
are \cite{?}. The related family of techniques,
known as image-congealing \cite{?}, uses implicit
models to align a set of images as a whole, which means
that both performing alignment to a new image and constructing
a model is not straightforward. Our methodology
differs from these works because we employ an explicit texture
model which is learned through the process.
The two most closely related works to the proposed
method are the automatic construction of Active Appearance
Models (AAMs) in \cite{?} and the so-called RASL
methodology in \cite{?} for person-specific face alignment.
There are two main differences between our framework
and \cite{?}. (1) We use a predefined statistical shape model
instead of trying to find both the shape and appearance models.
We believe that with the current available optimization
techniques, it is extremely difficult to simultaneously optimize
for both the texture and shape parameters. (2) We
employ the robust component analysis of \cite{?} for the appearance
which deals with outliers. Thus, even though
our method is similar in concept to \cite{?}, these two differences
make the problem feasible to solve. In particular, the
methodology in \cite{?} fails to create a generic model even in
controlled recording conditions, due to extremely high dimensionality
of the parameters to be found and to the sensitivity
of the subspace method to outliers. This was probably
one of the reasons why the authors demonstrate very
limited and only person-specific experiments. Furthermore,
our methodology bypasses some of the limitations of \cite{?},
which requires the presence of only one low-rank subspace,
hence it has been shown to work only for the case of congealing
images of a single person. Finally, we argue that
in order for an automatically constructed AAM methodology
to be robust to both within-class and out-of-class outliers4,
which cannot be avoided in totally unsupervised settings,
statistical component analysis techniques should be
employed \cite{?}.

\clearpage

### 2015-03-24 contents/title.tex
Init

\title{Shape Flow - Deformable Model without Landmarks}

\author{Yuxiang Zhou, Joan Alabort-i-Medina, Anastasios Roussos, Stefanos Zafeiriou\\
Imperial College London\\
180 Queen’s Gate, SW7 2AZ, London, U.K.\\
{\tt\small \{yuxiang.zhou10, ja310, troussos, s.zafeiriou\}@imperial.ac.uk}}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both

### 2015-03-24 contents/implementation.tex
Init

@@
 
-After solving the equation, $\bm{u_n}(\bm{x}), x \in \Omega$ gives a group of dense deformations that registering every decision functions in the shape sequence to reference frame e.g.
+After solving the equation, $\bm{u_n}(\bm{x}), x \in \Omega$ gives a group of deformation fields that registering every decision functions in the shape sequence to reference frame e.g.
 $\bm{u_1}(\bm{x})$ registers decision function $\bm{d_1}(\bm{x})$ to the reference frame.
-Applying PCA on deformations gives dense deformable shape model.
+Applying PCA on deformations gives dense deformable shape model:
+\begin{equation*}
+    \bm{s_p}=\bm{\bar{s}} + \bm{U}_s\bm{p}
+\end{equation*}
+
+\begin{figure}[h!]
+    \centering
+        \includegraphics[width=0.5\textwidth]{resources/df}
+    \caption{Deformation field built}
+    \label{fig:deformationfield}
+\end{figure}
+
+\begin{figure}[h!]
+    \centering
+        \includegraphics[width=0.5\textwidth]{resources/models}
+    \caption{Dense Deformable Model}
+    \label{fig:models}
+\end{figure}
 

### 2015-03-24 contents/evaluation.tex
Algorithms

To evaluate the quality of model,

\subsection{Using Sparse Point Annotation}

\subsection{Using Drawing Annotation}

\clearpage

### 2015-03-24 contents/implementation.tex
Algorithms

@@
 With correspondences produced after applying NICP, Thin-Plate Spline (TPS)\cite{?} transformations are utilized to warp every shape planes to template plane thereby generates an implicit dense shape registering.
-For all dense transformations $\bm{u_n}(\bm{x}), n \in {1,...,F}$, where $F$ is number of data and $\bm{x}$ is vector of pixels, Principle Component Analysis (PCA) is performed on trajectory to obtain low rank trajectory basis:
+For all dense transformations $\bm{u_n}(\bm{x}), n \in \{1,...,F\}$, where $F$ is number of data and $\bm{x}$ is vector of pixels, Principle Component Analysis (PCA) is performed on trajectory to obtain low rank trajectory basis:
 \begin{equation}
@@
 \begin{align}
-    E[\bm{u_n}(\bm{x}), \bm{v}]&=\alpha \int_{\Omega}\sum_{n=1}^F|\bm{d_n}(x+\bm{u_n}(x))-\bm{d_0}(x)\| dx  \label{eq:costfunc}\\
+    \operatorname*{arg\,min}_{\bm{u_n}(\bm{x}), \bm{v}}&=\alpha \int_{\Omega}\sum_{n=1}^F|\bm{d_n}(x+\bm{u_n}(x))-\bm{d_0}(x)\| dx  \label{eq:costfunc}\\
     &+ \beta \int_{\Omega}\sum_{n=1}^F\|\bm{u_n}(x)-\sum_{i=1}^R\bm{q_i}(n)\bm{v_i}(x)\|^2 dx \label{eq:lowrank}\\
@@
 \end{align}
-where $d_n(x)$ is the decision function from~\eqref{eq:decisionfunc}, which returns possibilities of given coordinate classified as shape compunent.
+where $d_n(x)$ is the decision function from~\eqref{eq:decisionfunc}, which returns possibilities of given coordinate classified as shape component where coordianates are from set $\Omega \in \Re^2$.
 $TV(Qv)$ is total variation as regularization on low rank subspace, $Q$ is trajectory basis and $v^T.L.v$ is low rank spacial constrains.
@@
 The equation can be solved using thresholding scheme as used in \cite{?} after linearisation of image functions.
-The minimisation can be speed up by paralleling the minimisation for every spatial-temporal point $(x;n), x \in \Omega, n \in {1,...F}$ independently.
+The minimisation can be speed up by paralleling the minimisation for every spatial-temporal point $(x;n), x \in \Omega, n \in \{1,...F\}$ independently.
 
@@
 $\bm{u_1}(\bm{x})$ registers decision function $\bm{d_1}(\bm{x})$ to the reference frame.
-Applying PCA on deformations gives dense deformable shape model:
-\begin{equation*}
-    \bm{s_p}=\bm{\bar{s}} + \bm{U}_s\bm{p}
-\end{equation*}
+Figure~\ref{fig:deformationfield} demonstrates deformation fields that warps from reference frame where there is no deformation.
 
@@
 
+Applying PCA on deformations trains dense deformable shape model:
+\begin{equation*}
+    \bm{s_p}=\bm{\bar{s}} + \bm{U}_s\bm{p}
+\end{equation*}
+where $\bm{s_p}$ is deformed shape instance.
+$\bm{\bar{s}}$ is mean shape and $\bm{U}_s\bm{p}$ are eigenvectors with corresponding parameters $p$.
+Figure~\ref{fig:models} shows an instance of deformed shape and appearance model.
 \begin{figure}[h!]
     \centering
-        \includegraphics[width=0.5\textwidth]{resources/models}
+        \includegraphics[width=0.4\textwidth]{resources/models}
     \caption{Dense Deformable Model}
@@
 
-\subsubsection{Computational Complexity?}
+\subsubsection{Drawing Annotation}
+
+The purpose of the shape descriptor $\bm{d_i}(x)$ generates probabilities for arbitrary points.
+If we sample points that are exactly pixel-wise integers, and normalise classification value, we can visualise a SVS as an image for example in figure~\ref{fig:svs}.
+In other words, our architecture will also works for images with landmarks similar to SVS visualisations like drawing.
+Assuming the intensity of a gray-scale image simulate the decision function, named $\bm{I_i}(x), x \in \Omega, i \in \{1,...F\}$.
+But in this situation, pixels at image space are discontinued, so $x$ is constrained to be integer and within the view window of size $N\times M$.
 

### 2015-03-24 contents/introduction.tex
Algorithms

@@
 progress in object detection, alignment and recognition.
+
 In order to train deformable models with good generalization
@@
 consistency of annotations and they may require correction.
+
 In this paper, we deal with the problem of automatically
@@
 from images \cite{?}.
+
 Due to the fact that manual annotation is a rather costly
@@
 model which is learned through the process.
+
 The two most closely related works to the proposed
@@
 statistical component analysis techniques should be
-employed \cite{?}.
+employed \cite{?}. We summarize our contributions as follows:
+
+We present experimental results on the task of face alignment.
+We choose this application because there exist many
+in-the-wild facial databases with a large number of images
+and annotated landmarks, hence solid quantitative evaluations
+can be performed.
 

### 2015-03-25 contents/implementation.tex
changes to beginning part of implementation

@@
 
-Deformable models is wildly used for object detection, localization, recognition and tracking while training a deformable model with good generalisation requires tremendous amount of carefully annotated data, which is extremely time consuming.
-Even more, annotated data normally requires same numbers of landmarks for one object category in every training data that exacerbated the cost of manual annotation.
+Deformable models are widely used for object detection, localization, recognition and tracking while training a deformable model with good generalisation requires tremendous amount of carefully annotated data, which is extremely time consuming.
+Even more, annotated data of a specific object category typically requires same numbers of landmarks for every training sample, making the annotation procedure significantly complex where corrext menual annotation of landmarks is impossible in various object classes e.g.
+ears.
 
-In addition, in contrast with sparse landmarks, dense shape reveals more nuanced structure. However, there is, to the best of our knowledge, no available densely annotated data set.
+Despite the fact that that vast majority of existing methods are based on a sparse shape representation, dense shape representation reveals more nuanced structure in terms of [todo: explain].
 
-Our research proposed an architecture of accepting various annotations and structuring deformable model without using landmarks.
-Moreover, we proposed a new method of annotating data which is drawing.
-The architecture contains two major modules.
-The first modules handles inconsistent annotation set by converting to landmark independent shape discriminator.
+We propose a novel framework for building deformable models that does not require any consistent set of annotated landmarks and is based on dense shape representation.
+Our method only requires a set of point or curve annotation that does not need to be consistent over different training samples.
+
+It combines NICP, SVS representation and multi-image subspace flow in an effective framework that has significant descriptive power.
+The pipeline contains two major modules.
+The first module handles inconsistent annotation set by converting to landmark independent shape discriminator.
 While the other module produces shape flow on object discriminators to generate dense flow transformations in shape space following by robust PCA\cite{?} to generate deformable model.
@@
 Currently existing annotated databases contains large variety on landmarking, which largely restricted model training to stick to one data set also make evaluation challenging on using distinct data set.
-We proposed an algorithm that utilizes a combination of Iterative Closest Point and Support Vector Shape for pre-processing before building the model.
+We propose an algorithm that utilizes a combination of Iterative Closest Point and Support Vector Shape for pre-processing before building the model.
 

### 2015-03-27 contents/implementation.tex
changes in pipeline description

@@
 Our method only requires a set of point or curve annotation that does not need to be consistent over different training samples.
+It combines NICP, SVS representation and multi-image subspace flow in an effective framework that has significant descriptive power.
 
-It combines NICP, SVS representation and multi-image subspace flow in an effective framework that has significant descriptive power.
-The pipeline contains two major modules.
+The proposed pipeline is depicted in Figure ....
+It takes as input a set of training images of an object class, along with point and/or curve annotations.
+Its first step is the application of ICP to achieve an initial alignment of the training images.
+Next, the shapes that correspond to the training data are consistently represented using multichannel SVS.
+These are then fed into a multi-image subspace flow estimation that establishes dense correspondences between all shapes of the training set.
+In order for the flow estimation to be accurate and exploit the correlation across the different training shapes, it utilises a correspondence basis that is built on sparse correspondences given by Nonrigid ICP alignment of the annotated data.
+Finally, the dense correspondences that are yielded by the optical flow serve as automatic dense landmarks and are used by a dense AAM training and fitting procedure.
+The following sections discuss in more detail the steps of the proposed pipeline.
+
+%two major modules.
 The first module handles inconsistent annotation set by converting to landmark independent shape discriminator.
@@
 
-\subsection{Sparse Landmarks Pre-Processing}
+\subsection{Shape Representation Without Consistent Annotations}
 The first module is to bridge the gap that training data has to have consistent number of landmarks.
@@
 
-\subsubsection{Model Invariance}
+\subsubsection{Initial Alignment of the Training Images}
+
 The model built should only captures deformations that specific to the object, transformations thus rotation, translation and scaling are processed to be invariant to the model\cite{?}.
@@
 
-\subsubsection{Landmark Inconsistency}
+\subsubsection{Multichannel Support Vector Shape Representation}
 Ordinarily, construction of deformable model requires training data set having consistent number of landmarks.
@@
 
-\subsubsection{Trajectory Basis} \label{sec:trabasis}
+\subsubsection{Non-rigid ICP and Correspondence Basis Creation} \label{sec:trabasis}
 Since shapes from training data set having completely no motion smoothness, it is of importance to contain constrains in optimization on how pixels moves from one shape frame to another.
-We constrain the optimization on trajectory subspace.
+We constrain the optimization on correspondence subspace.
 We supervise trajectories from sparse landmarks.
@@
 
-\subsubsection{Algorithm}
+\subsubsection{Multi-image Subspace Flow}
 To register all decision functions to template shape, decision function $d_i(\bm{x}), i \in {1,...,F}$ are grouped into one sequence before applying flow algorithm.

### 2015-04-10 contents/evaluation.tex
Update Abstract & Evalutation Structure
added figures for evaluation section

@@
-To evaluate the quality of model,
+We perform evaluation of dense deformable model
+\subsection{Models Qualitative Analysis}
 
-\subsection{Using Sparse Point Annotation}
+\subsubsection{Model Compactness}
 
-\subsection{Using Drawing Annotation}
+\begin{figure}[h!]
+    \centering
+    \begin{subfigure}[b]{0.2\textwidth}
+            \includegraphics[width=\textwidth]{resources/aam_ear_eigen_value}
+        \caption{AAM Principle Components Contribution}
+        \label{}
+    \end{subfigure}
+    ~~
+    \begin{subfigure}[b]{0.2\textwidth}
+            \includegraphics[width=\textwidth]{resources/of_ear_eigen_value}
+        \caption{Shape Flow Principle Components Contribution}
+    \end{subfigure}
+    \caption{Principle Components Contribution}
+\end{figure}
+
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=0.1\textwidth]{resources/landmark_drifting}
+    \caption{Landmark Drifting}
+\end{figure}
+
+\subsubsection{Shape Reconstruction}
+
+\begin{figure}[h!]
+    \centering
+    \begin{subfigure}[b]{0.2\textwidth}
+            \includegraphics[width=\textwidth]{resources/warp_reconstruction_error}
+        \caption{Warp Reconstruction Errors}
+        \label{}
+    \end{subfigure}
+    ~~
+    \begin{subfigure}[b]{0.2\textwidth}
+            \includegraphics[width=\textwidth]{resources/sparse_reconstruction_error}
+        \caption{Spare Reconstruction Errors}
+    \end{subfigure}
+    \caption{Reconstruction Errors}
+\end{figure}
+
+\begin{figure}[h!]
+    \centering
+    \begin{subfigure}[b]{0.2\textwidth}
+            \includegraphics[width=\textwidth]{resources/warp_projecting_error_aam}
+        \caption{AAM Warp Projecting Errors}
+        \label{}
+    \end{subfigure}
+    ~~
+    \begin{subfigure}[b]{0.2\textwidth}
+            \includegraphics[width=\textwidth]{resources/warp_projecting_error_of}
+        \caption{Shape Flow Warp Projecting Errors}
+    \end{subfigure}
+    \caption{Projecting Errors}
+\end{figure}
+
+\subsection{Evaluation on Fitting}
+
+\subsubsection{Using Sparse Point Annotation}
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=0.4\textwidth]{resources/face_digo_mc}
+    \caption{CED Fitting Results on Face}
+\end{figure}
+
+\subsubsection{Using Drawing Annotation}
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=0.4\textwidth]{resources/ear_digo_mc}
+    \caption{CED Fitting Results on Ear}
+\end{figure}
 

### 2015-04-15 contents/introduction.tex
Update Abstract & Evalutation Structure
Introduction edited

@@
-Uses Introductions from Nondas' paper "Automatic Construction of Deformable Models In-The-Wild" as place holder
-
-Many deformable objects exist everywhere around us.
-Some examples are the human face and body, animals, vehicles
-such as cars and motorcycles and objects of everyday
-use like tables, chairs etc. Most of these objects consist of
-different parts and appear in instances with great variance
-in shape and appearance. Thus, the concept of a deformable
-object refers to the deformation of both shape and appearance
-of an object. For example cars have parts (i.e. doors,
-windows, tires etc.) with significant changes in shape, size
-and texture. Furthermore, faces consist of parts (i.e. nose,
-eyes, mouth etc.) which not only vary with respect to shape
-and appearance, but can demonstrate a number of expressions
-due to muscles. Recently, we have witnessed a great
+Building and training deformable models of objects (e.g.
+faces, ears, bodies, bottles, vehicles etc.) has recently been widely researched for object detection, part localisation, fitting, recognition and tracking using manual annotated data.
+Shapes and appearances of majority of objects vary significantly from object instance.
+To illustrate, ears have complicated inner structures (e.g.
+helix, crus antihelicis, scapha, tragus, lobe etc.) which differs remarkably between ears and highly sensitive to intensity changes.
+Recently, we have witnessed a great
 progress in object detection, alignment and recognition.
 
-In order to train deformable models with good generalization
-ability, a large amount of carefully annotated data
-is needed. Developing useful datasets and benchmarks that
-can contribute in the progress of an application domain is
-a highly time consuming and costly procedure. It requires
-both careful selection of the images, so that they can model
-the vast amount of an object’s variability, and careful annotation
-of the various parts of the object (or landmarks).
-The amount of annotation that is required depends on both
-the object and the application. In faces, for example, where
-many landmark points are needed in tasks such as facial expression
-analysis, motion capture and expression transfer,
-usually more than 60 points are annotated \cite{?}.
-To illustrate how much time consuming careful face annotation
-is, according to our experience, a trained annotator
-may need an average of 8 minutes per image for the manual
-annotation of 68 landmarks1. This means that the annotation
-of 1000 images requires a total of about 130 hours2.
-Furthermore, fatigue can cause errors on the accuracy and
-consistency of annotations and they may require correction.
+To train deformable models with satisfiable generalisation, large amount of careful manual annotation is required.
+However, landmark annotation is extremely time consuming, work intensive and, most importantly, number of landmarks have to stay consistent for all training data while it is challenging to maintain the consistency or to avoid bias when annotating objects that having reach features.
+In ears, for example, large amount of landmarks required as the inner structure of ears are complex.
+To annotate an ear with clear contour, helix and cavum conchae, more than 50 landmarks are required.
+The inconsistency of ear features enhanced the difficulty of accurate annotation (e.g.
+Fossa Triangularies and Crus Helicis are optional feature of an ear also their visibility is highly sensitive to pose and illumination variation).
+To illustrate how much time consuming careful ear annotation is, according to our experience, a trained annotator may need an average of (TODO: experiment) minutes per image for the manual annotation of 55 landmarks.
+This means that the annotation of 1000 images requires a total of about (TODO: experiment).
+Furthermore, personal issue, prior knowledge and circumstances can heavily bias the annotation accuracy thus second round correction might desired.
+
+We propose framework to handle training data with inconsistent annotation, build dense shape model and introduce effective curve annotation methods.
+In our experiment, we show building dense models trained with inconsistent annotation and trained with curve annotation improves performance of discriminative models trained on carefully annotated data.
+
+Uses Introductions from Nondas' paper "Automatic Construction of Deformable Models In-The-Wild" as place holder.
 

### 2015-04-16 contents/introduction.tex
Edited Intro

@@
 helix, crus antihelicis, scapha, tragus, lobe etc.) which differs remarkably between ears and highly sensitive to intensity changes.
-Recently, we have witnessed a great
-progress in object detection, alignment and recognition.
+Recently, we have witnessed a great progress in object detection, alignment and recognition.
 
@@
 
-We propose framework to handle training data with inconsistent annotation, build dense shape model and introduce effective curve annotation methods.
-In our experiment, we show building dense models trained with inconsistent annotation and trained with curve annotation improves performance of discriminative models trained on carefully annotated data.
+We propose a framework to (1) construct SDMs using training data with inconsistent annotation, (2) introduce highly effective curve annotation which tremendously reduces manual work overload but maintains same performance level against state-of-the-art SDMs and (3) build dense correspondent SDMs with shape flow.
 
-Uses Introductions from Nondas' paper "Automatic Construction of Deformable Models In-The-Wild" as place holder.
+% Back Ground
+The two most closely related works to the proposed
+method are the automatic construction of Active Appearance
+Models (AAMs) in \cite{?} and the so-called RASL
+methodology in \cite{?} for person-specific face alignment.
+There are two main differences between our framework
+and \cite{?}. (1) We use a predefined statistical shape model
+instead of trying to find both the shape and appearance models.
+We believe that with the current available optimization
+techniques, it is extremely difficult to simultaneously optimize
+for both the texture and shape parameters. (2) We
+employ the robust component analysis of \cite{?} for the appearance
+which deals with outliers. Thus, even though
+our method is similar in concept to \cite{?}, these two differences
+make the problem feasible to solve. In particular, the
+methodology in \cite{?} fails to create a generic model even in
+controlled recording conditions, due to extremely high dimensionality
+of the parameters to be found and to the sensitivity
+of the subspace method to outliers. This was probably
+one of the reasons why the authors demonstrate very
+limited and only person-specific experiments. Furthermore,
+our methodology bypasses some of the limitations of \cite{?},
+which requires the presence of only one low-rank subspace,
+hence it has been shown to work only for the case of congealing
+images of a single person. Finally, we argue that
+in order for an automatically constructed AAM methodology
+to be robust to both within-class and out-of-class outliers4,
+which cannot be avoided in totally unsupervised setting
+statistical component analysis techniques should be
+employed \cite{?}. We summarize our contributions as follows:
 
-In this paper, we deal with the problem of automatically
-constructing a robust deformable model using (1) a simple
-bounding box object detector and (2) a shape by means of
-a Point Distribution Model (PDM). The detector can be as
+% contribution summerize
+
+In our experiment, we show that building robust dense models trained with inconsistent annotation and trained with curve annotation improves performance of discriminative models trained on carefully annotated data including ears, faces, bottles, (cars ?) and bodies.
+Evaluation methods and choices are described in details.
+
+Uses Introductions from Nondas' paper "Automatic Construction of Deformable Models In-The-Wild" as place holder below.
+
+The detector can be as
 simple as the Viola-Jones object detector \cite{?}
@@
 Other detectors that can be used are efficient subwindow
-search \cite{?}. The
+search \cite{?}.
+
+The
 annotations that are needed to train the object detector can
@@
 
-The two most closely related works to the proposed
-method are the automatic construction of Active Appearance
-Models (AAMs) in \cite{?} and the so-called RASL
-methodology in \cite{?} for person-specific face alignment.
-There are two main differences between our framework
-and \cite{?}. (1) We use a predefined statistical shape model
-instead of trying to find both the shape and appearance models.
-We believe that with the current available optimization
-techniques, it is extremely difficult to simultaneously optimize
-for both the texture and shape parameters. (2) We
-employ the robust component analysis of \cite{?} for the appearance
-which deals with outliers. Thus, even though
-our method is similar in concept to \cite{?}, these two differences
-make the problem feasible to solve. In particular, the
-methodology in \cite{?} fails to create a generic model even in
-controlled recording conditions, due to extremely high dimensionality
-of the parameters to be found and to the sensitivity
-of the subspace method to outliers. This was probably
-one of the reasons why the authors demonstrate very
-limited and only person-specific experiments. Furthermore,
-our methodology bypasses some of the limitations of \cite{?},
-which requires the presence of only one low-rank subspace,
-hence it has been shown to work only for the case of congealing
-images of a single person. Finally, we argue that
-in order for an automatically constructed AAM methodology
-to be robust to both within-class and out-of-class outliers4,
-which cannot be avoided in totally unsupervised settings,
-statistical component analysis techniques should be
-employed \cite{?}. We summarize our contributions as follows:
+% The two most closely related works to the proposed
+% method are the automatic construction of Active Appearance
+% Models (AAMs) in \cite{?} and the so-called RASL
+% methodology in \cite{?} for person-specific face alignment.
+% There are two main differences between our framework
+% and \cite{?}. (1) We use a predefined statistical shape model
+% instead of trying to find both the shape and appearance models.
+% We believe that with the current available optimization
+% techniques, it is extremely difficult to simultaneously optimize
+% for both the texture and shape parameters. (2) We
+% employ the robust component analysis of \cite{?} for the appearance
+% which deals with outliers. Thus, even though
+% our method is similar in concept to \cite{?}, these two differences
+% make the problem feasible to solve. In particular, the
+% methodology in \cite{?} fails to create a generic model even in
+% controlled recording conditions, due to extremely high dimensionality
+% of the parameters to be found and to the sensitivity
+% of the subspace method to outliers. This was probably
+% one of the reasons why the authors demonstrate very
+% limited and only person-specific experiments. Furthermore,
+% our methodology bypasses some of the limitations of \cite{?},
+% which requires the presence of only one low-rank subspace,
+% hence it has been shown to work only for the case of congealing
+% images of a single person. Finally, we argue that
+% in order for an automatically constructed AAM methodolo
+% to be robust to both within-class and out-of-class outliers4,
+% which cannot be avoided in totally unsupervised setti
+% statistical component analysis techniques should be
+% employed \cite{?}. We summarize our contributions as follows:
 
-We present experimental results on the task of face alignment.
-We choose this application because there exist many
-in-the-wild facial databases with a large number of images
-and annotated landmarks, hence solid quantitative evaluations
-can be performed.
+% We present experimental results on the task of face alignment.
+% We choose this application because there exist many
+% in-the-wild facial databases with a large number of images
+% and annotated landmarks, hence solid quantitative evaluations
+% can be performed.
 

### 2015-04-16 contents/introduction.tex
Introduction

--- 2015-04-15 contents/introduction.tex
@@
 
-We propose framework to handle training data with inconsistent annotation, build dense shape model and introduce effective curve annotation methods.
-In our experiment, we show building dense models trained with inconsistent annotation and trained with curve annotation improves performance of discriminative models trained on carefully annotated data.
+We propose a framework to (1) construct SDMs using training data with inconsistent annotation, (2) introduce highly effective curve annotation which tremendously reduces manual work overload but maintains same performance level against state-of-the-art SDMs and (3) build dense correspondent SDMs with shape flow.
 
-Uses Introductions from Nondas' paper "Automatic Construction of Deformable Models In-The-Wild" as place holder.
+%(1)
+Annotated data of same objects can have various number of landmarks, \cite{?} shown faces have landmarks different in range 10+ to 70+.
+Building SDMs (e.g.
+Active Appearance Models), however, require training data are annotated consistently, for example, all faces have 68 landmarks, 6 landmarks for an eye and 9 for a nose \cite{?}.
+Such property of SDMs largely limited their application area like combining different dataset as one.
+We propose the pipeline with non-rigid alignment and support vector shape to blend landmarks into relatively consistent shape discriminator before building models.
 
-In this paper, we deal with the problem of automatically
-constructing a robust deformable model using (1) a simple
-bounding box object detector and (2) a shape by means of
-a Point Distribution Model (PDM). The detector can be as
-simple as the Viola-Jones object detector \cite{?}
-3 which returns
-only a bounding box of a detected object. Such detectors
-are widely employed in commercial products (e.g.
-even the cheapest digital camera has a robust face detector).
-Other detectors that can be used are efficient subwindow
-search \cite{?}. The
-annotations that are needed to train the object detector can
-be acquired very quickly, since only a bounding box containing the object is required. Specifically, after selecting
-the images that are going to be used, the annotation procedure
-takes a couple of seconds per image. The statistical
-shape model can be created by using only 40-50 shape examples,
-which can be produced by either drawing possible
-shape variations of the 2D shape of the object or projecting
-3D CAD model instances of the object on the 2D camera
-plane (such an example is shown in \cite{?} for cars). Even
-the annotation of the shape examples is not a time consuming
-task, due to their small number. Furthermore, there are
-unsupervised techniques to learn the shape prior (model) directly
-from images \cite{?}.
+%(2)
+Due to the fact that manual annotation is a rather costly and labour-intensive procedure, unsupervised and semi supervised learning of models for the tasks of alignment, landmark localization, tracking and recognition has attracted considerable attention \cite{?}.
+As our proposed framework are available to handle landmarks with inconsistency, it leads to a more efficient, convenient, unbiased and simple annotation methods - curve annotation.
 
-Due to the fact that manual annotation is a rather costly
-and labour-intensive procedure, unsupervised and semisupervised
-learning of models for the tasks of alignment,
-landmark localization, tracking and recognition has attracted
-considerable attention \cite{?}. In this paper, we
-propose a method to automatically construct deformable
-models for object alignment and the most related works
-are \cite{?}. The related family of techniques,
-known as image-congealing \cite{?}, uses implicit
-models to align a set of images as a whole, which means
-that both performing alignment to a new image and constructing
-a model is not straightforward. Our methodology
-differs from these works because we employ an explicit texture
-model which is learned through the process.
+%(3)
+To build dense correspondence between independent shapes, we apply optical flow on shapes with low rank constrains, so we name it shape flow.
+Optical flow is originally applied to video sequences that several assumptions holds, illumination consistency and motion smoothness, while shapes having no motion smoothness completely as all training data are independent.
+Low rank constrain plays important role to simulate motion smoothness assumption.
 
+% Back Ground, uses Nondas' paper "Automatic Construction of Deformable Models In-The-Wild" as place holder
 The two most closely related works to the proposed
@@
 to be robust to both within-class and out-of-class outliers4,
-which cannot be avoided in totally unsupervised settings,
+which cannot be avoided in totally unsupervised setting
 statistical component analysis techniques should be
-employed \cite{?}. We summarize our contributions as follows:
+employed \cite{?}.
 
-We present experimental results on the task of face alignment.
-We choose this application because there exist many
-in-the-wild facial databases with a large number of images
-and annotated landmarks, hence solid quantitative evaluations
-can be performed.
+We summarize our contributions as follows:
+\begin{itemize}
+  \item Constructing SDMs using training data with inconsistent annotation.
+  \item Introduce highly effective curve annotation which tremendously reduces manual work overload but maintains same performance level against state-of-the-art SDMs.
+  \item Building dense correspondent SDMs with shape flow
+\end{itemize}
+
+In our experiment, we show that building robust dense models trained with inconsistent annotation and trained with curve annotation improves performance of discriminative models trained on carefully annotated data including ears, faces, bottles, (cars ?) and bodies.
+Evaluation methods and choices are described in details.
 

### 2015-04-20 contents/introduction.tex
Introduction Updated by Stefanos

@@
-Building and training deformable models of objects (e.g.
+% Building and training deformable models of objects (e.g.
 faces, ears, bodies, bottles, vehicles etc.) has recently been widely researched for object detection, part localisation, fitting, recognition and tracking using manual annotated data.
@@
 
-To train deformable models with satisfiable generalisation, large amount of careful manual annotation is required.
+% To train deformable models with satisfiable generalisation, large amount of careful manual annotation is required.
 However, landmark annotation is extremely time consuming, work intensive and, most importantly, number of landmarks have to stay consistent for all training data while it is challenging to maintain the consistency or to avoid bias when annotating objects that having reach features.
@@
 Fossa Triangularies and Crus Helicis are optional feature of an ear also their visibility is highly sensitive to pose and illumination variation).
-To illustrate how much time consuming careful ear annotation is, according to our experience, a trained annotator may need an average of (TODO: experiment) minutes per image for the manual annotation of 55 landmarks.
+% To illustrate how much time consuming careful ear annotation is, according to our experience, a trained annotator may need an average of (TODO: experiment) minutes per image for the manual annotation of 55 landmarks.
 This means that the annotation of 1000 images requires a total of about (TODO: experiment).
@@
 
-We propose a framework to (1) construct SDMs using training data with inconsistent annotation, (2) introduce highly effective curve annotation which tremendously reduces manual work overload but maintains same performance level against state-of-the-art SDMs and (3) build dense correspondent SDMs with shape flow.
+% We propose a framework to (1) construct SDMs using training data with inconsistent annotation, (2) introduce highly effective curve annotation which tremendously reduces manual work overload but maintains same performance level against state-of-the-art SDMs and (3) build dense correspondent SDMs with shape flow.
 
-%(1)
-Annotated data of same objects can have various number of landmarks, \cite{?} shown faces have landmarks different in range 10+ to 70+.
+% %(1)
+% Annotated data of same objects can have various number of landmarks, \cite{?} shown faces have landmarks different in range 10+ to 70+.
 Building SDMs (e.g.
@@
 
-%(2)
-Due to the fact that manual annotation is a rather costly and labour-intensive procedure, unsupervised and semi supervised learning of models for the tasks of alignment, landmark localization, tracking and recognition has attracted considerable attention \cite{?}.
+% %(2)
+% Due to the fact that manual annotation is a rather costly and labour-intensive procedure, unsupervised and semi supervised learning of models for the tasks of alignment, landmark localization, tracking and recognition has attracted considerable attention \cite{?}.
 As our proposed framework are available to handle landmarks with inconsistency, it leads to a more efficient, convenient, unbiased and simple annotation methods - curve annotation.
 
-%(3)
-To build dense correspondence between independent shapes, we apply optical flow on shapes with low rank constrains, so we name it shape flow.
+% %(3)
+% To build dense correspondence between independent shapes, we apply optical flow on shapes with low rank constrains, so we name it shape flow.
 Optical flow is originally applied to video sequences that several assumptions holds, illumination consistency and motion smoothness, while shapes having no motion smoothness completely as all training data are independent.
@@
 
-% Back Ground, uses Nondas' paper "Automatic Construction of Deformable Models In-The-Wild" as place holder
-The two most closely related works to the proposed
-method are the automatic construction of Active Appearance
-Models (AAMs) in \cite{?} and the so-called RASL
-methodology in \cite{?} for person-specific face alignment.
-There are two main differences between our framework
-and \cite{?}. (1) We use a predefined statistical shape model
-instead of trying to find both the shape and appearance models.
-We believe that with the current available optimization
-techniques, it is extremely difficult to simultaneously optimize
-for both the texture and shape parameters. (2) We
-employ the robust component analysis of \cite{?} for the appearance
-which deals with outliers. Thus, even though
-our method is similar in concept to \cite{?}, these two differences
-make the problem feasible to solve. In particular, the
-methodology in \cite{?} fails to create a generic model even in
-controlled recording conditions, due to extremely high dimensionality
-of the parameters to be found and to the sensitivity
-of the subspace method to outliers. This was probably
-one of the reasons why the authors demonstrate very
-limited and only person-specific experiments. Furthermore,
-our methodology bypasses some of the limitations of \cite{?},
-which requires the presence of only one low-rank subspace,
-hence it has been shown to work only for the case of congealing
-images of a single person. Finally, we argue that
-in order for an automatically constructed AAM methodology
-to be robust to both within-class and out-of-class outliers4,
-which cannot be avoided in totally unsupervised setting
-statistical component analysis techniques should be
-employed \cite{?}.
+% % Back Ground, uses Nondas' paper "Automatic Construction of Deformable Models In-The-Wild" as place holder
+% The two most closely related works to the proposed
+% method are the automatic construction of Active Appearance
+% Models (AAMs) in \cite{?} and the so-called RASL
+% methodology in \cite{?} for person-specific face alignment.
+% There are two main differences between our framework
+% and \cite{?}. (1) We use a predefined statistical shape model
+% instead of trying to find both the shape and appearance models.
+% We believe that with the current available optimization
+% techniques, it is extremely difficult to simultaneously optimize
+% for both the texture and shape parameters. (2) We
+% employ the robust component analysis of \cite{?} for the appearance
+% which deals with outliers. Thus, even though
+% our method is similar in concept to \cite{?}, these two differences
+% make the problem feasible to solve. In particular, the
+% methodology in \cite{?} fails to create a generic model even in
+% controlled recording conditions, due to extremely high dimensionality
+% of the parameters to be found and to the sensitivity
+% of the subspace method to outliers. This was probably
+% one of the reasons why the authors demonstrate very
+% limited and only person-specific experiments. Furthermore,
+% our methodology bypasses some of the limitations of \cite{?},
+% which requires the presence of only one low-rank subspace,
+% hence it has been shown to work only for the case of congealing
+% images of a single person. Finally, we argue that
+% in order for an automatically constructed AAM methodology
+% to be robust to both within-class and out-of-class outliers4,
+% which cannot be avoided in totally unsupervised setting
+% statistical component analysis techniques should be
+% employed \cite{?}.
 
-We summarize our contributions as follows:
+% We summarize our contributions as follows:
+% \begin{itemize}
+%   \item Constructing SDMs using training data with inconsistent annotation.
+%   \item Introduce highly effective curve annotation which tremendously reduces manual work overload but maintains same performance level against state-of-the-art SDMs.
+%   \item Building dense correspondent SDMs with shape flow
+% \end{itemize}
+
+% In our experiment, we show that building robust dense models trained with inconsistent annotation and trained with curve annotation improves performance of discriminative models trained on carefully annotated data including ears, faces, bottles, (cars ?) and bodies.
+Evaluation methods and choices are described in details.
+
+% \clearpage
+
+Building and fitting statistical deformable models of objects is a well-studied and popular area in the intersection of computer vision and machine learning [..].
+Recently, we have witnessed tremendous developments in building and fitting models of human face and body using images captured in unconstrained recording conditions, usually referred to as "in-the-wild" [..].
+This is attributed to
+\begin{itemize}
+
+\item the abundance of complex visual data, spread mostly through the internet via web services such as Youtube, Flickr and Google Images.
+The latter has led to the development of huge databases of "in-the-wild" images of human faces and bodies [..].
+Equally important is the task of manual annotation of images with regards to face and body parts and that has been undertaken by several research teams [..].
+
+\item the development of powerful visual features, able to describe objects and its parts in a robust manner (e.g., Scale Invariant Feature Transforms (SIFT) [39], Histogram of Oriented Gradients (HoGs) [16] and recently Deep Convolutional Neural Networks [..]), as well as generative and discriminative methodologies for learning deformable models.
+
+\end{itemize}
+
+There are two drawbacks on building deformable models that rely on landmarks 
+\begin{itemize}
+
+\item annotating with regards to consistent landmark annotation is extremely time consuming, laborious and labour intensive work [..], which usually can be performed by a trained person.
+Furthermore, for many objects it requires a highly skilled person to identify and annotate a set of images with regards to a consistent set of landmarks.
+For example human ears have very complicated inner structures (e.g.
+helix, crus antihelicis, scapha, tragus, lobe etc.) which differs remarkably between ears.
+Furthermore,
+certain ear parts, such as  Fossa Triangularies and Crus Helicis, do not appear in all ears and  their visibility is highly sensitive to pose and illumination variation. Please see Fig...
+
+\item the nature of many deformable objects do not allow to be consistently annotated with regards to a set of landmarks (e.g.
+bottles, fruits etc.).
+Also the boundary/outline of objects, such as faces, ears, body can be very difficultly annotated consistently.
+That is why many state-of-the-art opt to leave the boundary out for comparison [..].
+An example is given in Fig..
+The majority of the state-of-the-art methods for landmark-based deformable models [..] are not applicable for objects with no consistent set of landmarks.
+
+\end{itemize}
+
+To illustrate how time consuming careful annotation of ears is we lay down our own experience.
+A trained annotator needs an average of (TODO: experiment) minutes per image for the manual annotation of 55 landmarks.
+This means that the annotation of 1000 images requires a total of about (TODO: experiment).
+Furthermore,  training and fatigue largely influence the annotation accuracy.
+Hence, a second pass on the annotated data is, in many cases, necessary.
+Due to the fact that manual annotation is a rather costly and labour-intensive procedure, unsupervised learning of deformable models for the tasks of alignment has recently attracted some attention \cite{?}.
+Nevertheless, the method [..] requires a consistent set of shapes annotated with landmarks to perform deformable face congealing.
+Finally, since the problem of fully unsupervised discovery of the deformations of arbitrary objects is a very difficult and ill-posed problems the limited number of methods [..] that have been applied for the task cannot be applied for arbitrary collection of images collected "in-the-wild".
+
+In this paper, we provide a solution for annotating an object with regards to its deformations that requires considerable less effort and in the same time can be used to define statistical deformations for objects without consistent set of landmarks.
+That is, we argue that it is better to annotate an object with regards to a set of continues lines that describe the shape of the object.
+An example is provided in Fig..
+where the shape of the facial parts is annotated with continuous lines instead of a number of discrete landmarks.
+Similarly, the shape annotations for the ear, a bottle and human body is shown in Fig..
+Annotating facial images by following this procedure takes only ...
+secs per image.
+Furthermore, these shapes can be automatically produced by recent methods that perform discriminative segmentation of objects.
+
+Furthermore, we show that flow methods have mature enough so that it can be used to densely annotate the proposed shapes using simple, as well as more recent and robust shape representations methods [..].
+In particular, to build dense correspondence between independent shapes, we apply optical flow on shapes with low rank constrains, so we name it shape flow.
+Optical flow is originally applied to video sequences that several assumptions holds, illumination consistency and motion smoothness, while shapes having no motion smoothness completely as all training data are independent.
+Low rank constrain plays important role to simulate motion smoothness assumption.
+
+We show that this way dense correspondences between images can be established and dense Active Appearance Models (AAMs) can be build on top of that.
+We show that the proposed methodology even though not tailored to landmark localization can be applied for landmark localization achieving very good performance.
+Finally, we demonstrate the performance of the proposed methodology for describing objects that do not have consistent landmarks.
+To the best of our knowledge this is the first methodology which can create a dense statistical model for AAM which can operate in "in-the-wild" [..].
+There are methods such as [..] and [..] but ...
+
+In summarize the paper proposed ...:
 \begin{itemize}
@@
 
-In our experiment, we show that building robust dense models trained with inconsistent annotation and trained with curve annotation improves performance of discriminative models trained on carefully annotated data including ears, faces, bottles, (cars ?) and bodies.
-Evaluation methods and choices are described in details.
+%In our experiment, we show that building robust dense models trained with inconsistent annotation and %trained with curve annotation improves performance of discriminative models trained on carefully %annotated data including ears, faces, bottles, (cars ?) and bodies.
+Evaluation methods and choices are %described in details.
+
+%We propose a framework to (1) construct SDMs using training data with inconsistent annotation, (2) %introduce highly effective curve annotation which tremendously reduces manual work overload but %maintains same performance level against state-of-the-art SDMs and (3) build dense correspondent SDMs %with shape flow.
+
+%(1)
+%Annotated data of same objects can have various number of landmarks, \cite{?} shown faces have %landmarks different in range 10+ to 70+.
+Building SDMs (e.g.
+Active Appearance Models), however, %%require training data are annotated consistently, for example, all faces have 68 landmarks, 6 landmarks %for an eye and 9 for a nose \cite{?}.
+Such property of SDMs largely limited their application area like %combining different dataset as one.
+We propose the pipeline with non-rigid alignment and support vector %shape to blend landmarks into relatively consistent shape discriminator before building models.
+
+%(2)
+
+%(3)
+
+% Back Ground, uses Nondas' paper "Automatic Construction of Deformable Models In-The-Wild" as place holder
+%The two most closely related works to the proposed
+%method are the automatic construction of Active Appearance
+%Models (AAMs) in \cite{?} and the so-called RASL
+%methodology in \cite{?} for person-specific face alignment.
+%There are two main differences between our framework
+%and \cite{?}. (1) We use a predefined statistical shape model
+%instead of trying to find both the shape and appearance models.
+%We believe that with the current available optimization
+%techniques, it is extremely difficult to simultaneously optimize
+%for both the texture and shape parameters. (2) We
+%employ the robust component analysis of \cite{?} for the appearance
+%which deals with outliers. Thus, even though
+%our method is similar in concept to \cite{?}, these two differences
+%make the problem feasible to solve. In particular, the
+%methodology in \cite{?} fails to create a generic model even in
+%controlled recording conditions, due to extremely high dimensionality
+%of the parameters to be found and to the sensitivity
+%of the subspace method to outliers. This was probably
+%one of the reasons why the authors demonstrate very
+%limited and only person-specific experiments. Furthermore,
+%our methodology bypasses some of the limitations of \cite{?},
+%which requires the presence of only one low-rank subspace,
+%hence it has been shown to work only for the case of congealing
+%images of a single person. Finally, we argue that
+%in order for an automatically constructed AAM methodology
+%to be robust to both within-class and out-of-class outliers4,
+%which cannot be avoided in totally unsupervised setting
+%statistical component analysis techniques should be
+%employed \cite{?}.
 

### 2015-04-21 contents/introduction.tex
Added Figures for Introduction
Figure Added for Introduction and Implementation

@@
 % \clearpage
+\begin{figure}[t!]
+    \centering
+    \begin{subfigure}[b]{0.145\textwidth}
+            \includegraphics[width=\textwidth]{resources/intro_0_0}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.145\textwidth}
+            \includegraphics[width=\textwidth]{resources/intro_0_1}
+    \end{subfigure}
+   	\hfill
+    \begin{subfigure}[b]{0.145\textwidth}
+            \includegraphics[width=\textwidth]{resources/intro_0_2}
+    \end{subfigure}
+    \\
+    \begin{subfigure}[b]{0.075\textwidth}
+            \includegraphics[width=\textwidth]{resources/intro_1_0}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.075\textwidth}
+            \includegraphics[width=\textwidth]{resources/intro_1_1}
+    \end{subfigure}
+   	\hfill
+    \begin{subfigure}[b]{0.075\textwidth}
+            \includegraphics[width=\textwidth]{resources/intro_1_2}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.075\textwidth}
+            \includegraphics[width=\textwidth]{resources/intro_1_3}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.075\textwidth}
+            \includegraphics[width=\textwidth]{resources/intro_1_4}
+    \end{subfigure}
+   	\hfill
+    \begin{subfigure}[b]{0.075\textwidth}
+            \includegraphics[width=\textwidth]{resources/intro_1_5}
+    \end{subfigure}
+    \\
+    \begin{subfigure}[b]{0.07\textwidth}
+            \includegraphics[width=\textwidth]{resources/intro_2_0}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.07\textwidth}
+            \includegraphics[width=\textwidth]{resources/intro_2_1}
+    \end{subfigure}
+   	\hfill
+    \begin{subfigure}[b]{0.07\textwidth}
+            \includegraphics[width=\textwidth]{resources/intro_2_2}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.07\textwidth}
+            \includegraphics[width=\textwidth]{resources/intro_2_3}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.07\textwidth}
+            \includegraphics[width=\textwidth]{resources/intro_2_4}
+    \end{subfigure}
+   	\hfill
+    \begin{subfigure}[b]{0.07\textwidth}
+            \includegraphics[width=\textwidth]{resources/intro_2_5}
+    \end{subfigure}
+    \\
+    \begin{subfigure}[b]{0.075\textwidth}
+            \includegraphics[width=\textwidth]{resources/intro_3_0}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.075\textwidth}
+            \includegraphics[width=\textwidth]{resources/intro_3_1}
+    \end{subfigure}
+   	\hfill
+    \begin{subfigure}[b]{0.075\textwidth}
+            \includegraphics[width=\textwidth]{resources/intro_3_2}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.075\textwidth}
+            \includegraphics[width=\textwidth]{resources/intro_3_3}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.075\textwidth}
+            \includegraphics[width=\textwidth]{resources/intro_3_4}
+    \end{subfigure}
+   	\hfill
+    \begin{subfigure}[b]{0.075\textwidth}
+            \includegraphics[width=\textwidth]{resources/intro_3_5}
+    \end{subfigure}
+    \caption{Figure}
+\end{figure}
 
@@
 To illustrate how time consuming careful annotation of ears is we lay down our own experience.
-A trained annotator needs an average of (TODO: experiment) minutes per image for the manual annotation of 55 landmarks.
-This means that the annotation of 1000 images requires a total of about (TODO: experiment).
+A trained annotator needs an average of 4 minutes per image for the manual annotation of 55 landmarks.
+This means that the annotation of 1000 images requires a total of about 67 hours.
 Furthermore,  training and fatigue largely influence the annotation accuracy.
@@
 Similarly, the shape annotations for the ear, a bottle and human body is shown in Fig..
-Annotating facial images by following this procedure takes only ...
-secs per image.
+Annotating facial images by following this procedure takes less than 30 secs per image.
 Furthermore, these shapes can be automatically produced by recent methods that perform discriminative segmentation of objects.
@@
 %employed \cite{?}.
-
-\clearpage

### 2015-04-22 contents/evaluation.tex
Convergence Test
Updates from ShareLaTeX
Introduction Updated by Stefanos
Temp Push to share with tassos

--- 2015-03-24 contents/evaluation.tex
@@
-To evaluate the quality of model,
+In this section we evaluate the performance of the proposed methodology in a variety of tasks.
+Results for 4 different experiments are reported.
+Experiment \ref{exp:1} compares the fitting accuracy of Dense Active Appearance Models (DAAMs) built using our methodology with respect to that of classic AAMs on the problems of non-rigid face and ear alignment in-the-wild.
+Experiment \ref{exp:2} investigates the impact that the Support Vector Shape representation has on the performance achieved by DAAMs on the the first experiment.
+Experiment \ref{exp:3} evaluates the effectiveness of the proposed methodology to build DAAMs of objects that are difficult to annotated with respect to a consistent set of landmarks, such as bottles and human bodies.
+Finally, experiment \ref{exp:4} serves as a qualitative demonstration of how the proposed pipeline can use be effectively used to generate novel modified instances of an object, e.g.
+caricatures, from simple hand drawn sketches.
 
-\subsection{Using Sparse Point Annotation}
+\subsection{Shape representation and flow constraints}
 
-\subsection{Using Drawing Annotation}
+\begin{figure}[t!]
+\centering
+\includegraphics[width=0.38\textwidth]{resources/Fig_Alignment/svs_experiment}
+\caption{CED over 68 landmarks on the LFPW database.}
+\label{fig:face_ced}
+\end{figure}
+
+\begin{table}[t]
+\small
+\centering
+\begin{tabular}{|l|c|c|c|}
+\hline
+\emph{Method}         & \emph{mean $\pm$ std} & \emph{median} & $\leq 0.05$\\
+\hline
+Initialization        & $\pm$ & & \%\\
+\hline
+SVS representation    & $\pm$ & & \%\\
+Binary representation & $\pm$ & & \%\\
+\hline
+Constraint Flow       & $\pm$ & & \%\\
+Unconstrained Flow    & $\pm$ & & \%\\
+\hline
+\end{tabular}
+\caption{Fitting statistics on the LFPW database.}
+\label{tab:face_statistics}
+\end{table}
+
+\begin{figure}[h!]
+    \centering
+    \begin{subfigure}[b]{0.45\textwidth}
+        \includegraphics[width=\textwidth]{resources/Fig_SVS/faces_svs_binary_gaussian}
+        \caption{AAM Principle Components Contribution}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.2\textwidth}
+            \includegraphics[width=\textwidth]{resources/Fig_SVS/ears_svs_binary_gaussian}
+        % \caption{Shape Flow Principle Components Contribution}
+    \end{subfigure}
+    \\
+    \begin{subfigure}[b]{0.2\textwidth}
+            \includegraphics[width=\textwidth]{resources/Fig_SVS/faces_svs_binary_gaussian_statistics}
+        % \caption{AAM Principle Components Contribution}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.2\textwidth}
+            \includegraphics[width=\textwidth]{resources/Fig_SVS/ears_svs_binary_gaussian_statistics}
+        % \caption{Shape Flow Principle Components Contribution}
+    \end{subfigure}
+    \caption{Principle Components Contribution}
+\end{figure}
+
+\subsection{Non-rigid object alignment in-the-wild}
+\label{exp:1}
+
+\subsubsection{Face alignment}
+
+This experiment compares the fitting accuracy of our DAAMs and classic AAMs.
+For this experiment, both models were built using the 811 training images of the Labelled Faces Parts in-the-Wild (LFPW) \cite{} database and corresponding 68 point annotations provided by the iBUG group \footnote{\label{ibug_300}\url{http://ibug.doc.ic.ac.uk/resources/300-W/}}.
+Classic AAMs were built using the standard procedure described in \cite{} using piece-wise affine as their motion model.
+Our DAAMs were built using the methodology described on the main part of the paper.
+Notice that we modified the previous 68 point annotations of all images by adding and removing $\pm$5 to and from the that were not or subtracted $\approx$
+
+Results for this experiment are reported over the 224 test images of the LFPW cite{} database. 66
+points ground truth landmark annotations were provided by
+the iBUG group8
+. All methods were initialized by perturbing
+the ground truth scale and translation parameters with
+Gaussian noise (rotations were not considered) and applying
+the resulting transformation to mean of the shape model.
+(Notice that this procedure produces initializations that are
+considerably more challenging than those reported in the recent
+AAM literature [32, 33]). The Cumulative Error Distributions
+(CED) for this experiment is shown in Figures 1
+and 2. Figures 3 and 4 shows the evolution of the mean
+normalized point-to-point error as a function of the number
+of iterations run by each algorithm
+
+\begin{figure}[t!]
+\centering
+\includegraphics[width=0.38\textwidth]{resources/Fig_Alignment/face_experiment}
+\caption{CED over 68 landmarks on the LFPW database.}
+\label{fig:face_ced}
+\end{figure}
+
+\begin{table}[t]
+\small
+\centering
+\begin{tabular}{|l|c|c|c|}
+\hline
+\emph{Method}   & \emph{mean $\pm$ std} & \emph{median} & $\leq 0.05$\\
+\hline
+Initialization  & $\pm$ & & \%\\
+\hline
+INT - dAAM      & $\pm$ & & \%\\
+INT - AAM       & $\pm$ & & \%\\
+HOG - dAAM      & $\pm$ & & \%\\
+HOG - AAM       & $\pm$ & & \%\\
+\hline
+\end{tabular}
+\caption{Fitting statistics on the LFPW database.}
+\label{tab:face_statistics}
+\end{table}
+
+%\begin{figure}[h!]
+%    \centering
+%    \begin{subfigure}[b]{0.2\textwidth}
+%            \includegraphics[width=\textwidth]{resources/Fig_Alignment/face_intensity}
+%        % \caption{AAM Principle Components Contribution}
+%    \end{subfigure}
+%    \hfill
+%    \begin{subfigure}[b]{0.2\textwidth}
+%            \includegraphics[width=\textwidth]{resources/Fig_Alignment/ear_intensity}
+%        % \caption{Shape Flow Principle Components Contribution}
+%    \end{subfigure}
+%    \\
+%    \begin{subfigure}[b]{0.2\textwidth}
+%            \includegraphics[width=\textwidth]{resources/Fig_Alignment/face_intensity_statistics}
+%        % \caption{AAM Principle Components Contribution}
+%    \end{subfigure}
+%    \hfill
+%    \begin{subfigure}[b]{0.2\textwidth}
+%            \includegraphics[width=\textwidth]{resources/Fig_Alignment/ear_intensity_statistics}
+%        % \caption{Shape Flow Principle Components Contribution}
+%    \end{subfigure}
+%    \caption{CED Plot and Statistics of Comparison with Classic AAM}
+%\end{figure}
+
+\subsubsection{Ear alignment}
+
+\subsubsection{Objects with loosely define landmarks}
+
+\subsection{DAAMs without consistent annotations}
+\label{exp:3}
+
+\subsection{Object generation from sketches}
+\label{exp:4}
+
+\begin{figure}[h!]
+    \centering
+    \begin{subfigure}[b]{0.1\textwidth}
+            \includegraphics[width=\textwidth]{resources/Fig_Draw/test_01}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.12\textwidth}
+            \includegraphics[width=\textwidth]{resources/Fig_Draw/test_01_base}
+    \end{subfigure}
+   	\hfill
+    \begin{subfigure}[b]{0.1\textwidth}
+            \includegraphics[width=\textwidth]{resources/Fig_Draw/test_01_aam}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.1\textwidth}
+            \includegraphics[width=\textwidth]{resources/Fig_Draw/test_01_of}
+    \end{subfigure}
+    \\
+    \begin{subfigure}[b]{0.1\textwidth}
+            \includegraphics[width=\textwidth]{resources/Fig_Draw/test_02}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.12\textwidth}
+            \includegraphics[width=\textwidth]{resources/Fig_Draw/test_02_base}
+    \end{subfigure}
+   	\hfill
+    \begin{subfigure}[b]{0.1\textwidth}
+            \includegraphics[width=\textwidth]{resources/Fig_Draw/test_02_aam}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.1\textwidth}
+            \includegraphics[width=\textwidth]{resources/Fig_Draw/test_02_of}
+    \end{subfigure}
+    \\
+    \begin{subfigure}[b]{0.1\textwidth}
+            \includegraphics[width=\textwidth]{resources/Fig_Draw/test_03}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.12\textwidth}
+            \includegraphics[width=\textwidth]{resources/Fig_Draw/test_03_base}
+    \end{subfigure}
+   	\hfill
+    \begin{subfigure}[b]{0.1\textwidth}
+            \includegraphics[width=\textwidth]{resources/Fig_Draw/test_03_aam}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.1\textwidth}
+            \includegraphics[width=\textwidth]{resources/Fig_Draw/test_03_of}
+    \end{subfigure}
+    \\
+    \begin{subfigure}[b]{0.1\textwidth}
+            \includegraphics[width=\textwidth]{resources/Fig_Draw/test_04}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.12\textwidth}
+            \includegraphics[width=\textwidth]{resources/Fig_Draw/test_04_base}
+    \end{subfigure}
+   	\hfill
+    \begin{subfigure}[b]{0.1\textwidth}
+            \includegraphics[width=\textwidth]{resources/Fig_Draw/test_04_aam}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.1\textwidth}
+            \includegraphics[width=\textwidth]{resources/Fig_Draw/test_04_of}
+    \end{subfigure}
+    \caption{Figure}
+    \label{fig:draw}
+\end{figure}
 

### 2015-04-22 contents/implementation.tex
Edited Intro
Figure Added for Introduction and Implementation
Temp Push to share with tassos

@@
-\section{Deformable Model without Landmarks}
-
-\begin{figure}[h!]
+\begin{figure*}[t!]
     \centering
-        \includegraphics[width=0.5\textwidth]{resources/architecture}
+        \includegraphics[width=\textwidth]{resources/architecture}
     \caption{Training Architecture}
     \label{fig:archi}
-\end{figure}
+\end{figure*}
+
+\section{Deformable Model without Landmarks}
 
@@
 Our method only requires a set of point or curve annotation that does not need to be consistent over different training samples.
-It combines NICP, SVS representation and multi-image subspace flow in an effective framework that has significant descriptive power.
+It combines Non-Rigid Iterative closest point (NICP) \cite{}, Support Vector Shape (SVS) \cite{} representation and multi-image subspace flow \cite{} in an effective framework that has significant descriptive power.
 
-The proposed pipeline is depicted in Figure ....
-It takes as input a set of training images of an object class, along with point and/or curve annotations.
+The proposed pipeline is depicted in Figure~\ref{fig:archi}.
+It takes as input a set of training images of a particular object class, along with (possibly inconsistent) point and/or curve annotations.
 Its first step is the application of ICP to achieve an initial alignment of the training images.

### 2015-04-22 contents/introduction.tex
Temp Push to share with tassos

--- 2015-04-20 contents/introduction.tex
@@
 % \clearpage
+\begin{figure}[t!]
+    \centering
+    \begin{subfigure}[b]{0.145\textwidth}
+            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_0_0}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.145\textwidth}
+            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_0_1}
+    \end{subfigure}
+   	\hfill
+    \begin{subfigure}[b]{0.145\textwidth}
+            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_0_2}
+    \end{subfigure}
+    \\
+    \begin{subfigure}[b]{0.075\textwidth}
+            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_1_0}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.075\textwidth}
+            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_1_1}
+    \end{subfigure}
+   	\hfill
+    \begin{subfigure}[b]{0.075\textwidth}
+            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_1_2}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.075\textwidth}
+            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_1_3}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.075\textwidth}
+            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_1_4}
+    \end{subfigure}
+   	\hfill
+    \begin{subfigure}[b]{0.075\textwidth}
+            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_1_5}
+    \end{subfigure}
+    \\
+    \begin{subfigure}[b]{0.07\textwidth}
+            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_2_0}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.07\textwidth}
+            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_2_1}
+    \end{subfigure}
+   	\hfill
+    \begin{subfigure}[b]{0.07\textwidth}
+            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_2_2}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.07\textwidth}
+            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_2_3}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.07\textwidth}
+            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_2_4}
+    \end{subfigure}
+   	\hfill
+    \begin{subfigure}[b]{0.07\textwidth}
+            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_2_5}
+    \end{subfigure}
+    \\
+    \begin{subfigure}[b]{0.075\textwidth}
+            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_3_0}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.075\textwidth}
+            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_3_1}
+    \end{subfigure}
+   	\hfill
+    \begin{subfigure}[b]{0.075\textwidth}
+            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_3_2}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.075\textwidth}
+            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_3_3}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.075\textwidth}
+            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_3_4}
+    \end{subfigure}
+   	\hfill
+    \begin{subfigure}[b]{0.075\textwidth}
+            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_3_5}
+    \end{subfigure}
+    \caption{Demonstration of classical landmark annotation and curve annotation of}
+    \label{fig:intro}
+\end{figure}
 
@@
 Recently, we have witnessed tremendous developments in building and fitting models of human face and body using images captured in unconstrained recording conditions, usually referred to as "in-the-wild" [..].
-This is attributed to
+This is attributed to:
 \begin{itemize}
 
-\item the abundance of complex visual data, spread mostly through the internet via web services such as Youtube, Flickr and Google Images.
-The latter has led to the development of huge databases of "in-the-wild" images of human faces and bodies [..].
+\item The abundance of complex visual data, spread mostly through the internet via web services such as Youtube, Flickr and Google Images.
+The latter has led to the development of large databases of "in-the-wild" images of human faces and bodies [..].
 Equally important is the task of manual annotation of images with regards to face and body parts and that has been undertaken by several research teams [..].
 
-\item the development of powerful visual features, able to describe objects and its parts in a robust manner (e.g., Scale Invariant Feature Transforms (SIFT) [39], Histogram of Oriented Gradients (HoGs) [16] and recently Deep Convolutional Neural Networks [..]), as well as generative and discriminative methodologies for learning deformable models.
+\item The development of powerful visual features, able to describe objects and its parts in a robust manner (e.g., Scale Invariant Feature Transforms (SIFT) [39], Histogram of Oriented Gradients (HoGs) [16] and recently Deep Convolutional Neural Networks [..]), as well as generative and discriminative methodologies for learning deformable models.
 
@@
 
-\item annotating with regards to consistent landmark annotation is extremely time consuming, laborious and labour intensive work [..], which usually can be performed by a trained person.
+\item Annotating with regards to consistent landmark annotation is extremely time consuming, tedious and labour intensive work [..], which usually can be performed by a trained person.
 Furthermore, for many objects it requires a highly skilled person to identify and annotate a set of images with regards to a consistent set of landmarks.
@@
 helix, crus antihelicis, scapha, tragus, lobe etc.) which differs remarkably between ears.
-Furthermore,
-certain ear parts, such as  Fossa Triangularies and Crus Helicis, do not appear in all ears and  their visibility is highly sensitive to pose and illumination variation. Please see Fig...
+Furthermore, certain ear parts, such as  Fossa Triangularies and Crus Helicis, do not appear in all ears and  their visibility is highly sensitive to pose and illumination variation.
 
-\item the nature of many deformable objects do not allow to be consistently annotated with regards to a set of landmarks (e.g.
+\item The nature of many deformable objects does not allow them to be consistently annotated with regards to a set of landmarks (e.g.
 bottles, fruits etc.).
-Also the boundary/outline of objects, such as faces, ears, body can be very difficultly annotated consistently.
+Also the boundary/outline of objects, such as faces, ears, body can be very difficultly annotated consistently, Fig.
+\ref{fig:main}.
 That is why many state-of-the-art opt to leave the boundary out for comparison [..].

### 2015-04-23 contents/conclusion.tex
Final Review Submition

We proposed the first, to the best of our knowledge, methodology that can build a dense deformable model "in-the-wild". This methodology does not require a consistent set of landmarks, avoiding the tedious task of careful manual annotations. We have exploited state-of-the-art multiframe optical flow methodologies to establish accurate and robust dense correspondences among shapes, when represented in a landmarks-free fashion. The experimental evaluations and comparisons revealed that dense AAMs that are built on top of our methodology achieve very good performance and can work effectively even in cases of objects that cannot have consistent landmarks.

### 2015-04-23 contents/evaluation.tex
Final Review Submition

--- 2015-03-24 contents/evaluation.tex
@@
-To evaluate the quality of model,
+This sections evaluates the performance of dense Active Appearance Models (dAAMs) built using the proposed methodology in the problem of non-rigid object alignment in-the-wild.
+Results for four different experiments are reported.
+Experiments \ref{exp:svs} and \ref{exp:basis} investigate the impact that the Support Vector Shape representation and the subspace constrains for shape flow have, respectively, on the fitting accuracy achieved by dense AAMs build using the proposed pipeline.
+Experiments \ref{exp:face} and \ref{exp:ear} compare the fitting accuracy of our dense AAMs with respect to that of classic AAMs on the problems of non-rigid face and ear alignment in-the-wild.
+% Finally, experiment \ref{exp:lose} evaluates the effectiveness and performance of the proposed methodology to build dense AAMs of objects that are difficult to annotated with respect to a consistent set of landmarks, such as bottles and human bodies.
+Note that all results reported in this section were obtained by fitting all AAM (dense and classic) using the fast version of the Simultaneous Inverse Compositional algorithm (Fast-SIC) originally proposed by the authors of \cite{Papandreou2008}.
+For further experimental results and visualizations please refer to our supplementary material.
 
-\subsection{Using Sparse Point Annotation}
+%In this section we evaluate the performance of the proposed methodology in a variety of tasks.
+Results for 4 different experiments are reported.
+Experiment \ref{exp:1} compares the fitting accuracy of Dense Active Appearance Models (DAAMs) built using our methodology with respect to that of classic AAMs on the problems of non-rigid face and ear alignment in-the-wild.
+Experiment \ref{exp:2} investigates the impact that the Support Vector Shape representation has on the performance achieved by DAAMs on the the first experiment.
+Experiment \ref{exp:3} evaluates the effectiveness of the proposed methodology to build DAAMs of objects that are difficult to annotated with respect to a consistent set of landmarks, such as bottles and human bodies.
+Finally, experiment \ref{exp:4} serves as a qualitative demonstration of how the proposed pipeline can use be effectively used to generate novel modified instances of an object, e.g.
+caricatures, from simple hand drawn sketches.
 
-\subsection{Using Drawing Annotation}
+\subsection{Shape representation}
+\label{exp:svs}
 
-\clearpage
+This experiment investigates the impact that the SVS representation described in section \ref{sec:svs} has on the final fitting accuracy achieved by dense models built using the propose pipeline.
+In particular, we compare the SVS representation with a simpler shape representation that consists of directly using binary images obtained from curve line annotations.
+In order to make the experiment fair we keep all remaining stages of the pipeline intact and simply change between these two shape representations.
+We use our methodology to build two dense AAMs, one using the SVS representation (SVS-dAAMs) and another using the binary shape representation (Binary-dAAMs).
+Both models were built using 811 training images of the Labelled Faces Parts in-the-Wild (LFPW) \cite{Belhumeur2011} database and tested on 224 testing images of the same database.
+We re-annotated all images from this database using the proposed curve line annotation scheme.
+In order to provide quantitative results, we annotated the reference frame of both dense AAMs (2 images) with the standard 68 point annotation scheme provided by the iBUG group\footnote{\label{ibug_300} \url{http://ibug.doc.ic.ac.uk/resources/300-W/}}.
+Note that, any set of landmarks annotated on the reference frame can be easily extrapolated to any shape generated by dense shape models.
+%; for example, by interpolating its relative position with respect to its immediate reference frame neighbours on the newly generated dense shape instance, \ref{fig:extrapolate_landmarks}. 
+Accuracy is reported in terms of the normalized point-to-point error measure described in \cite{Zhu2012}.
+
+The Cumulative Error Distribution (CED) for this experiment is shown in Figure \ref{fig:svs_ced} while fitting statistics are reported in Table \ref{tab:svs_stats}.
+Looking at the results it can be clearly seen that using SVS results in a constant $\approx$5\% improvement over the simple binary shape representation for almost all CED graph and on the reported fitting statistics.
+
+\begin{figure}[t!]
+\centering
+\includegraphics[width=0.42\textwidth]{resources/Fig_SVS/svs_ced}
+\caption{CED over 68 landmarks on the LFPW database for experiment \ref{exp:svs}}
+\label{fig:svs_ced}
+\end{figure}
+
+\begin{table}[t]
+\small
+\centering
+\begin{tabular}{|l|c|c|c|}
+\hline
+\emph{Method}       & \emph{mean $\pm$ std} & \emph{median} & $\leq 0.05$\\
+\hline\hline
+Initialization      & 0.0805 $\pm$ 0.0246 & 0.0785 & 12\%\\
+SVS                 & 0.0583 $\pm$ 0.0297 & 0.0443 & 57\%\\
+Binary              & 0.0640 $\pm$ 0.0300 & 0.0588 & 39\%\\
+\hline
+\end{tabular}
+\caption{Fitting statistics on the LFPW database for experiment \ref{exp:svs}}
+\label{tab:svs_stats}
+\end{table}
+
+\subsection{Constrained Basis}
+\label{exp:basis}
+
+This experiment investigate the impact of introducing subspace constrains for shape flow.
+The shape representations of training data are independence, thus simply applying flows on shapes breaks the fundamental assumption of motion smoothness.
+The hypothesis is able to be maintained for shapes as described in section~\ref{sec:trabasis}.
+To be specific, we take measures of point-to-point error for fitting same data with our pipeline with same configuration, but only alter the low rank basis.
+
+The experiment results are manifested by constructing two dense AAMs, Basis-dAAMs and no-Basis-dAAMs,among 811 training images from Labelled Faces Parts in-the-Wild (LFPW)\cite{Belhumeur2011} database with 224 testing images using same annotation scheme by iBUG\footnoteref{ibug_300}.
+Cumulative error distributions are shown in Figure~\ref{fig:basis_ced} and corresponding statistics are listed in Table~\ref{tab:basis_stats}. 
+It shows shape flow with constrained basis outperforms, constantly, standard flow technique by an unavoidable amount, which significantly supported the necessities of our low rank basis introduced in~\ref{sec:trabasis}.
+
+\begin{figure}[t!]
+\centering
+\includegraphics[width=0.42\textwidth]{resources/basis_ced}
+\caption{CED over 68 landmarks on the LFPW database for experiment \ref{exp:basis}}
+\label{fig:basis_ced}
+\end{figure}
+
+\begin{table}[t]
+\small
+\centering
+\begin{tabular}{|l|c|c|c|}
+\hline
+\emph{Method}       & \emph{mean $\pm$ std} & \emph{median} & $\leq 0.05$\\
+\hline\hline
+Initialization      & 0.0805 $\pm$ 0.0246 & 0.0785 & 12\%\\
+Constrained Flow    & 0.0583 $\pm$ 0.0332 & 0.0443 & 57\%\\
+Unconstrained Flow  & 0.0698 $\pm$ 0.0458 & 0.0556 & 46\%\\
+\hline
+\end{tabular}
+\caption{Fitting statistics on the LFPW database for experiment \ref{exp:basis}}
+\label{tab:basis_stats}
+\end{table}
+
+\subsection{Non-rigid object alignment in-the-wild}
+\label{exp:alignment}
+
+In the following set of experiments we use the proposed methodology to build dense AAMs of various object classes (faces, ears, bottles and body pose) and quantitatively asses their respective fitting accuracy when fitted to novel in-the-wild images of the previous objects.
+
+\subsubsection{Face alignment}
+\label{exp:face}
+
+This experiment compares the fitting accuracy of our dense AAM versus the one of classic AAM on the problem of non-rigid face alignment in-the-wild.
+For this experiment, both models were built using the 811 training images of the Labelled Faces Parts in-the-Wild (LFPW) \cite{Belhumeur2011} database.
+Classic AAM were built from 68 point landmark annotations\footnoteref{ibug_300} using the standard procedure described in \cite{Cootes2001, Matthews2004}; piece-wise affine was used as their motion model.
+Our dense AAM were built as described in experiment \ref{exp:svs}.
+Given the evidence obtained from that experiment, we used SVS as the shape representation used throughout our pipeline.
+
+Results for this experiment are reported over the 224 testing images of the LFPW database using again 68 point ground truth landmark annotations\footnoteref{ibug_300}.
+For this experiment, we report results using two different image representations, \ie pixels intensities (INT) and Histogram of Oriented Gradients (HOG) \cite{Dalal2005} for both models.
+The two techniques were initialized using our own version of the face detector described in \cite{Zhu2012}.
+
+Cumulative Error Distributions (CED) for this experiment are shown in Figure \ref{fig:face_ced} while fitting statistics are reported in Table \ref{tab:face_stats}.
+Results show that, for this experiment, the fitting accuracy achieved by our dense AAM is comparable to the one achieved by classic AAMs using both image representations.
+In particular, our method seems to perform marginally better when pixel intensities are used as the image representation, while classic AAMs slightly outperform our technique for HOG.
+Overall, both methods achieve similar performance for errors below 5\%.
+We believe this results are remarkable, provided that our model was learned from curve annotations ($\approx$ 30 seconds/image) instead of expensive point landmark annotations ($\approx$ 4 minutes/image).
+
+\begin{figure}[t!]
+\centering
+\includegraphics[width=0.42\textwidth]{resources/Fig_Alignment/face_ced}
+\caption{CED over 68 landmarks on the LFPW database for experiment \ref{exp:face}}
+\label{fig:face_ced}
+\end{figure}
+
+\begin{table}[t]
+\small
+\centering
+\begin{tabular}{|l|c|c|c|}
+\hline
+\emph{Method}   & \emph{mean $\pm$ std} & \emph{median} & $\leq 0.05$\\
+\hline\hline
+Initialization  & 0.0805 $\pm$ 0.0246 & 0.0785 & 12\%\\
+INT - dAAM      & 0.0583 $\pm$ 0.0332 & 0.0443 & 57\%\\
+INT - AAM       & 0.0876 $\pm$ 0.0608 & 0.0797 & 40\%\\
+HOG - dAAM      & 0.0413 $\pm$ 0.0212 & 0.0340 & 85\%\\
+HOG - AAM       & 0.0354 $\pm$ 0.0210 & 0.0266 & 77\%\\
+\hline
+\end{tabular}
+\caption{Fitting statistics on the LFPW database for experiment \ref{exp:face}}
+\label{tab:face_stats}
+\end{table}
+
+\subsubsection{Ear alignment}
+\label{exp:ear}
+
+In this experiment, we studied the feasibility of building and fitting statistical deformable models that capture the variability of the human ear.
+To this end, we collected 605 high resolution images of ears in unconstrained scenarios and annotated them using both a newly defined 55 point annotation scheme for ears and the curve annotations proposed in this paper.
+Examples of these two type of ear annotations are shown in Figure \ref{fig:intro}.
+We randomly split the previous database into two disjoint sets of training (500) and testing (105) images.
+We compare the fitting accuracy obtained by our dense AAM model versus the one of classic AAM on these data.
+Both models were built using the 500 images on the previous training set and their fitting accuracy evaluated on the 105 images of the testing set.
+Note here that we used the same procedures used in experiment \ref{exp:svs} to build the models and evaluate the results (piece-wise affine motion model for classic AAM and SVS, constrained flow and landmark interpolation for dense AAM).
+
+Results for this experiments are shown in Figure \ref{fig:ear_ced} and Table \ref{tab:ear_stats}.
+In this case, we can readily observe that the accuracy achieved by ear models, in terms of the previous normalized point-to-point error measure, is lower than the one achieved by face models.
+This result is expected due to the more complex structure of the ear shape.
+Through visual inspection we determined that fitting errors below $0.1$ for ears typically look plausible under the previous error measure \ref{fig:ear_error}.
+Results for this experiment show that our approach performs significantly better than the classic AAM when pixels intensities are used as image representation.
+In fact, classic AAM fail to improve the accuracy of the original initialization on $\approx45\%$ of the test images while for our the case of our dense model this number goes up to $\approx70\%$.
+On the other hand, the accuracy of both models dramatically improves using HOG.
+In this case, classic AAM outperform our dense AAM for small errors up to $0.1$ while both models obtain similar results for errors around $0.1$.
+Again, the fact that the propose pipeline is capable of dealing with the complex structure of the ear shape and learn dense AAM from simple curve line annotations that can compete and even surpass (in the case of a simple pixel intensity image representation) classic AAM, build from carefully annotated point landmarks, is quite remarkable.
+
+\begin{figure}[t!]
+\centering
+    \begin{subfigure}[b]{0.115\textwidth}
+            \includegraphics[height=1\textwidth]{resources/Fig_Alignment/ear_06_55}
+    \caption{$0.06$}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.115\textwidth}
+            \includegraphics[height=1\textwidth]{resources/Fig_Alignment/ear_1_55}
+    \caption{$0.1$}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.115\textwidth}
+            \includegraphics[height=1\textwidth]{resources/Fig_Alignment/ear_14_55}
+    \caption{$0.14$}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.115\textwidth}
+            \includegraphics[height=1\textwidth]{resources/Fig_Alignment/ear_23_55}
+    \caption{$0.23$}
+    \end{subfigure}
+\caption{Qualitative examples showing different values of normalize point-to-point error measure for ears.}
+\label{fig:ear_error}
+\end{figure}
+
+\begin{figure}[t!]
+\centering
+\includegraphics[width=0.42\textwidth]{resources/Fig_Alignment/ear_ced}
+\caption{CED over 55 landmarks on the collected ear database for experiment \ref{exp:ear}}
+\label{fig:ear_ced}
+\end{figure}
+
+\begin{table}[t]
+\small
+\centering
+\begin{tabular}{|l|c|c|c|}
+\hline
+\emph{Method}   & \emph{mean $\pm$ std} & \emph{median} & $\leq 0.1$\\
+\hline\hline
+Initialization  & 0.1246 $\pm$ 0.0394 & 0.1186 & 32\%\\
+INT - dAAM      & 0.1180 $\pm$ 0.0533 & 0.1030 & 47\%\\
+INT - AAM       & 0.1332 $\pm$ 0.0547 & 0.1261 & 35\%\\
+HOG - dAAM      & 0.0967 $\pm$ 0.0436 & 0.0856 & 66\%\\
+HOG - AAM       & 0.0908 $\pm$ 0.0522 & 0.0729 & 69\%\\
+\hline
+\end{tabular}
+\caption{Fitting statistics on the collected ear database for experiment \ref{exp:ear}}
+\label{tab:ear_stats}
+\end{table}
+
+% \subsubsection{Object alignment with loosely defined landmarks}
+% \label{exp:lose}
+
+% In this section, we experimenting on utilising our dense AAM for objects segmentation.
+Two subjects, bottles and human, are involved.
+As for human segmentation, we gather ground true images from Space-Time Actions\footnote{\label{sta} \url{http://www.wisdom.weizmann.ac.il/~vision/SpaceTimeActions.html}}\cite{ActionsAsSpaceTimeShapes_iccv05]}, where several human action sequences are provided with segmentation.
+There are 10 categories actions where each category contains 10 subjects each are recorded with more than 120 frames.
+For bottles, 500 high resolution images of bottles are collected and annotated using not only a newly defined 50 point annotation scheme for bottles, but also the curve annotations proposed in this paper.
+Figure \ref{fig:intro} demonstrated different annotations of both bottles and human actions.
+We randomly split the previous database into two disjoint sets of training (500) and testing (105) images.
+We compare the fitting accuracy obtained by our dense AAM model versus the one of classic AAM on these data.
+Both models were built using the 500 images on the previous training set and their fitting accuracy evaluated on the 105 images of the testing set.
+Note here that we used the same procedures used in experiment \ref{exp:1} to build the models and evaluate the results (piece-wise affine motion model for classic AAM and SVS, constrained flow and landmark interpolation for dense AAM).
+
+%\subsection{DAAMs without consistent annotations}
+%\label{exp:3}
+
+%\subsection{Object generation from sketches}
+%\label{exp:4}
+
+%\begin{figure}[h!]
+%    \centering
+%    \includegraphics[width=0.45\textwidth]{resources/Fig_Draw/draw}
+%    \caption{Figure}
+%    \label{fig:draw}
+%\end{figure}
+
+% \clearpage
+
+%\begin{figure}[h!]
+%    \centering
+%    \begin{subfigure}[b]{0.45\textwidth}
+%        \includegraphics[width=\textwidth]{resources/Fig_SVS/faces_svs_binary_gaussian}
+%        \caption{AAM Principle Components Contribution}
+%    \end{subfigure}
+%    \hfill
+%    \begin{subfigure}[b]{0.2\textwidth}
+%            \includegraphics[width=\textwidth]{resources/Fig_SVS/ears_svs_binary_gaussian}
+%        % \caption{Shape Flow Principle Components Contribution}
+%    \end{subfigure}
+%    \\
+%    \begin{subfigure}[b]{0.2\textwidth}
+%            \includegraphics[width=\textwidth]{resources/Fig_SVS/faces_svs_binary_gaussian_statistics}
+%        % \caption{AAM Principle Components Contribution}
+%    \end{subfigure}
+%    \hfill
+%    \begin{subfigure}[b]{0.2\textwidth}
+%            \includegraphics[width=\textwidth]{resources/Fig_SVS/ears_svs_binary_gaussian_statistics}
+%        % \caption{Shape Flow Principle Components Contribution}
+%    \end{subfigure}
+%    \caption{Principle Components Contribution}
+%\end{figure}
+
+%\begin{figure}[h!]
+%    \centering
+%    \begin{subfigure}[b]{0.2\textwidth}
+%            \includegraphics[width=\textwidth]{resources/Fig_Alignment/face_intensity}
+%        % \caption{AAM Principle Components Contribution}
+%    \end{subfigure}
+%    \hfill
+%    \begin{subfigure}[b]{0.2\textwidth}
+%            \includegraphics[width=\textwidth]{resources/Fig_Alignment/ear_intensity}
+%        % \caption{Shape Flow Principle Components Contribution}
+%    \end{subfigure}
+%    \\
+%    \begin{subfigure}[b]{0.2\textwidth}
+%            \includegraphics[width=\textwidth]{resources/Fig_Alignment/face_intensity_statistics}
+%        % \caption{AAM Principle Components Contribution}
+%    \end{subfigure}
+%    \hfill
+%    \begin{subfigure}[b]{0.2\textwidth}
+%            \includegraphics[width=\textwidth]{resources/Fig_Alignment/ear_intensity_statistics}
+%        % \caption{Shape Flow Principle Components Contribution}
+%    \end{subfigure}
+%    \caption{CED Plot and Statistics of Comparison with Classic AAM}
+%\end{figure}

### 2015-04-23 contents/implementation.tex
Final Review Submition

@@
         \includegraphics[width=\textwidth]{resources/architecture}
-    \caption{Training Architecture}
+    \caption{Proposed pipeline.}
     \label{fig:archi}
@@
 
-\section{Deformable Model without Landmarks}
+\section{Deformable Models without Landmarks}
 
-Deformable models are widely used for object detection, localization, recognition and tracking while training a deformable model with good generalisation requires tremendous amount of carefully annotated data, which is extremely time consuming.
+% Deformable models are widely used for object detection, localization, recognition and tracking while training a deformable model with good generalisation requires tremendous amount of carefully annotated data, which is extremely time consuming.
 Even more, annotated data of a specific object category typically requires same numbers of landmarks for every training sample, making the annotation procedure significantly complex where corrext menual annotation of landmarks is impossible in various object classes e.g.
@@
 
-Despite the fact that that vast majority of existing methods are based on a sparse shape representation, dense shape representation reveals more nuanced structure in terms of [todo: explain].
+% Despite the fact that that vast majority of existing methods are based on a sparse shape representation, dense shape representation reveals more nuanced structure in terms of [todo: explain].
 
-We propose a novel framework for building deformable models that does not require any consistent set of annotated landmarks and is based on dense shape representation.
-Our method only requires a set of point or curve annotation that does not need to be consistent over different training samples.
-It combines Non-Rigid Iterative closest point (NICP) \cite{}, Support Vector Shape (SVS) \cite{} representation and multi-image subspace flow \cite{} in an effective framework that has significant descriptive power.
+We propose a novel framework for building deformable models that does not require any consistent set of annotated landmarks and is based on a dense shape representation.
+Our method only requires a set of point or curve line annotations that does not need to be consistent over different training samples.
+It combines the techniques of Non-rigid Iterative Closest Point (NICP) \cite{Amber2007}, multi-channel Support Vector Shape (SVS) \cite{Nguyen2013} representation and multi-image subspace flow \cite{} in an effective framework that has significant descriptive power.
 
 The proposed pipeline is depicted in Figure~\ref{fig:archi}.
-It takes as input a set of training images of a particular object class, along with (possibly inconsistent) point and/or curve annotations.
-Its first step is the application of ICP to achieve an initial alignment of the training images.
-Next, the shapes that correspond to the training data are consistently represented using multichannel SVS.
-These are then fed into a multi-image subspace flow estimation that establishes dense correspondences between all shapes of the training set.
+It takes as input a set of training images of a particular object class, along with (possibly inconsistent) point and/or curve line annotations.
+As a first step, the shapes that correspond to the training data are consistently represented using multichannel SVS. 
+The next step is the application of ICP to achieve an initial simple alignment of the SVS images. 
+The similarity-aligned SVS images are then fed into a multi-image subspace flow estimation that establishes dense correspondences between all shapes of the training set.
 In order for the flow estimation to be accurate and exploit the correlation across the different training shapes, it utilises a correspondence basis that is built on sparse correspondences given by Nonrigid ICP alignment of the annotated data.
-Finally, the dense correspondences that are yielded by the optical flow serve as automatic dense landmarks and are used by a dense AAM training and fitting procedure.
-The following sections discuss in more detail the steps of the proposed pipeline.
+Finally, the dense correspondences that are yielded by the optical flow serve as automatic dense landmarks and are used to define a novel dense version of Active Appearance Models.
+The following sections discuss the different stages of the proposed pipeline in further detail.
 
@@
 \subsection{Shape Representation Without Consistent Annotations}
-The first module is to bridge the gap that training data has to have consistent number of landmarks.
-Currently existing annotated databases contains large variety on landmarking, which largely restricted model training to stick to one data set also make evaluation challenging on using distinct data set.
-We propose an algorithm that utilizes a combination of Iterative Closest Point and Support Vector Shape for pre-processing before building the model.
-
-\subsubsection{Initial Alignment of the Training Images}
-
-The model built should only captures deformations that specific to the object, transformations thus rotation, translation and scaling are processed to be invariant to the model\cite{?}.
-ICP is applied to align sparse landmarks.
-ICP is a perfect choice to align various point clouds with no restriction on shape dimension or quantity.
-
-\subsubsection{Multichannel Support Vector Shape Representation}
-Ordinarily, construction of deformable model requires training data set having consistent number of landmarks.
+\label{sec:svs}
+%Ordinarily, construction of deformable model requires training data set having consistent number of landmarks.
 But unavoidable changes has to be made before applying same algorithm on diverse annotated data set.
 
-We proposed a method based on Support Vector Shape (SVS)\cite{?}, which is a decision function trained on shapes using v-SVM with RBF kernel.
-There are several advantages of representing shapes as classifier: general enough to apply on 2D or 3D data, depending on only sparse points and robust against noise, missing data and artifacts.
+In order to fully capture the variability among most deformable object shapes annotations, we use a representation based on Support Vector Shapes (SVS) \cite{Nguyen2013}.
+An SVS is a decision function trained on shapes using Support Vector Machines (SVMs) with  Radial Basis Function (RBF) kernels.
+In this way, a shape is represented as a classifier function, which has several advantages: (a) The representation is completely general, \eg it can be applied to sparse landmark points, curves lines or a combination of the two and (b) It fuses inconsistent landmarks into consistent and directly comparable decision functions.
+Furthermore, this representations is also robust against noise, missing data and outliers.
 
-Assuming input training images are all differently annotated of same object category.
+In practice, we assume that all the training images correspond to the same object category and contain a set of inconsistent points and curve line annotations.
+All annotations are densely sampled to yield a set of annotated landmarks per image, with this set being different for every training image.
 Initially, negative points get randomly sampled around sparse landmarks while annotated landmarks are positive points.
-Since the number of positive points are far less that the that of negative samples, landmarks are assigned considerably larger weight that $N_p \times W_p=N_n \times W_n$ where $N_p, N_n$ are number of positive/negative points and $W_p, W_n$ are weights of positive/negative samples.
+Since the number of positive points is far smaller that the number of negative ones, landmarks are assigned considerably larger weights so that $N_p \times W_p=N_n \times W_n$ where $N_p, N_n$ are number of positive/negative samples and $W_p, W_n$ are their corresponding weights.
 
-SVM with RBF kernel function maps any numbers of data points onto an infinite-dimensional space where positive and negative points are linearly separable, hence classification boundary on 2D space represents the actual shape.
-The decision function for SVM shown below:
+SVMs with RBF kernel function map any numbers of data points onto an infinite-dimensional space where positive and negative points are linearly separable, hence the classification boundary on 2D space represents the actual shape of the object.
+Note that the decision function for SVMs can be mathematically expressed as:
 \begin{equation} \label{eq:decisionfunc}
-    d(x)=\sum_i\alpha k(x_i^*,x)
+    d(\mathbf{x})=\sum_i\alpha_i \, k(\mathbf{x}_i^*,\mathbf{x})
 \end{equation}
-where $x_i^*$ are support vectors and $k(x_i^*,x)$ are Gaussian Radial Basis Function kernel $k(x_i^*,x)=exp(-\lambda \|x_i^*,x\|^2)$.
+where $\mathbf{x}_i^*$ are support vectors and \mbox{$k(\mathbf{x}_i^*, \mathbf{x}) = exp(-\lambda \|\mathbf{x}_i^* -\mathbf{x}\|^2)$} is the RBF kernel .
 
-Figure~\ref{fig:build_svs} demonstrate trained shape descriptor using SVM and the final result is irrelevant to landmark amount.
-Figure~\ref{svs} displays the visualization of the decision function where brighter colour means corresponding pixels belongs to original shape with higher possibility.
-It is a very generalized shape discriminator that blends inconsistent landmark annotations into decision functions.
+Figure \ref{fig:build_svs} shows an exemplar shape representation using SVS. As it can be observed, the final result does not drastically depend on the original number of annotated landmarks.
 
-\begin{figure}[h!]
+\begin{figure}[b!]
     \centering
-    \begin{subfigure}[b]{0.15\textwidth}
+    \begin{subfigure}[b]{0.2\textwidth}
             \includegraphics[width=\textwidth]{resources/landmark}
@@
     \end{subfigure}
-    ~~~~~~~~~
-    \begin{subfigure}[b]{0.15\textwidth}
+    \qquad
+    \begin{subfigure}[b]{0.2\textwidth}
             \includegraphics[width=\textwidth]{resources/svs}
-        \caption{Visualise decision function trained}
+        \caption{Decision function}
         \label{fig:svs}
     \end{subfigure}
-    \caption{Decision function trained on sparse landmarks}
+    \caption{Exemplar SVS shape representation.
+The decision function is trained on the set of sparse landmarks.
+In (b), brighter colour represents higher probability of a pixels belonging to the original shape.}
     \label{fig:build_svs}
+\end{figure}
+
+After constructing the SVS representation for all images, the next step is to apply a simple similarity alignment over them.
+This is done because the goal here is to build a model capable of effectively representing non-rigid local shape deformations rather than global rotation, translation and scaling.
+The alignment is performed by using the Iterative Closest Point (ICP) algorithm \cite{Besl1992} on the annotated landmarks point cloud of the training images.
+
+\subsection{Shape Correspondence Basis}
+
+In order to robustly establish dense correspondences across all SVS images using optical flow, it is important to constrain how pixels are allowed to move from one SVS image to another.
+In this work, we constrained the range of allowed pixels movements by learning a correspondence subspace.
+
+In order to learn the such a subspace, we first transform the original annotation to point clouds.
+Then, we use NICP to align the previous point clouds with respect to a reference point cloud template.
+NICP iteratively deforms each point cloud until its points match the ones on the shape template and correspondences are established.
+However, because optical flow is a pixel-wise frame registration technique, we need to establish correspondences for all pixels on the reference frame rather than for sparse point clouds.
+To achieve this, we apply Thin Plate Spline (TPS) \cite{Bookstein1989} to find correspondences for all pixels in the reference frame given the point cloud correspondences provided by the previous NICP stage.
+Once dense correspondences have been established among all pixels, the so-called correspondence subspace is obtained by performing PCA the trajectory of all pixels.
+Note that incorporating the previous subspace as a low rank constrained in optical flow is consistent with its assumption of smooth motion.
+
+% For all dense transformations $\bm{u_n}(\bm{x}), n \in \{1,...,F\}$, where $F$ is number of data and $\bm{x}$ is vector of pixels, Principle Component Analysis (PCA) is performed on trajectory to obtain low rank trajectory basis:
+% \begin{equation}
+%     \begin{bmatrix}
+%         \bm{u_1}(\bm{x}) \\
+%         \vdots \\
+%         \bm{u_F}(\bm{x})
+%     \end{bmatrix}
+%     =
+%     \begin{bmatrix}
+%         \bm{q_1}(1) & \cdots & \bm{q_R}(1) \\
+%         \vdots      & \ddots & \vdots  \\
+%         \bm{q_1}(F) & \cdots & \bm{q_R}(F)
+%     \end{bmatrix}
+%     \times
+%     \begin{bmatrix}
+%         \bm{v_1}(x) \\
+%         \vdots \\
+%         \bm{v_R}(x)
+%     \end{bmatrix}
+% \end{equation}
+% where $\bm{q_i}(n)$ are low rank components with $R \ll 2F$ and $\bm{v_i}(x)$ weighted each component with dependencies on $x$. Simpler expression shown below:
+% \begin{equation}
+%     \bm{u_n}(\bm{x})=\sum_{i=1}^R\bm{q_i}(n)\bm{v_i}(x)+\bm{\varepsilon_n}(\bm{x})
+% \end{equation}
+
+\begin{figure}[t!]
+    \centering
+    \begin{subfigure}[b]{0.15\textwidth}
+            \includegraphics[width=\textwidth]{resources/Fig_Flows/0}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.15\textwidth}
+            \includegraphics[width=\textwidth]{resources/Fig_Flows/1}
+    \end{subfigure}
+   	\hfill
+    \begin{subfigure}[b]{0.15\textwidth}
+            \includegraphics[width=\textwidth]{resources/Fig_Flows/2}
+    \end{subfigure}
+    \\
+    \begin{subfigure}[b]{0.15\textwidth}
+            \includegraphics[width=\textwidth]{resources/Fig_Flows/3}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.15\textwidth}
+            \includegraphics[width=\textwidth]{resources/Fig_Flows/4}
+    \end{subfigure}
+   	\hfill
+    \begin{subfigure}[b]{0.15\textwidth}
+            \includegraphics[width=\textwidth]{resources/Fig_Flows/5}
+    \end{subfigure}
+    \\
+    \begin{subfigure}[b]{0.15\textwidth}
+            \includegraphics[width=\textwidth]{resources/Fig_Flows/6}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.15\textwidth}
+            \includegraphics[width=\textwidth]{resources/Fig_Flows/7}
+    \end{subfigure}
+   	\hfill
+    \begin{subfigure}[b]{0.15\textwidth}
+            \includegraphics[width=\textwidth]{resources/Fig_Flows/8}
+    \end{subfigure}
+    \caption{Deformation field built}
+    \label{fig:deformationfield}
 \end{figure}
@@
 \subsection{Shape Flow}
+\label{sec:shapeflow}
 
-With decision functions built from training data, the second module designed to register all decision functions to mean shape, we named it Shape Flow.
-Shape Flow is introduced based on optical flow, which generate pixel-wise correspondences for video sequences.
-Optical flow works for video sequences based on assumptions e.g.
-brightness constancy and motion smoothness.
+Using the SVS functions built from training data, the next step of our pipeline is to establish dense correspondences between all these functions.
+We propose to do this procedure jointly, by using the correspondence basis.
+This procedure shares similarities with multiframe optical flow and we call it Shape flow.
+We build upon robust methods for  optical flow estimation.
+Optical flow estimation typically works based on the assumptions of brightness or colour constancy and motion smoothness.
 However, in terms of shapes, neither constant illumination nor continuous motion exists in sequence of shapes as all training data are independent.
-Thus we proposed shape flow with subspace constrains introduced from trajectories.
+For this reason, we propose to modify the formulation of multiframe optical flow by using the correspondence basis that we introduced in conjunction with the SVS functions, rather than actual images.
 
@@
 We supervise trajectories from sparse landmarks.
-To begin with, Non-rigid Iterative Closest Point (NICP)\cite{?} applied on sparse annotated points.
+To begin with, Non-rigid Iterative Closest Point (NICP)\cite{Amber2007} applied on sparse annotated points.
 NICP deforms target points to fit the template iteratively until all points on target deformed to match points on template.
@@
 
-Since optical flow pixel-wise frame registration, the trajectory basis build should also matches the dimension, which is dense on shapes with trajectory length depends on number of training data.
-With correspondences produced after applying NICP, Thin-Plate Spline (TPS)\cite{?} transformations are utilized to warp every shape planes to template plane thereby generates an implicit dense shape registering.
+Since optical flow pixel-wise frame registration, the trajectory basis build should also match the dimension, which is dense on shapes with trajectory length depends on number of training data.
+With correspondences produced after applying NICP, Thin-Plate Spline (TPS)\cite{Bookstein1989} transformations are utilized to warp every shape planes to template plane thereby generates an implicit dense shape registering.
 For all dense transformations $\bm{u_n}(\bm{x}), n \in \{1,...,F\}$, where $F$ is number of data and $\bm{x}$ is vector of pixels, Principle Component Analysis (PCA) is performed on trajectory to obtain low rank trajectory basis:
@@
     &+ \beta \int_{\Omega}\sum_{n=1}^F\|\bm{u_n}(x)-\sum_{i=1}^R\bm{q_i}(n)\bm{v_i}(x)\|^2 dx \label{eq:lowrank}\\
-    &+ \sum[\bm{TV}(Qv)]  + v^T.L.v
+    &+ \sum[\bm{TV}(Qv)]
 \end{align}
-where $d_n(x)$ is the decision function from~\eqref{eq:decisionfunc}, which returns possibilities of given coordinate classified as shape component where coordianates are from set $\Omega \in \Re^2$.
+where $d_n(x)$ is the decision function from~\eqref{eq:decisionfunc}, which returns possibilities of given coordinate classified as shape component where coordinates are from set $\Omega \in \Re^2$.
 $TV(Qv)$ is total variation as regularization on low rank subspace, $Q$ is trajectory basis and $v^T.L.v$ is low rank spacial constrains.
@@
 Part~\eqref{eq:lowrank} applies constrain on low rank trajectory basis states in section~\ref{sec:trabasis}.
-The objective cost function has two free parameters $u$ and $v$, so we performs alternating minimisation.
-The equation can be solved using thresholding scheme as used in \cite{?} after linearisation of image functions.
+The objective cost function has two free parameters $u$ and $v$, so we perform alternating minimisation.
+The equation can be solved using a thresholding scheme after linearisation of image functions.
 The minimisation can be speed up by paralleling the minimisation for every spatial-temporal point $(x;n), x \in \Omega, n \in \{1,...F\}$ independently.
@@
 
-\begin{figure}[h!]
-    \centering
-        \includegraphics[width=0.5\textwidth]{resources/df}
-    \caption{Deformation field built}
-    \label{fig:deformationfield}
-\end{figure}
+% \begin{figure}[h!]
+%     \centering
+%         \includegraphics[width=0.5\textwidth]{resources/df}
+%     \caption{Deformation field built}
+%     \label{fig:deformationfield}
+% \end{figure}
 
@@
     \centering
-        \includegraphics[width=0.4\textwidth]{resources/models}
+    \begin{subfigure}[b]{0.22\textwidth}
+            \includegraphics[width=\textwidth]{resources/Fig_dAAM/of_shape}
+    \end{subfigure}
+  	\hfill
+    \begin{subfigure}[b]{0.22\textwidth}
+            \includegraphics[width=\textwidth]{resources/Fig_dAAM/of_app}
+    \end{subfigure}
     \caption{Dense Deformable Model}
@@
 
-\subsubsection{Drawing Annotation}
+% \begin{figure}[h!]
+%     \centering
+%     \begin{subfigure}[b]{0.22\textwidth}
+%             \includegraphics[width=\textwidth]{resources/Fig_dAAM/of_shape}
+%     \end{subfigure}
+%   	\hfill
+%     \begin{subfigure}[b]{0.22\textwidth}
+%             \includegraphics[width=\textwidth]{resources/Fig_dAAM/of_app}
+%     \end{subfigure}
+%     \caption{Dense Deformable Model}
+%     \label{fig:models}
+% \end{figure}
 
-The purpose of the shape descriptor $\bm{d_i}(x)$ generates probabilities for arbitrary points.
+\subsection{Dense Active Appearance Models}
+
+The deformation fields obtained in section \ref{sec:shapeflow} can be effectively used to learn a naturally dense version of Active Appearance Models \cite{Cootes2001, Matthews2004}.
+Because all deformation fields contain the same number of pixels (the same as on the reference frame) the spatial positions $\mathbf{x}_i=(x_i, y_i)$ of these pixels can be treated as point landmarks and the deformation field themselves as dense annotations of the object's shape.
+Consequently, building a dense shape model reduces to normalizing these dense annotations with respect to a global similarity transform (typically using Procrustes Analysis) and applying Principal Component Analysis (PCA).
+The resulting shape model can be mathematically expressed as:
+\begin{equation}
+    \begin{aligned}
+        \mathbf{s} & = \mathbf{\bar{s}} + \mathbf{S} \mathbf{p}
+    \end{aligned}
+    \label{eq:shape_model}
+\end{equation}
+where $\mathbf{\bar{s}}$ is mean shape and $\mathbf{S}$ and $\mathbf{p}$ are the shape bases and parameters respectively.
+
+On the other hand, the texture model associated to the previous set of densified shapes can be easily obtained by warping all image onto the reference frame, making explicit use of the one-to-one correspondence between pixels on the reference frame and on the deformation fields.
+Once the images have been warped, the texture model is obtained by applying PCA on the warped images.
+The texture model is mathematically defined by the following expression:
+\begin{equation}
+    \begin{aligned}
+        \mathbf{a} = \mathbf{\bar{a}} + \mathbf{A} \mathbf{c}
+    \end{aligned}
+	\label{eq:tex_model}
+\end{equation}
+where $\mathbf{a}$ is the mean texture, and $\mathbf{A}$ and $\mathbf{c}$ are the texture bases and parameters respectively.
+
+Note that, both shape and texture models are directly related through the existent one-to-one correspondence between dense landmarks and pixels on the reference
+frame.
+Therefore, in clear contrast to classic AAMs formulations \cite{Cootes2001, Matthews2004}, no motion model (piece-wise affine, thin-plates splines \cite{Bookstein1989}) is required to relate the previous shape and texture models in our dense formulation.
+As noted by other authors \cite{Amberg2009, Tzimiropoulos2014}, this has the advantage that all efficient compositional gradient descent algorithms for fitting AAMs \cite{Papandreou2008, Matthews2004, Amberg2009, Tzimiropoulos2013, Alabort2014} become exact under our formulation.
+
+%\subsubsection{Drawing Annotation}
+%The purpose of the shape descriptor $\bm{d_i}(x)$ generates probabilities for arbitrary points.
 If we sample points that are exactly pixel-wise integers, and normalise classification value, we can visualise a SVS as an image for example in figure~\ref{fig:svs}.
@@
 But in this situation, pixels at image space are discontinued, so $x$ is constrained to be integer and within the view window of size $N\times M$.
-
-\clearpage

### 2015-04-23 contents/introduction.tex
Final Review Submition

@@
     \end{subfigure}
-    \caption{Demonstration of classical landmark annotation and curve annotation of}
+    \caption{Demonstration of classical landmark annotation and curve annotation of faces, ears, bottles and human actions.}
     \label{fig:intro}
@@
 
-Building and fitting statistical deformable models of objects is a well-studied and popular area in the intersection of computer vision and machine learning [..].
-Recently, we have witnessed tremendous developments in building and fitting models of human face and body using images captured in unconstrained recording conditions, usually referred to as "in-the-wild" [..].
+Building and fitting statistical deformable models of objects is a well-studied and popular area in the intersection of computer vision and machine learning \cite{Cootes1995, Cootes2001, Matthews2004, Saragih2011, Belhumeur2011, Zhu2012, Xiong2013}.
+Recently, we have witnessed tremendous developments in building and fitting models of human face and body using images captured in unconstrained recording conditions, usually referred to as "in-the-wild" \cite{Belhumeur2011, Cao2012, Zhu2012, Xiong2013, Asthana2013, Tzimiropoulos2014, Asthana2014}.
 This is attributed to:
@@
 \item The abundance of complex visual data, spread mostly through the internet via web services such as Youtube, Flickr and Google Images.
-The latter has led to the development of large databases of "in-the-wild" images of human faces and bodies [..].
-Equally important is the task of manual annotation of images with regards to face and body parts and that has been undertaken by several research teams [..].
+The latter has led to the development of large databases of "in-the-wild" images of human faces and bodies \cite{Belhumeur2011, Le2012, Zhu2012, Burgos2013}.
+Equally important is the task of manual annotation of images with regards to face and body parts and that has been undertaken by several research teams \cite{sagonas_iccv_300w_2013}.
 
-\item The development of powerful visual features, able to describe objects and its parts in a robust manner (e.g., Scale Invariant Feature Transforms (SIFT) [39], Histogram of Oriented Gradients (HoGs) [16] and recently Deep Convolutional Neural Networks [..]), as well as generative and discriminative methodologies for learning deformable models.
+\item The development of powerful visual features, able to describe objects and its parts in a robust manner (e.g., Scale Invariant Feature Transforms (SIFT) \cite{lowe1999object}, Histogram of Oriented Gradients (HoGs) \cite{Dalal2005} and recently Deep Convolutional Neural Networks \cite{sermanet2013overfeat}), as well as generative and discriminative methodologies for learning deformable models.
 
@@
 
-There are two drawbacks on building deformable models that rely on landmarks 
+There are two drawbacks on building deformable models that rely on landmarks: 
 \begin{itemize}
 
-\item Annotating with regards to consistent landmark annotation is extremely time consuming, tedious and labour intensive work [..], which usually can be performed by a trained person.
+\item Annotating with regards to consistent landmark annotation is extremely time consuming, tedious and labour intensive work \cite{sagonas_iccv_300w_2013}, which usually can be performed by a trained person.
 Furthermore, for many objects it requires a highly skilled person to identify and annotate a set of images with regards to a consistent set of landmarks.
@@
 helix, crus antihelicis, scapha, tragus, lobe etc.) which differs remarkably between ears.
-Furthermore, certain ear parts, such as  Fossa Triangularies and Crus Helicis, do not appear in all ears and  their visibility is highly sensitive to pose and illumination variation.
+Moreover, certain ear parts, such as  Fossa Triangularies and Crus Helicis, do not appear in all ears and  their visibility is highly sensitive to pose and illumination variation.
 
@@
 bottles, fruits etc.).
-Also the boundary/outline of objects, such as faces, ears, body can be very difficultly annotated consistently, Fig.
-\ref{fig:main}.
-That is why many state-of-the-art opt to leave the boundary out for comparison [..].
-An example is given in Fig..
-The majority of the state-of-the-art methods for landmark-based deformable models [..] are not applicable for objects with no consistent set of landmarks.
+Also the boundary/outline of objects, such as faces, ears, body can be very difficultly annotated consistently, Figure \ref{fig:intro}.
+That is why many state-of-the-art methods opt to leave the boundary out for comparison \cite{Tzimiropoulos2014, Asthana2014}.
+The majority of the state-of-the-art methods for landmark-based deformable models \cite{Cao2012, Zhu2012, Xiong2013, Tzimiropoulos2014, Asthana2014} are not applicable for objects with no consistent set of landmarks.
 
@@
 Hence, a second pass on the annotated data is, in many cases, necessary.
-Due to the fact that manual annotation is a rather costly and labour-intensive procedure, unsupervised learning of deformable models for the tasks of alignment has recently attracted some attention \cite{?}.
-Nevertheless, the method [..] requires a consistent set of shapes annotated with landmarks to perform deformable face congealing.
-Finally, since the problem of fully unsupervised discovery of the deformations of arbitrary objects is a very difficult and ill-posed problems the limited number of methods [..] that have been applied for the task cannot be applied for arbitrary collection of images collected "in-the-wild".
+Due to the fact that manual annotation is a rather costly and labour-intensive procedure, unsupervised learning of deformable models for the tasks of alignment has recently attracted some attention \cite{kokkinos2007unsupervised,jojic2006escaping,jiang2009learning,liu2009simultaneous,baker2004automatic,cox2008least,cootes2004groupwise,frey2003learning}.
+Nevertheless, the method of \cite{antonakos2014automatic} requires a consistent set of shapes annotated with landmarks to perform deformable face congealing.
+Finally, since the problem of fully unsupervised discovery of the deformations of arbitrary objects is a very difficult and ill-posed problems the limited number of methods that have been applied for the task cannot be applied for arbitrary collection of images collected "in-the-wild".
 
@@
 That is, we argue that it is better to annotate an object with regards to a set of continues lines that describe the shape of the object.
-An example is provided in Fig..
-where the shape of the facial parts is annotated with continuous lines instead of a number of discrete landmarks.
-Similarly, the shape annotations for the ear, a bottle and human body is shown in Fig..
-Annotating facial images by following this procedure takes less than 30 secs per image.
+An example is provided in Figure \ref{fig:intro} where the shape of the facial parts is annotated with continuous lines instead of a number of discrete landmarks.
+Similarly, the shape annotations for the ear, a bottle and human body is shown in Figure \ref{fig:intro} Annotating facial images by following this procedure takes less than 30 secs per image.
 Furthermore, these shapes can be automatically produced by recent methods that perform discriminative segmentation of objects.
 
-Furthermore, we show that flow methods have mature enough so that it can be used to densely annotate the proposed shapes using simple, as well as more recent and robust shape representations methods [..].
+Furthermore, we show that flow methods have mature enough so that it can be used to densely annotate the proposed shapes using simple, as well as more recent and robust shape representations methods \cite{Garg:2013hu,Nguyen2013}.
 In particular, to build dense correspondence between independent shapes, we apply optical flow on shapes with low rank constrains, so we name it shape flow.
@@
 Finally, we demonstrate the performance of the proposed methodology for describing objects that do not have consistent landmarks.
-To the best of our knowledge this is the first methodology which can create a dense statistical model for AAM which can operate in "in-the-wild" [..].
-There are methods such as [..] and [..] but ...
+To the best of our knowledge this is the first methodology which can create a dense statistical model for AAM which can operate in "in-the-wild".
 
-In summarize the paper proposed ...:
+%[..]. There are methods such as [..] and [..] but ...
+
+Summarizing, the contributions proposed in this paper are:
 \begin{itemize}

### 2015-04-28 supplementary.tex
Updates from ShareLaTeX

\input{contents/header}

% \iccvfinalcopy % *** Uncomment this line for the final submission

\input{iccv_setting}

\begin{document}

%%%%%%%%% TITLE
\title{Supplementary Materials: Constructing Statistical Deformable Models with Shape Flow}

\author{Yuxiang Zhou, Joan Alabort-i-Medina, Anastasios Roussos, Stefanos Zafeiriou\\
Imperial College London\\
180 Queen’s Gate, SW7 2AZ, London, U.K.\\
{\tt\small \{yuxiang.zhou10, ja310, troussos, s.zafeiriou\}@imperial.ac.uk}}
\maketitle
\thispagestyle{empty}

The supplementary materials provided detailed evaluation of dense Active Appearance Models (dAAMs) built with proposed pipeline of constructing dense AAMs without consistent set of landmarks. There are four experiments reported to support the quality of dAAMs built

%%%%%%%%% Appendix
\appendix
\section{Fitting Results}
\label{sec:fittingresults}

\section{Model Analysis}
\label{sec:modelanalysis}

\section{Appearance \& Shape Reconstruction}
\label{sec:reconstruct}

\section{Segmentation using Dense AAM}
\label{sec:segmentation}

{\small
\bibliographystyle{ieee}
\bibliography{bib}
}

\end{document}

### 2015-04-29 supplementary.tex

@@
 
+\begin{figure}[h!]
+\centering
+    \begin{subfigure}[b]{0.115\textwidth}
+            \includegraphics[height=1\textwidth]{supports/Fittings/fitting_ear_0000}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.115\textwidth}
+            \includegraphics[height=1\textwidth]{supports/Fittings/fitting_ear_0001}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.115\textwidth}
+            \includegraphics[height=1\textwidth]{supports/Fittings/fitting_ear_0010}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.115\textwidth}
+            \includegraphics[height=1\textwidth]{supports/Fittings/fitting_ear_0015}
+    \end{subfigure}
+    % \begin{subfigure}[b]{0.115\textwidth}
+    %         \includegraphics[height=1\textwidth]{supports/Fittings/fitting_ear_0016}
+    % \end{subfigure}
+    % \begin{subfigure}[b]{0.115\textwidth}
+    %         \includegraphics[height=1\textwidth]{supports/Fittings/fitting_ear_0028}
+    % \end{subfigure}
+    % \begin{subfigure}[b]{0.115\textwidth}
+    %         \includegraphics[height=1\textwidth]{supports/Fittings/fitting_ear_0031}
+    % \end{subfigure}
+    % \begin{subfigure}[b]{0.115\textwidth}
+    %         \includegraphics[height=1\textwidth]{supports/Fittings/fitting_ear_0032}
+    % \end{subfigure}
+    % \begin{subfigure}[b]{0.115\textwidth}
+    %         \includegraphics[height=1\textwidth]{supports/Fittings/fitting_face_0001}
+    % \end{subfigure}
+    % \begin{subfigure}[b]{0.115\textwidth}
+    %         \includegraphics[height=1\textwidth]{supports/Fittings/fitting_face_0003}
+    % \end{subfigure}
+    % \begin{subfigure}[b]{0.115\textwidth}
+    %         \includegraphics[height=1\textwidth]{supports/Fittings/fitting_face_0006}
+    % \end{subfigure}
+    % \begin{subfigure}[b]{0.115\textwidth}
+    %         \includegraphics[height=1\textwidth]{supports/Fittings/fitting_face_0008}
+    % \end{subfigure}
+    % \begin{subfigure}[b]{0.115\textwidth}
+    %         \includegraphics[height=1\textwidth]{supports/Fittings/fitting_face_0009}
+    % \end{subfigure}
+    % \begin{subfigure}[b]{0.115\textwidth}
+    %         \includegraphics[height=1\textwidth]{supports/Fittings/fitting_face_0016}
+    % \end{subfigure}
+    % \begin{subfigure}[b]{0.115\textwidth}
+    %         \includegraphics[height=1\textwidth]{supports/Fittings/fitting_face_0020}
+    % \end{subfigure}
+    % \begin{subfigure}[b]{0.115\textwidth}
+    %         \includegraphics[height=1\textwidth]{supports/Fittings/fitting_face_0023}
+    % \end{subfigure}
+\caption{dAAMs Dense Grid Visualisation.}
+\label{fig:fr}
+\end{figure}
+
 The supplementary materials provided detailed evaluation of dense Active Appearance Models (dAAMs) built with proposed pipeline of constructing dense AAMs without consistent set of landmarks.
-There are four experiments reported to support the quality of dAAMs built
+There are four experiments reported to support applications of dAAMs.
+Experiment \ref{sec:fittingresults} exhibits a full fitting visualisations of non-rigid face and ear alignment in-the-wild between classic AAMs and our dense AAMs.
+Experiments \ref{sec:modelanalysis} compares analytical qualities of our dAAMs with respect to that of classic aams in terms of model compactness, warping quality and reconstruction.
+Moreover, experiment \ref{sec:reconstruct} serves as a qualitative demonstration of how the proposed pipeline can use be effectively used to generate novel modified instances of an object, e.g.
+caricatures, from simple hand drawn sketches.
+Finally, experiment \ref{sec:segmentation} evaluates the effectiveness and performance of the proposed methodology to build dense AAMs of objects that are difficult to annotated with respect to a consistent set of landmarks, such as bottles and human bodies.
+Corresponding demonstration shows the usage of utilising dAAMs for objects segmentation with corresponding evaluations on precision.
 
@@
 
-\section{Model Analysis}
+This section provided additional visualisation results of experiments in original paper section 3.3 Non-rigid object alignment in-the-wild, where quantitative analysis of dense AAMs of ears and faces are shown.
+Although there are few figures demonstrated normalise point-to-point error measure of ear fitting, only sparse points are shown in order to maintain readability.
+But here we have visualisation of pixel-wise dense fitting results for both faces and ears.
+Results for this experiment of faces are reported over the 224
+testing images of the LFPW database using 68 point ground truth landmark annotations\footnote{\label{ibug_300} \url{http://ibug.doc.ic.ac.uk/resources/300-W/}}.
+For ears, we collected 605 high resolution images of ears in unconstrained scenarios and annotated them using both a newly defined 55 point annotation scheme for ears and the curve annotations proposed in the paper.
+Results for fitting ears are reported over 105 testing images.
+
+Figure \ref{fig:fr} shows dense fitting results in grid view, thus dense points are visualisible without affecting the visibility of appearance.
+
+\section{Shape Models Analysis}
 \label{sec:modelanalysis}
 
-\section{Appearance \& Shape Reconstruction}
+\begin{figure}[h!]
+    \centering
+    \begin{subfigure}[b]{0.2\textwidth}
+            \includegraphics[width=\textwidth]{supports/Model_Analysis/Shape_Reconstruct_ear}
+        \caption{dAAMs Fitting on Faces}
+    \end{subfigure}
+    \qquad
+    \begin{subfigure}[b]{0.2\textwidth}
+            \includegraphics[width=\textwidth]{supports/Model_Analysis/Shape_Reconstruct_ear_test}
+        \caption{dAAMs Fitting on Ears}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.2\textwidth}
+            \includegraphics[width=\textwidth]{supports/Model_Analysis/Shape_Reconstruct_ear_aam}
+        \caption{AAMs Fitting on Faces}
+    \end{subfigure}
+    \qquad
+    \begin{subfigure}[b]{0.2\textwidth}
+            \includegraphics[width=\textwidth]{supports/Model_Analysis/Shape_Reconstruct_ear_aam_test}
+        \caption{AAMs Fitting on Ears}
+    \end{subfigure}
+    \caption{Final Fitting Statistics of dAAMs and AAMs on Faces}
+    \label{fig:rc_face}
+\end{figure}
+
+There are two experiments shown in this section.
+First experiment investigate the impact of constructing dense points correspondence.
+Note that we are using the same AAMs and dAAMs models built from experiments \ref{sec:fittingresults}.
+The experiment is used to reveal accuracy of dense model reconstruction in shape space.
+In particular, given a ground-truth shape, we use shape models from both AAMs and dAAMs to reconstruct the given shape densely.
+As AAMs having sparse shape model, we densify it the same way as warping textures on to shape model, in this case is piecewise affine transform.
+
+Statistical evaluation are given in terms of the normalised point-to-point error
+measure for reconstructing both ears and faces.
+Figure \ref{fig:rc_face} clearly shows the number of shape components used for reconstruction and corresponding normalised point-to-point error in terms of mean and variance.
+It manifests dAAMs is significantly out performed classic AAMs on shape reconstruction.
+The reconstruction of appearance are shown in experiment \ref{sec:reconstruct}.
+
+\begin{figure}[h!]
+    \centering
+    \begin{subfigure}[b]{0.5\textwidth}
+            \includegraphics[width=\textwidth]{supports/Model_Analysis/ear_aam_eigen_shape}
+        \caption{AAMs Variance Ratio on Ears}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.5\textwidth}
+            \includegraphics[width=\textwidth]{supports/Model_Analysis/ear_of_eigen_shape}
+        \caption{dAAMs Variance Ratio on Ears}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.5\textwidth}
+            \includegraphics[width=\textwidth]{supports/Model_Analysis/face_aam_eigen_shape}
+        \caption{AAMs Variance Ratio on Faces}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.5\textwidth}
+            \includegraphics[width=\textwidth]{supports/Model_Analysis/face_of_eigen_shape}
+        \caption{dAAMs Variance Ratio on Faces}
+    \end{subfigure}
+    \caption{AAMs Variance Ratio}
+    \label{fig:compact}
+\end{figure}
+
+Second experiment are performed to investigate the impact of shape components of AAMs and dAAMs in terms of variance ratio of eigenvalues, shown in figure \ref{fig:compact}.
+We can observe in detail variance ratio of each principle components of shape models and cumulative ratio of first few components.
+As plot revealed, dAAMs proved having a more compact shape model as first few components captures higher variance ratio than that of classic AAMs, therefore less components are needed in order to capture certain amount of variance which leads to better reconstruction especially with few shape components.
+
+\section{Appearance Reconstruction}
 \label{sec:reconstruct}
+
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=0.45\textwidth]{resources/Fig_Draw/draw}
+    \caption{Caricatures Appearance Reconstruction}
+    \label{fig:draw}
+\end{figure}
+
+This experiment serves as a qualitative demonstration of how the proposed pipeline can be effectively used to generate novel modified instances of an object, e.g.
+caricatures.
+To be specific, firstly we manually craft a set of hand-drawn cartoon-like shape sketch before applying shape flow on them to align with reference frame, thus having dense correspondence of landmarks.
+Following with shape reconstruction using both AAMs and dAAMs.
+Lastly warp appearance from arbitrarily chosen faces onto reconstructed shape using piecewise affine (of AAMs) and shape flow (of dAAMs).
+
+The comprehensive results are shown in figure \ref{fig:draw}, where first column is caricatures, second is source textures, third and last columns are corresponding reconstructions of AAMs and dAAMs.
+Comparing with dAAMs, AAMs turned to introduce artifacts on reconstructions especially mouth and eyes area, where nuanced information are missing or models are overly deformed.
+Again, dAAMs not only have remarkable non-rigid alignment performance against AAMs (experiment \ref{sec:fittingresults}) but performs considerably better at objects reconstruction.
 
@@
 \label{sec:segmentation}
+
+\begin{figure}[h!]
+    \centering
+    \begin{subfigure}[b]{0.1\textwidth}
+            \includegraphics[width=\textwidth]{supports/Segmentation_Measure/ear}
+        \caption{Ear Initial Bounding Box}
+    \end{subfigure}
+    \qquad
+    \begin{subfigure}[b]{0.1\textwidth}
+            \includegraphics[width=\textwidth]{supports/Segmentation_Measure/bottle}
+        \caption{Bottle Initial Bounding Box}
+    \end{subfigure}
+    \qquad
+    \begin{subfigure}[b]{0.1\textwidth}
+            \includegraphics[width=\textwidth]{supports/Segmentation_Measure/body}
+        \caption{Body Initial Bounding Box}
+    \end{subfigure}
+    \caption{Perturb Initialisation of Object Detector}
+    \label{fig:seg_init}
+\end{figure}
+
+\begin{figure}[h!]
+    \centering
+    \begin{subfigure}[b]{0.1\textwidth}
+            \includegraphics[width=\textwidth]{supports/Segmentation_Measure/bottle_seg}
+        \caption{Precision Measure of Bottles}
+    \end{subfigure}
+    \qquad
+    \begin{subfigure}[b]{0.1\textwidth}
+            \includegraphics[width=\textwidth]{supports/Segmentation_Measure/body_jump_seg}
+        \caption{Precision Measure of Jumping Action}
+    \end{subfigure}
+    \qquad
+    \begin{subfigure}[b]{0.1\textwidth}
+            \includegraphics[width=\textwidth]{supports/Segmentation_Measure/body_slide_seg}
+        \caption{Precision Measure of Sliding Action}
+    \end{subfigure}
+    \caption{Precision Measure on Segmentation}
+    \label{fig:seg_result}
+\end{figure}
+
+In this section, we experimenting on utilising our dense AAM for objects segmentation.
+Two subjects, bottles and human, are involved.
+As for human segmentation, we gather ground true images from Space-Time Actions\footnote{\label{sta} \url{http://www.wisdom.weizmann.ac.il/~vision/SpaceTimeActions.html}}\cite{ActionsAsSpaceTimeShapes_iccv05]}, where several human action sequences are provided with segmentation.
+There are 10 categories actions where each category contains 10 subjects each are recorded with more than 120 frames.
+For bottles, 500 high resolution images of bottles are collected and annotated using not only a newly defined 50 point annotation scheme for bottles, but also the curve annotations proposed in this paper.
+We randomly split the previous database into two disjoint sets of training (400) and testing (100) images.
+Bottle models were built using 400 training images while body models are built in terms of human actions (e.g.
+jumping), each having approximately 200 training images and 50 test images.
+Note here that we used the same procedures used in experiment \ref{sec:fittingresult} to build models.
+
+Fitting dAAMs on test images gives dense landmarks which could be used to perform segmentation.
+A simple object detector would be required in prior to our pipeline to initialise the fitting.
+For simple evaluation, we perturb the ground-truth segmentation with certain variance to simulate an object detector with implicit detection.
+Initialisation samples are shown in Figure \ref{fig:seg_init}.
+The performance of fitting bottles and bodies are measured based on the segmentation precision shown in Figure \ref{fig:seg_result}, where statistical results including mean, variance and median are presented.
 

### 2015-04-29 supplementary.tex
Another Draft
Supplementary Material Final

@@
 
-\begin{figure}[h!]
-\centering
-    \begin{subfigure}[b]{0.115\textwidth}
-            \includegraphics[height=1\textwidth]{supports/Fittings/fitting_ear_0000}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.115\textwidth}
-            \includegraphics[height=1\textwidth]{supports/Fittings/fitting_ear_0001}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.115\textwidth}
-            \includegraphics[height=1\textwidth]{supports/Fittings/fitting_ear_0010}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.115\textwidth}
-            \includegraphics[height=1\textwidth]{supports/Fittings/fitting_ear_0015}
-    \end{subfigure}
-    % \begin{subfigure}[b]{0.115\textwidth}
-    %         \includegraphics[height=1\textwidth]{supports/Fittings/fitting_ear_0016}
-    % \end{subfigure}
-    % \begin{subfigure}[b]{0.115\textwidth}
-    %         \includegraphics[height=1\textwidth]{supports/Fittings/fitting_ear_0028}
-    % \end{subfigure}
-    % \begin{subfigure}[b]{0.115\textwidth}
-    %         \includegraphics[height=1\textwidth]{supports/Fittings/fitting_ear_0031}
-    % \end{subfigure}
-    % \begin{subfigure}[b]{0.115\textwidth}
-    %         \includegraphics[height=1\textwidth]{supports/Fittings/fitting_ear_0032}
-    % \end{subfigure}
-    % \begin{subfigure}[b]{0.115\textwidth}
-    %         \includegraphics[height=1\textwidth]{supports/Fittings/fitting_face_0001}
-    % \end{subfigure}
-    % \begin{subfigure}[b]{0.115\textwidth}
-    %         \includegraphics[height=1\textwidth]{supports/Fittings/fitting_face_0003}
-    % \end{subfigure}
-    % \begin{subfigure}[b]{0.115\textwidth}
-    %         \includegraphics[height=1\textwidth]{supports/Fittings/fitting_face_0006}
-    % \end{subfigure}
-    % \begin{subfigure}[b]{0.115\textwidth}
-    %         \includegraphics[height=1\textwidth]{supports/Fittings/fitting_face_0008}
-    % \end{subfigure}
-    % \begin{subfigure}[b]{0.115\textwidth}
-    %         \includegraphics[height=1\textwidth]{supports/Fittings/fitting_face_0009}
-    % \end{subfigure}
-    % \begin{subfigure}[b]{0.115\textwidth}
-    %         \includegraphics[height=1\textwidth]{supports/Fittings/fitting_face_0016}
-    % \end{subfigure}
-    % \begin{subfigure}[b]{0.115\textwidth}
-    %         \includegraphics[height=1\textwidth]{supports/Fittings/fitting_face_0020}
-    % \end{subfigure}
-    % \begin{subfigure}[b]{0.115\textwidth}
-    %         \includegraphics[height=1\textwidth]{supports/Fittings/fitting_face_0023}
-    % \end{subfigure}
-\caption{dAAMs Dense Grid Visualisation.}
-\label{fig:fr}
-\end{figure}
-
 The supplementary materials provided detailed evaluation of dense Active Appearance Models (dAAMs) built with proposed pipeline of constructing dense AAMs without consistent set of landmarks.
@@
 Finally, experiment \ref{sec:segmentation} evaluates the effectiveness and performance of the proposed methodology to build dense AAMs of objects that are difficult to annotated with respect to a consistent set of landmarks, such as bottles and human bodies.
-Corresponding demonstration shows the usage of utilising dAAMs for objects segmentation with corresponding evaluations on precision.
+Corresponding demonstration shows the usage of utilising dAAMs for objects segmentation.
 
@@
 But here we have visualisation of pixel-wise dense fitting results for both faces and ears.
-Results for this experiment of faces are reported over the 224
-testing images of the LFPW database using 68 point ground truth landmark annotations\footnote{\label{ibug_300} \url{http://ibug.doc.ic.ac.uk/resources/300-W/}}.
+Results for this experiment of faces are reported over the 224 testing images of the LFPW database using 68 point ground truth landmark annotations
+\footnote{\label{ibug_300} \url{http://ibug.doc.ic.ac.uk/resources/300-W/}}. 
 For ears, we collected 605 high resolution images of ears in unconstrained scenarios and annotated them using both a newly defined 55 point annotation scheme for ears and the curve annotations proposed in the paper.
@@
 Figure \ref{fig:fr} shows dense fitting results in grid view, thus dense points are visualisible without affecting the visibility of appearance.
+Full fitting results visualisation are provided in supplementary videos.
+
+\begin{figure}[!t]
+\centering
+\includegraphics[width=0.45\textwidth]{supports/Fittings/fittings}
+\caption{dAAMs Dense Grid Visualisation.}
+\label{fig:fr}
+\end{figure}
 
@@
 
-\begin{figure}[h!]
+\begin{figure*}[!t]
 \centering
-    \begin{subfigure}[b]{0.2\textwidth}
-            \includegraphics[width=\textwidth]{supports/Model_Analysis/Shape_Reconstruct_ear}
-        \caption{dAAMs Fitting on Faces}
-    \end{subfigure}
-    \qquad
-    \begin{subfigure}[b]{0.2\textwidth}
-            \includegraphics[width=\textwidth]{supports/Model_Analysis/Shape_Reconstruct_ear_test}
-        \caption{dAAMs Fitting on Ears}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.2\textwidth}
-            \includegraphics[width=\textwidth]{supports/Model_Analysis/Shape_Reconstruct_ear_aam}
-        \caption{AAMs Fitting on Faces}
-    \end{subfigure}
-    \qquad
-    \begin{subfigure}[b]{0.2\textwidth}
-            \includegraphics[width=\textwidth]{supports/Model_Analysis/Shape_Reconstruct_ear_aam_test}
-        \caption{AAMs Fitting on Ears}
-    \end{subfigure}
-    \caption{Final Fitting Statistics of dAAMs and AAMs on Faces}
-    \label{fig:rc_face}
-\end{figure}
+\includegraphics[width=\textwidth]{supports/Models/models}
+\caption{First Five Principle Components Visualisation of dAAMs on Ears and Faces}
+\label{fig:pcamodel}
+\end{figure*}
 
@@
 
-Statistical evaluation are given in terms of the normalised point-to-point error
-measure for reconstructing both ears and faces.
+\begin{figure}[!b]
+    \centering
+    \vspace*{-0.1in}
+    \begin{subfigure}[b]{0.4\textwidth}
+            \includegraphics[width=\textwidth]{supports/Model_Analysis/sr_daams}
+        %\caption{dAAMs dense shape reconstruction}
+    \end{subfigure}
+    \\
+    \begin{subfigure}[b]{0.4\textwidth}
+            \includegraphics[width=\textwidth]{supports/Model_Analysis/sr_aams}
+        %\caption{AAMs dense shape reconstruction}
+    \end{subfigure}
+    \caption{Dense Shape Reconstruction}
+    \label{fig:rc_face}
+\end{figure}
+
+Statistical evaluation are given in terms of the normalised point-to-point error measure for reconstructing both ears and faces.
 Figure \ref{fig:rc_face} clearly shows the number of shape components used for reconstruction and corresponding normalised point-to-point error in terms of mean and variance.
@@
 
-\begin{figure}[h!]
+\begin{figure}[!b]
     \centering
-    \begin{subfigure}[b]{0.5\textwidth}
-            \includegraphics[width=\textwidth]{supports/Model_Analysis/ear_aam_eigen_shape}
-        \caption{AAMs Variance Ratio on Ears}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.5\textwidth}
-            \includegraphics[width=\textwidth]{supports/Model_Analysis/ear_of_eigen_shape}
-        \caption{dAAMs Variance Ratio on Ears}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.5\textwidth}
-            \includegraphics[width=\textwidth]{supports/Model_Analysis/face_aam_eigen_shape}
-        \caption{AAMs Variance Ratio on Faces}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.5\textwidth}
-            \includegraphics[width=\textwidth]{supports/Model_Analysis/face_of_eigen_shape}
-        \caption{dAAMs Variance Ratio on Faces}
-    \end{subfigure}
-    \caption{AAMs Variance Ratio}
-    \label{fig:compact}
+    \includegraphics[width=0.45\textwidth]{resources/Fig_Draw/draw}
+    \caption{Caricatures Appearance Reconstruction}
+    \label{fig:draw}
 \end{figure}
@@
 
+Figure \ref{fig:pcamodel} demonstrated shape and appearance models visualisation for dense AAMs of ears and faces.
+Middle column shows mean shape and mean appearance while rest columns present corresponding principle components with $\pm 3$ variance.
+
+\begin{figure}[!t]
+    \centering
+    \begin{subfigure}[b]{0.4\textwidth}
+            \includegraphics[width=\textwidth]{supports/Model_Analysis/variance_ratio}
+        %\caption{dAAMs vs AAMs Variance Ratio}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.4\textwidth}
+            \includegraphics[width=\textwidth]{supports/Model_Analysis/cumulative_variance_ratio}
+        %\caption{dAAMs vs AAMs Cumulative Variance Ratio}
+    \end{subfigure}
+    \caption{dAAMs vs AAMs Variance Ratios}
+    \label{fig:compact}
+\end{figure}
+
 \section{Appearance Reconstruction}
@@
 
-\begin{figure}[h!]
+\begin{table}[!b]
+\small
 \centering
-    \includegraphics[width=0.45\textwidth]{resources/Fig_Draw/draw}
-    \caption{Caricatures Appearance Reconstruction}
-    \label{fig:draw}
-\end{figure}
+\begin{tabular}{|l|c|c|c|}
+\hline
+\emph{Object}   & \emph{mean} & \emph{std} & \emph{median}\\
+\hline\hline
+Bottles         & 0.8125      & 0.1460     & 0.8414\\
+Action - Jump   & 0.6102      & 0.0198     & 0.6099\\
+Action - Slide  & 0.6444      & 0.0500     & 0.6501\\
+\hline
+\end{tabular}
+\caption{Segmentation statistics for experiment \ref{sec:segmentation}}
+\label{tab:seg_result}
+\end{table}
 
@@
 
-\begin{figure}[h!]
+\begin{figure}[!t]
     \centering
-    \begin{subfigure}[b]{0.1\textwidth}
-            \includegraphics[width=\textwidth]{supports/Segmentation_Measure/ear}
-        \caption{Ear Initial Bounding Box}
+    \begin{subfigure}[b]{0.15\textwidth}
+            \includegraphics[height=\textwidth]{supports/Segmentation_Measure/ear}
+        %\caption{Ear Initial Bounding Box}
     \end{subfigure}
-    \qquad
-    \begin{subfigure}[b]{0.1\textwidth}
-            \includegraphics[width=\textwidth]{supports/Segmentation_Measure/bottle}
-        \caption{Bottle Initial Bounding Box}
+    \begin{subfigure}[b]{0.15\textwidth}
+            \includegraphics[height=\textwidth]{supports/Segmentation_Measure/bottle}
+        %\caption{Bottle Initial Bounding Box}
     \end{subfigure}
-    \qquad
-    \begin{subfigure}[b]{0.1\textwidth}
-            \includegraphics[width=\textwidth]{supports/Segmentation_Measure/body}
-        \caption{Body Initial Bounding Box}
+    \begin{subfigure}[b]{0.15\textwidth}
+            \includegraphics[height=\textwidth]{supports/Segmentation_Measure/body}
+        %\caption{Body Initial Bounding Box}
     \end{subfigure}
@@
 
-\begin{figure}[h!]
-    \centering
-    \begin{subfigure}[b]{0.1\textwidth}
-            \includegraphics[width=\textwidth]{supports/Segmentation_Measure/bottle_seg}
-        \caption{Precision Measure of Bottles}
-    \end{subfigure}
-    \qquad
-    \begin{subfigure}[b]{0.1\textwidth}
-            \includegraphics[width=\textwidth]{supports/Segmentation_Measure/body_jump_seg}
-        \caption{Precision Measure of Jumping Action}
-    \end{subfigure}
-    \qquad
-    \begin{subfigure}[b]{0.1\textwidth}
-            \includegraphics[width=\textwidth]{supports/Segmentation_Measure/body_slide_seg}
-        \caption{Precision Measure of Sliding Action}
-    \end{subfigure}
-    \caption{Precision Measure on Segmentation}
-    \label{fig:seg_result}
-\end{figure}
-
 In this section, we experimenting on utilising our dense AAM for objects segmentation.
 Two subjects, bottles and human, are involved.
-As for human segmentation, we gather ground true images from Space-Time Actions\footnote{\label{sta} \url{http://www.wisdom.weizmann.ac.il/~vision/SpaceTimeActions.html}}\cite{ActionsAsSpaceTimeShapes_iccv05]}, where several human action sequences are provided with segmentation.
+As for human segmentation, we gather ground true images from Space-Time Actions
+\footnote{\label{sta} \url{http://www.wisdom.weizmann.ac.il/~vision/SpaceTimeActions.html}},
+where several human action sequences are provided with segmentation.
 There are 10 categories actions where each category contains 10 subjects each are recorded with more than 120 frames.
@@
 jumping), each having approximately 200 training images and 50 test images.
-Note here that we used the same procedures used in experiment \ref{sec:fittingresult} to build models.
+Note here that we used the same procedures used in experiment \ref{sec:fittingresults} to build models.
 
@@
 Initialisation samples are shown in Figure \ref{fig:seg_init}.
-The performance of fitting bottles and bodies are measured based on the segmentation precision shown in Figure \ref{fig:seg_result}, where statistical results including mean, variance and median are presented.
+The performance of fitting bottles and bodies are measured based on the segmentation precision shown in Table \ref{tab:seg_result}, where statistical results including mean, variance and median are presented.
 

### 2015-04-29 supplementary.tex
year fix, figure -> eps

@@
     \begin{subfigure}[b]{0.4\textwidth}
-            \includegraphics[width=\textwidth]{supports/Model_Analysis/variance_ratio}
+            \includegraphics[width=\textwidth]{supports/Model_Analysis/var_ratio}
         %\caption{dAAMs vs AAMs Variance Ratio}
@@
     \begin{subfigure}[b]{0.4\textwidth}
-            \includegraphics[width=\textwidth]{supports/Model_Analysis/cumulative_variance_ratio}
+            \includegraphics[width=\textwidth]{supports/Model_Analysis/cumu_var_ratio}
         %\caption{dAAMs vs AAMs Cumulative Variance Ratio}

### 2015-04-29 supplementary.tex
Updates from ShareLaTeX

--- 2015-04-29 supplementary.tex
@@
 %%%%%%%%% TITLE
-\title{Supplementary Materials: Constructing Statistical Deformable Models with Shape Flow}
+\title{Supplementary Material: Constructing Statistical Deformable Models with Shape Flow}
 
@@
 
-The supplementary materials provided detailed evaluation of dense Active Appearance Models (dAAMs) built with proposed pipeline of constructing dense AAMs without consistent set of landmarks.
-There are four experiments reported to support applications of dAAMs.
-Experiment \ref{sec:fittingresults} exhibits a full fitting visualisations of non-rigid face and ear alignment in-the-wild between classic AAMs and our dense AAMs.
-Experiments \ref{sec:modelanalysis} compares analytical qualities of our dAAMs with respect to that of classic aams in terms of model compactness, warping quality and reconstruction.
+%%%%%%%%% Appendix
+\appendix
+\section{Introduction}
+In this supplementary material, we provide additional experimental results and comparisons for the proposed pipeline of constructing dense AAMs without consistent set of landmarks. 
+We present four different sets of experiments.
+
+reported to support applications of dAAMs.
+
+In Section \ref{sec:fittingresults}, we present visualisations of in-the-wild model fitting  for faces and ears, comparing classic AAMs and the proposed dense AAMs.
+In Section \ref{sec:modelanalysis}, we compares analytical qualities of our dAAMs with respect to that of classic aams in terms of model compactness, warping quality and reconstruction.
 Moreover, experiment \ref{sec:reconstruct} serves as a qualitative demonstration of how the proposed pipeline can use be effectively used to generate novel modified instances of an object, e.g.
@@
 
-%%%%%%%%% Appendix
-\appendix
 \section{Fitting Results}

### 2015-04-29 supplementary.tex
Edited By Tassos

@@
 %%%%%%%%% Appendix
-\appendix
-\section{Introduction}
+\section*{Introduction}
 In this supplementary material, we provide additional experimental results and comparisons for the proposed pipeline of constructing dense AAMs without consistent set of landmarks. 
 We present four different sets of experiments. 
+In Section \ref{sec:fittingresults}, we present visualisations of in-the-wild model fitting  for faces and ears, comparing classic AAMs and the proposed dense AAMs.
+In Section \ref{sec:modelanalysis}, we provide evaluations and comparisons of dAAMs, in terms of model compactness, warping quality and reconstruction accuracy.
+Moreover, Section \ref{sec:reconstruct} serves as a qualitative demonstration of how the proposed pipeline can be used to effectively generate novel modified instances of an object, such as caricatures, from simple hand drawn sketches.
+Finally, in Section \ref{sec:segmentation}, we evaluate the application of the proposed methodology on the problem of segmenting objects that are difficult to annotate with a consistent set of landmarks, such as bottles and human bodies.
 
-reported to support applications of dAAMs.
-
-In Section \ref{sec:fittingresults}, we present visualisations of in-the-wild model fitting  for faces and ears, comparing classic AAMs and the proposed dense AAMs.
-In Section \ref{sec:modelanalysis}, we compares analytical qualities of our dAAMs with respect to that of classic aams in terms of model compactness, warping quality and reconstruction.
-Moreover, experiment \ref{sec:reconstruct} serves as a qualitative demonstration of how the proposed pipeline can use be effectively used to generate novel modified instances of an object, e.g.
-caricatures, from simple hand drawn sketches.
-Finally, experiment \ref{sec:segmentation} evaluates the effectiveness and performance of the proposed methodology to build dense AAMs of objects that are difficult to annotated with respect to a consistent set of landmarks, such as bottles and human bodies.
-Corresponding demonstration shows the usage of utilising dAAMs for objects segmentation.
-
+\appendix
 \section{Fitting Results}
@@
 
-This section provided additional visualisation results of experiments in original paper section 3.3 Non-rigid object alignment in-the-wild, where quantitative analysis of dense AAMs of ears and faces are shown.
-Although there are few figures demonstrated normalise point-to-point error measure of ear fitting, only sparse points are shown in order to maintain readability.
-But here we have visualisation of pixel-wise dense fitting results for both faces and ears.
+This section provides additional visualisations for the experiments of Section 3.3 of the main submission (Non-rigid object alignment in-the-wild).
+We visualise pixel-wise dense fitting results for both faces and ears.
 Results for this experiment of faces are reported over the 224 testing images of the LFPW database using 68 point ground truth landmark annotations
@@
 
-Figure \ref{fig:fr} shows dense fitting results in grid view, thus dense points are visualisible without affecting the visibility of appearance.
-Full fitting results visualisation are provided in supplementary videos.
+Figure \ref{fig:fr} shows dense fitting results using a grid visualisation, thus dense points are visible without affecting the visibility of appearance.
 
@@
 \includegraphics[width=0.45\textwidth]{supports/Fittings/fittings}
-\caption{dAAMs Dense Grid Visualisation.}
+\caption{Result of fitting dAAMs on ears (first two rows) and faces (last two rows). A dense grid visualisation is used.}
 \label{fig:fr}
@@
 
-\section{Shape Models Analysis}
+\section{Shape Model Analysis}
 \label{sec:modelanalysis}
-
-\begin{figure*}[!t]
-\centering
-\includegraphics[width=\textwidth]{supports/Models/models}
-\caption{First Five Principle Components Visualisation of dAAMs on Ears and Faces}
-\label{fig:pcamodel}
-\end{figure*}
-
-There are two experiments shown in this section.
-First experiment investigate the impact of constructing dense points correspondence.
-Note that we are using the same AAMs and dAAMs models built from experiments \ref{sec:fittingresults}.
-The experiment is used to reveal accuracy of dense model reconstruction in shape space.
-In particular, given a ground-truth shape, we use shape models from both AAMs and dAAMs to reconstruct the given shape densely.
-As AAMs having sparse shape model, we densify it the same way as warping textures on to shape model, in this case is piecewise affine transform.
 
@@
     \centering
-    \vspace*{-0.1in}
+    % \vspace*{-0.1in}
     \begin{subfigure}[b]{0.4\textwidth}
@@
     \end{subfigure}
-    \caption{Dense Shape Reconstruction}
+    \caption{Dense shape reconstruction errors for ears and faces.
+Top: results of dAAMs, bottom: results of AAMs.
+The normalised point-to-point error is used an evaluation measure.
+Please notice the major difference in the error scale (vertical axis) between the two plots.}
     \label{fig:rc_face}
@@
 
-Statistical evaluation are given in terms of the normalised point-to-point error measure for reconstructing both ears and faces.
-Figure \ref{fig:rc_face} clearly shows the number of shape components used for reconstruction and corresponding normalised point-to-point error in terms of mean and variance.
-It manifests dAAMs is significantly out performed classic AAMs on shape reconstruction.
-The reconstruction of appearance are shown in experiment \ref{sec:reconstruct}.
+We first investigate the reconstruction accuracy of AAMs and dAAMs in the shape space.
+In particular, given a ground-truth shape, we use the shape models from both AAMs and dAAMs to reconstruct the given shape densely.
+Since AAMs contain a sparse shape model, we densify it using a piecewise affine transformation, which is typically used in warping textures on to shape model too.
+Figure \ref{fig:rc_face} shows plots of dense shape reconstruction errors for ears and faces, for varying number of principal components kept.
+We observe that dAAMs significantly outperform classic AAMs on shape reconstruction.
 
-\begin{figure}[!b]
-    \centering
-    \includegraphics[width=0.45\textwidth]{resources/Fig_Draw/draw}
-    \caption{Caricatures Appearance Reconstruction}
-    \label{fig:draw}
-\end{figure}
-
-Second experiment are performed to investigate the impact of shape components of AAMs and dAAMs in terms of variance ratio of eigenvalues, shown in figure \ref{fig:compact}.
-We can observe in detail variance ratio of each principle components of shape models and cumulative ratio of first few components.
-As plot revealed, dAAMs proved having a more compact shape model as first few components captures higher variance ratio than that of classic AAMs, therefore less components are needed in order to capture certain amount of variance which leads to better reconstruction especially with few shape components.
-
-Figure \ref{fig:pcamodel} demonstrated shape and appearance models visualisation for dense AAMs of ears and faces.
-Middle column shows mean shape and mean appearance while rest columns present corresponding principle components with $\pm 3$ variance.
+Furthermore, we explore the compactness of the built AAMs and dAAMs models. 
+Figure \ref{fig:compact} demonstrates the variance explained as a function of the number of principal components.
+One can infer that dAAMs have a more compact shape model than AAMs, which leads to better reconstruction especially with few shape components.
 
@@
     \end{subfigure}
-    \caption{dAAMs vs AAMs Variance Ratios}
+    \caption{Variance explained by each principal component, for both dAAM and AAM models.
+Top: variance explained by each principal component.
+Bottom: cumulative plot of the variance explained as a function of the principal components.}
     \label{fig:compact}
 \end{figure}
+
+Finally, Figure \ref{fig:pcamodel} visualises the principal components of dAAMs for ears and faces. We observe that the variation of both shape and appearance captured by the model seem plausible.
+
+\begin{figure*}[!t]
+\centering
+\includegraphics[width=\textwidth]{supports/Models/models}
+\caption{Principal components of dAAMs built on ears (top) and faces (bottom).
+The mean (middle columns) as well as the first five principal components are visualised for both shape (left) and appearance (right).
+$\pm 3$ times the variance of the corresponding component is used in each case.}
+\label{fig:pcamodel}
+\end{figure*}
 
@@
 
-\begin{table}[!b]
-\small
+\begin{figure}[!b]
     \centering
-\begin{tabular}{|l|c|c|c|}
-\hline
-\emph{Object}   & \emph{mean} & \emph{std} & \emph{median}\\
-\hline\hline
-Bottles         & 0.8125      & 0.1460     & 0.8414\\
-Action - Jump   & 0.6102      & 0.0198     & 0.6099\\
-Action - Slide  & 0.6444      & 0.0500     & 0.6501\\
-\hline
-\end{tabular}
-\caption{Segmentation statistics for experiment \ref{sec:segmentation}}
-\label{tab:seg_result}
-\end{table}
+    \includegraphics[width=0.45\textwidth]{resources/Fig_Draw/draw}
+    \caption{Synthesizing face images from caricature sketches.
+First column: caricature sketches.
+Second column: arbitrary chosen face images.
+Third and last column: sketch-based warping of images based on AAMs (third column) and dAAMs (last column).}
+    \label{fig:draw}
+\end{figure}
 
-This experiment serves as a qualitative demonstration of how the proposed pipeline can be effectively used to generate novel modified instances of an object, e.g.
+In this qualitative experiment, we show how the proposed pipeline can be used to generate novel modified instances of an object, e.g.
 caricatures.
-To be specific, firstly we manually craft a set of hand-drawn cartoon-like shape sketch before applying shape flow on them to align with reference frame, thus having dense correspondence of landmarks.
-Following with shape reconstruction using both AAMs and dAAMs.
-Lastly warp appearance from arbitrarily chosen faces onto reconstructed shape using piecewise affine (of AAMs) and shape flow (of dAAMs).
-
-The comprehensive results are shown in figure \ref{fig:draw}, where first column is caricatures, second is source textures, third and last columns are corresponding reconstructions of AAMs and dAAMs.
-Comparing with dAAMs, AAMs turned to introduce artifacts on reconstructions especially mouth and eyes area, where nuanced information are missing or models are overly deformed.
-Again, dAAMs not only have remarkable non-rigid alignment performance against AAMs (experiment \ref{sec:fittingresults}) but performs considerably better at objects reconstruction.
+To be specific, firstly we manually craft a set of hand-drawn cartoon-like shape sketches.
+We then apply shape flow to align them with the reference frame.
+In this way, we establish dense correspondences of landmarks.
+Afterwards, we perform shape reconstruction using both AAMs and dAAMs.
+Finally, we warp the appearance from arbitrarily chosen faces on the reconstructed shape using either piecewise affine warp (in the case of AAMs) or shape flow (in the case of dAAMs).
+The corresponding results are shown in figure \ref{fig:draw}.
+We see that AAMs introduce more severe artifacts, especially on the areas of mouth and eyes, where nuanced information is missing or models are overly deformed.
+In contrast, dAAMs yield a significantly more plausible result.
 
@@
 \label{sec:segmentation}
+
+In this section, we present experiments of utilising our dense AAM for object segmentation.
+Two object classes, bottles and human bodies, are considered.
+For human bodies, we use images along with ground truth segmentation from Space-Time Actions dataset \footnote{\label{sta} \url{http://www.wisdom.weizmann.ac.il/~vision/SpaceTimeActions.html}}, which includes sequences with several human actions.
+We use ``jumping'' and ``sliding'' actions.
+As far as bottles are concerned, we use 500 high-resolution images that we collected and annotated using a newly-defined 50 point annotation scheme, as well as the curve annotations proposed in this paper.
+We randomly split these images into two disjoint sets of training (400) and testing (100) images.
+Bottle models were built using 400 training images while body models are built in terms of human actions (e.g.
+jumping), each having approximately 200 training images and 50 test images.
 
@@
     \end{subfigure}
-    \caption{Perturb Initialisation of Object Detector}
+    \caption{Examples of fitting initialisations used for the segmentation experiment. These are created by random perturbation of the ground-truth bounding box.}
     \label{fig:seg_init}
@@
 
-In this section, we experimenting on utilising our dense AAM for objects segmentation.
-Two subjects, bottles and human, are involved.
-As for human segmentation, we gather ground true images from Space-Time Actions
-\footnote{\label{sta} \url{http://www.wisdom.weizmann.ac.il/~vision/SpaceTimeActions.html}},
-where several human action sequences are provided with segmentation.
-There are 10 categories actions where each category contains 10 subjects each are recorded with more than 120 frames.
-For bottles, 500 high resolution images of bottles are collected and annotated using not only a newly defined 50 point annotation scheme for bottles, but also the curve annotations proposed in this paper.
-We randomly split the previous database into two disjoint sets of training (400) and testing (100) images.
-Bottle models were built using 400 training images while body models are built in terms of human actions (e.g.
-jumping), each having approximately 200 training images and 50 test images.
-Note here that we used the same procedures used in experiment \ref{sec:fittingresults} to build models.
+Fitting dAAMs on test images yields dense landmarks that can be used to perform segmentation.
+In a real-world scenario, a simple object detector would be required to be applied prior to our pipeline to initialise the fitting.
+However, as a simple evaluation, we initialise the fitting by randomly perturbing the ground-truth bounding box with certain variance to simulate an object detector with implicit detection, see e.g.~Figure \ref{fig:seg_init}.
+Table  \ref{tab:seg_result} reports the segmentation precision, in case of fitting bottles and human bodies by adopting the proposed dAAMs pipeline.
 
-Fitting dAAMs on test images gives dense landmarks which could be used to perform segmentation.
-A simple object detector would be required in prior to our pipeline to initialise the fitting.
-For simple evaluation, we perturb the ground-truth segmentation with certain variance to simulate an object detector with implicit detection.
-Initialisation samples are shown in Figure \ref{fig:seg_init}.
-The performance of fitting bottles and bodies are measured based on the segmentation precision shown in Table \ref{tab:seg_result}, where statistical results including mean, variance and median are presented.
+\begin{table}[!h]
+\small
+\centering
+\begin{tabular}{|l|c|c|c|}
+\hline
+\emph{Object}   & \emph{mean} & \emph{std} & \emph{median}\\
+\hline\hline
+Bottles         & 0.8125      & 0.1460     & 0.8414\\
+Action - Jump   & 0.6102      & 0.0198     & 0.6099\\
+Action - Slide  & 0.6444      & 0.0500     & 0.6501\\
+\hline
+\end{tabular}
+\caption{Segmentation precision, in case of fitting bottles and human bodies by adopting the proposed dAAMs pipeline. The mean, standard deviation and median of the precision error are provided.}
+\label{tab:seg_result}
+\end{table}
 
-{\small
-\bibliographystyle{ieee}
-\bibliography{bib}
-}
+% {\small
+% \bibliographystyle{ieee}
+% \bibliography{bib}
+% }
 

### 2015-04-29 supplementary.tex
Supplementary Final

@@
 \centering
-\includegraphics[width=0.45\textwidth]{supports/Fittings/fittings}
+\includegraphics[width=0.5\textwidth]{supports/Fittings/fittings}
 \caption{Result of fitting dAAMs on ears (first two rows) and faces (last two rows). A dense grid visualisation is used.}
@@
     % \vspace*{-0.1in}
-    \begin{subfigure}[b]{0.4\textwidth}
-            \includegraphics[width=\textwidth]{supports/Model_Analysis/sr_daams}
+    \begin{subfigure}[b]{0.43\textwidth}
+            \includegraphics[width=\textwidth]{supports/Model_Analysis/sr_ear}
         %\caption{dAAMs dense shape reconstruction}
@@
     \\
-    \begin{subfigure}[b]{0.4\textwidth}
-            \includegraphics[width=\textwidth]{supports/Model_Analysis/sr_aams}
+    \begin{subfigure}[b]{0.43\textwidth}
+            \includegraphics[width=\textwidth]{supports/Model_Analysis/sr_face}
         %\caption{AAMs dense shape reconstruction}
@@
     \caption{Dense shape reconstruction errors for ears and faces.
-Top: results of dAAMs, bottom: results of AAMs.
-The normalised point-to-point error is used an evaluation measure.
-Please notice the major difference in the error scale (vertical axis) between the two plots.}
+Top: results of reconstruction on ears, bottom: results of reconstruction on faces.
+The normalised point-to-point error is used an evaluation measure.}
     \label{fig:rc_face}
@@
     \centering
-    \begin{subfigure}[b]{0.4\textwidth}
+    \begin{subfigure}[b]{0.43\textwidth}
             \includegraphics[width=\textwidth]{supports/Model_Analysis/var_ratio}
@@
     \end{subfigure}
-    \begin{subfigure}[b]{0.4\textwidth}
+    \begin{subfigure}[b]{0.43\textwidth}
             \includegraphics[width=\textwidth]{supports/Model_Analysis/cumu_var_ratio}
@@
     \centering
-    \includegraphics[width=0.45\textwidth]{resources/Fig_Draw/draw}
+    %\vspace*{-0.2in}
+    \includegraphics[width=0.5\textwidth]{resources/Fig_Draw/draw}
     \caption{Synthesizing face images from caricature sketches.

### 2015-07-08 rebuttal.tex
Rebuttal Added

\input{contents/header}

% \iccvfinalcopy % *** Uncomment this line for the final submission

\input{iccv_setting}

\begin{document}

%%%%%%%%% TITLE
\title{Rebuttal: Constructing Statistical Deformable Models with Shape Flow}

\author{Yuxiang Zhou, Joan Alabort-i-Medina, Anastasios Roussos, Stefanos Zafeiriou\\
Imperial College London\\
180 Queen’s Gate, SW7 2AZ, London, U.K.\\
{\tt\small \{yuxiang.zhou10, ja310, troussos, s.zafeiriou\}@imperial.ac.uk}}
\maketitle
\thispagestyle{empty}

\section{To Assigned Reviewer 13}

\textit{There is not much novel or interesting in this paper. The method consists of converting a finite number of user annotated points into a shape model using radial basis functions, something that is standard. It then uses registrations of those representations. The registration algorithm consists of components that are standard. Since there are many methods developed in the computer vision literature for registration of shape representations, this paper would need to compare to those approaches.}
\\ \\
Answer:
\\ \\
\textit{It needs to be elucidated why any standard registration technique would not suffice, and experimental comparison is necessary.}
\\ \\
Answer:
\\ \\

\textit{Section 2.3.2: the optimization of the functional introduced in Eqn 4-6 is not discussed.”}
\\ \\
Answer:
\\ \\
\textit{The experiment in 3.2 claims to show the necessity of the constrained basis in the registration scheme. However, it is not clear what was done. It seems that eqn 4 and 5 were eliminated in the energy functional. I wonder whether the authors used a TV spatial regularity penalty on u? If not, it is clear that the constrained basis would perform better.}
\\ \\
Answer:
To be more specific on the energy function, we still maintain all penalty terms that normal optical flow has, but one additional penalty terms as constrain on Trajactory basis. As we apply flows
\\ \\
\textit{The paper states that the method is robust to annotation errors. However, there are no experiments demonstrating this. There needs to be some experiment evaluating the performance of the algorithm as the user annotation degrades.}
\\ \\
Answer:
\\ \\
\textit{Registration is performed to a "reference image"; it is not stated how this reference image is determined.}
\\ \\
Answer:
\\ \\

\section{To Assigned Reviewer 19}
\textit{My main concern of this work is that it only achieves similar performance as the classic AAM method on the well studied face alignment application. This is very discouraging. If we consider the face alignment algorithms introduced in recent years, they are far better then the classic AAM introduced 7 years ago, and they will be better than the proposed method too.}
\\ \\
Answer:

Performance measured based on consistent number of landmarks which is required by all AAM-like algorithms. However, our model is built based on curve annotation where by default is not comparable with models with landmarks. To compare against AAM, we have to predict the finite number of landmarks from curve annotation which might not be a fair comparison. But we achieved that the predicted landmarks and similar to manual annotations.
\\ \\
\textit{This paper does not mention anything on the efficiency of dAAM method. Given the fact that it has a denser shape model, I assume the speed of the proposed dAAM method will be slower than the classic AAM method. Again, the state-of-art face alignment algorithms based on cascaded regressor are very fast. What is the advantage of the proposed method compared to the state-of-art face alignment algorithms, in terms of efficiency and accuracy? Please comment on this in rebuttal}
\\ \\
Answer:

Slower when building deformable models but faster in alignment due to explicit linear warp transform.
\\ \\
\textit{What is the fundamental advantage of dAAM compared to classic AAM?}
\\ \\
Answer:

Introduced Curve Annotation (need evidence)

Dense Model implies explicit warping in Alignment Stage

Reveals nuanced Shape Information
\\ \\

\textit{The paper discusses the application of this technique to annotating things like bottles and human pose, but does not present results on either task.}
\\ \\
Answer:

No existing benchmarks to against?
\\ \\
\section{To Assigned Reviewer 3}
\textit{The abstract claims that this is the first time SDMs have been built by putting examples in dense correspondence. This is a strange statement, since they refer to papers which do exactly that, such as [7,14]. There is a long history of algorithms for this.}
\\ \\
Answer:
\\ \\

\textit{This explicitly used optical flow to get dense correspondence for a variety of objects. There is also extensive literature on using non-rigid registration for this in the medical image analysis literature.}
\\ \\
Answer:
\\ \\

Final Version:

\end{document}

### 2015-07-15 contents/introduction.tex
Updates from ShareLaTeX

@@
 Building and fitting statistical deformable models of objects is a well-studied and popular area in the intersection of computer vision and machine learning \cite{Cootes1995, Cootes2001, Matthews2004, Saragih2011, Belhumeur2011, Zhu2012, Xiong2013}.
-Recently, we have witnessed tremendous developments in building and fitting models of human face and body using images captured in unconstrained recording conditions, usually referred to as "in-the-wild" \cite{Belhumeur2011, Cao2012, Zhu2012, Xiong2013, Asthana2013, Tzimiropoulos2014, Asthana2014}.
+Recently, we have witnessed tremendous developments in building and fitting models of human faces and bodies using images captured in unconstrained recording environments, usually referred to as "in-the-wild" \cite{Belhumeur2011, Cao2012, Zhu2012, Xiong2013, Asthana2013, Tzimiropoulos2014, Asthana2014}.
 This is attributed to:
@@
 
-\item Annotating with regards to consistent landmark annotation is extremely time consuming, tedious and labour intensive work \cite{sagonas_iccv_300w_2013}, which usually can be performed by a trained person.
+\item Annotating with regards to consistent landmark annotation is an extremely time consuming, tedious and labour intensive work \cite{sagonas_iccv_300w_2013}, which is usually performed by a trained person.
 Furthermore, for many objects it requires a highly skilled person to identify and annotate a set of images with regards to a consistent set of landmarks.
@@
 
-\item The nature of many deformable objects does not allow them to be consistently annotated with regards to a set of landmarks (e.g.
+\item The nature of many deformable objects does not allow them to be consistently annotated with regards to a consistent set of landmarks (e.g.
 bottles, fruits etc.).
@@
 That is why many state-of-the-art methods opt to leave the boundary out for comparison \cite{Tzimiropoulos2014, Asthana2014}.
-The majority of the state-of-the-art methods for landmark-based deformable models \cite{Cao2012, Zhu2012, Xiong2013, Tzimiropoulos2014, Asthana2014} are not applicable for objects with no consistent set of landmarks.
+The majority of the state-of-the-art methods for model-based landmark localisation \cite{Cao2012, Zhu2012, Xiong2013, Tzimiropoulos2014, Asthana2014} are not applicable for objects with inconsistent sets of landmarks.
 
@@
 
-To illustrate how time consuming careful annotation of ears is we lay down our own experience.
+To illustrate how time consuming careful annotation of the human ear is we lay down our own experience.
 A trained annotator needs an average of 4 minutes per image for the manual annotation of 55 landmarks.
@@
 Hence, a second pass on the annotated data is, in many cases, necessary.
-Due to the fact that manual annotation is a rather costly and labour-intensive procedure, unsupervised learning of deformable models for the tasks of alignment has recently attracted some attention \cite{kokkinos2007unsupervised,jojic2006escaping,jiang2009learning,liu2009simultaneous,baker2004automatic,cox2008least,cootes2004groupwise,frey2003learning}.
+Due to the fact that manual annotation is a costly and labour-intensive procedure, unsupervised learning of deformable models for the tasks of object alignment has recently attracted some attention \cite{kokkinos2007unsupervised, jojic2006escaping, jiang2009learning, liu2009simultaneous, baker2004automatic, cox2008least, cootes2004groupwise, frey2003learning}.
 Nevertheless, the method of \cite{antonakos2014automatic} requires a consistent set of shapes annotated with landmarks to perform deformable face congealing.
-Finally, since the problem of fully unsupervised discovery of the deformations of arbitrary objects is a very difficult and ill-posed problems the limited number of methods that have been applied for the task cannot be applied for arbitrary collection of images collected "in-the-wild".
+Finally, because the problem of fully unsupervised discovery of the deformations of arbitrary objects is difficult and ill-posed the limited number of methods that have been applied for the task cannot be applied for arbitrary collection of images collected "in-the-wild".
 
@@
 An example is provided in Figure \ref{fig:intro} where the shape of the facial parts is annotated with continuous lines instead of a number of discrete landmarks.
-Similarly, the shape annotations for the ear, a bottle and human body is shown in Figure \ref{fig:intro} Annotating facial images by following this procedure takes less than 30 secs per image.
+Similarly, the shape annotations for the ear, a bottle and human body is shown in Figure \ref{fig:intro} Annotating facial images by following this procedure takes 42, 38 and 43 secs per image for faces, ears and bottles correspondingly.
 Furthermore, these shapes can be automatically produced by recent methods that perform discriminative segmentation of objects.

### 2015-07-16 contents/implementation.tex
changes tassos shapeflow, locally

@@
 In this section, we present the entire architectures, design decision and algorithms.
-
 \subsection{Shape Representation Without Consistent Annotations}
@@
 We propose to do this procedure jointly, by using the correspondence basis.
-This procedure shares similarities with multiframe optical flow and we call it Shape flow.
+This procedure shares similarities with multiframe optical flow estimation \cite{Garg:2013hu} and we call it Shape flow.
 We build upon robust methods for  optical flow estimation.
@@
 \subsubsection{Non-rigid ICP and Correspondence Basis Creation} \label{sec:trabasis}
-Since shapes from training data set having completely no motion smoothness, it is of importance to contain constrains in optimization on how pixels moves from one shape frame to another.
-We constrain the optimization on correspondence subspace.
-We supervise trajectories from sparse landmarks.
-To begin with, Non-rigid Iterative Closest Point (NICP)\cite{Amber2007} applied on sparse annotated points.
-NICP deforms target points to fit the template iteratively until all points on target deformed to match points on template.
+
+Instead of the \emph{motion} basis used in multiframe optical flow formulation of \cite{Garg:2013hu}, we build a \emph{correspondence} basis that introduces constrains in how points of different shapes are matched to each other.
+By considering a reference shape, every pixel of the image that represents this shape is matched with its corresponding position and in this way defines a \emph{correspondence vector}.
+This vector consists of the 2D locations of the specific point in all shape images.
+To form this vector, the training shapes are arranged in an arbitrary order.
+Similarly to the order of training samples when Principal Component Analysis (PCA) is applied, this order does not affect the result of our method and any re-ordering would produce exactly the same results.
+
+The correspondence basis that we build constrains these correspondence vectors to lie on a subspace and in this way acts as a low-rank prior that enforces coherency of the shape registration result over the whole training dataset of shapes.
+To effectively build this basis, we first apply Non-rigid Iterative Closest Point (NICP)\cite{Amber2007} between the cloud of sparse annotated landmarks in the reference shape and the one of every shape of the training set.
+NICP deforms the cloud of points of every shape to match the points of the reference shape.
+This yields an initial estimation of the correspondence vectors on the sparse locations of annotated landmarks on the reference shape.
+To make this correspondence vectors estimation dense (i.e.~for every pixel of the reference shape), we apply Thin-Plate Splines (TPS)\cite{Bookstein1989} interpolation.
+This initial estimation of dense correspondence vectors define for every training shape a warping function that registers it with the reference shape and equivalently an initial ``shape flow'', i.e.~ an ``optical flow'' between the reference shape and every training shape.
+
+The correspondence basis is found by applying PCA on the result of TPS interpolation and keeping only the first $R$ principal components.
+Formally, let $F$ be the number of training shapes and $n=1,\ldots,F$ be the training shape index.
+Also, let $\boldsymbol{q}_1(n),\ldots,\boldsymbol{q}_R(n):
+\{1,\ldots,F\} \rightarrow \R^2$ be the $R$ orthonormal elements of the correspondence basis, where $\boldsymbol{q}_i(n)$ is the displacement vector that matches the points of the reference shape with the points of the $n$-th training shape shape, according to the variation described from the $i$-th correspondence basis element.
+Note that the basis elements $\boldsymbol{q}_i(n)$ are independent from the point location.
+
+In addition, let ..
+be the image domain where the reference and training shapes are defined and ...
+denote the point location.
+We denote the shape flow result as ...,  where u_n(x) is the displacement vector that matches the point ...
+of the image of the reference shape with its corresponding location at the image of the $n$-th training shape.
+
+Using the constructed correspondence basis, the shape flow can be approximated as:
+
+....
+
+where $\bm{v_i}(\bm{x})$ is the weight that needs to be applied on the $i$-th correspondence basis element, in order to get the correspondence vector for the point location $\bm{x}$.
+In other words, the shape flow for every point $\bm{x}$ is described as linear combination of basis elements that is controlled by the coefficients $\bm{v_i}(\bm{x})$ that depend on $\bm{x}$.
+The values of the $i$-th coefficient for all the points $\bm{v_i}(\bm{x})$ can be interpreted as an image defined on \Omega.
+Using the correspondence basis, the determination of the shape flow boils down to the determination of the set of coefficients $\bm{v_i}(\bm{x})$
+
+, where
+
+We apply PCA on the
+
+a set of warping functions that give an initial registration of every training shape with the reference shape.
+
 Performs the algorithm for all training data will get an implicit point correlation between sparse shapes.
@@
 \begin{equation}
-    \bm{u_n}(\bm{x})=\sum_{i=1}^R\bm{q_i}(n)\bm{v_i}(x)+\bm{\varepsilon_n}(\bm{x})
+    \bm{u_n}(\bm{x})=\sum_{i=1}^R\bm{q_i}(n)\bm{v_i}(\bm{x})+\bm{\varepsilon_n}(\bm{x})
 \end{equation}

### 2015-07-16 contents/implementation.tex
Updates from ShareLaTeX

--- 2015-04-23 contents/implementation.tex
@@
 Our method only requires a set of point or curve line annotations that does not need to be consistent over different training samples.
-It combines the techniques of Non-rigid Iterative Closest Point (NICP) \cite{Amber2007}, multi-channel Support Vector Shape (SVS) \cite{Nguyen2013} representation and multi-image subspace flow \cite{} in an effective framework that has significant descriptive power.
+It combines the techniques of Non-rigid Iterative Closest Point (NICP) \cite{Amber2007}, multi-channel Support Vector Shape (SVS) \cite{Nguyen2013} representation and multi-image subspace flow \cite{Garg:2013hu} in an effective framework that has significant descriptive power.
 
@@
 
-In order to learn the such a subspace, we first transform the original annotation to point clouds.
+In order to learn such a subspace, we first transform the original annotation to point clouds.
 Then, we use NICP to align the previous point clouds with respect to a reference point cloud template.
@@
 \subsubsection{Non-rigid ICP and Correspondence Basis Creation} \label{sec:trabasis}
-Since shapes from training data set having completely no motion smoothness, it is of importance to contain constrains in optimization on how pixels moves from one shape frame to another.
+Since shapes from training data set having completely no motion smoothness, it is of importance to contain constraints in optimization on how pixels moves from one shape frame to another.
 We constrain the optimization on correspondence subspace.
@@
     &+ \beta \int_{\Omega}\sum_{n=1}^F\|\bm{u_n}(x)-\sum_{i=1}^R\bm{q_i}(n)\bm{v_i}(x)\|^2 dx \label{eq:lowrank}\\
-    &+ \sum[\bm{TV}(Qv)]
+    &+ \sum[\bm{TV}(Qv)] + v^T.L.V
 \end{align}
 where $d_n(x)$ is the decision function from~\eqref{eq:decisionfunc}, which returns possibilities of given coordinate classified as shape component where coordinates are from set $\Omega \in \Re^2$.
-$TV(Qv)$ is total variation as regularization on low rank subspace, $Q$ is trajectory basis and $v^T.L.v$ is low rank spacial constrains.
+$TV(Qv)$ is total variation as regularization on low rank subspace, $Q$ is trajectory basis and $v^T.L.v$ is low rank spacial constraints.
 

### 2015-07-16 contents/evaluation.tex
Draft Version
Updates from ShareLaTeX

@@
 Finally, experiment \ref{exp:4} serves as a qualitative demonstration of how the proposed pipeline can use be effectively used to generate novel modified instances of an object, e.g.
-caricatures, from simple hand drawn sketches.
+caricatures, from simple hand drawn sketches
 
@@
 
-In the following set of experiments we use the proposed methodology to build dense AAMs of various object classes (faces, ears, bottles and body pose) and quantitatively asses their respective fitting accuracy when fitted to novel in-the-wild images of the previous objects.
+In the following set of experiments we use the proposed methodology to build dense AAMs of various object classes (faces, ears, bottles and body pose) and quantitatively assess their respective fitting accuracy when fitted to novel in-the-wild images of the previous objects.
 

### 2015-07-16 contents/implementation.tex
Updates from ShareLaTeX

--- 2015-07-16 contents/implementation.tex
@@
 denote the point location.
-We denote the shape flow result as ...,  where u_n(x) is the displacement vector that matches the point ...
+We denote the shape flow result as ...,  where $u_n(x)$ is the displacement vector that matches the point ...
 of the image of the reference shape with its corresponding location at the image of the $n$-th training shape.
@@
 In other words, the shape flow for every point $\bm{x}$ is described as linear combination of basis elements that is controlled by the coefficients $\bm{v_i}(\bm{x})$ that depend on $\bm{x}$.
-The values of the $i$-th coefficient for all the points $\bm{v_i}(\bm{x})$ can be interpreted as an image defined on \Omega.
+The values of the $i$-th coefficient for all the points $\bm{v_i}(\bm{x})$ can be interpreted as an image defined on $\Omega$.
 Using the correspondence basis, the determination of the shape flow boils down to the determination of the set of coefficients $\bm{v_i}(\bm{x})$

### 2015-07-16 contents/implementation.tex
updated sections related to shape flow theory

--- 2015-07-16 contents/implementation.tex
@@
 Our method only requires a set of point or curve line annotations that does not need to be consistent over different training samples.
-It combines the techniques of Non-rigid Iterative Closest Point (NICP) \cite{Amber2007}, multi-channel Support Vector Shape (SVS) \cite{Nguyen2013} representation and multi-image subspace flow \cite{Garg:2013hu} in an effective framework that has significant descriptive power.
+It combines the techniques of Non-rigid Iterative Closest Point (NICP) \cite{Amber2007}, multi-channel Support Vector Shape (SVS) \cite{Nguyen2013} representation and multi-image subspace flow \cite{} in an effective framework that has significant descriptive power.
 
@@
 
-In order to robustly establish dense correspondences across all SVS images using optical flow, it is important to constrain how pixels are allowed to move from one SVS image to another.
-In this work, we constrained the range of allowed pixels movements by learning a correspondence subspace.
+We consider the problem of dense correspondences across SVS images as a joint estimation of optical flow fields between a reference SVS image and every SVS image of the training dataset.
+The estimation of such a ``shape flow'' defines for every training SVS image a warping function that registers it with the reference SVS image.
+To establish the dense correspondences robustly, we are inspired by the idea of subspace constraints in the estimation of multiframe optical flow \cite{Garg:2013hu}.
 
-In order to learn such a subspace, we first transform the original annotation to point clouds.
-Then, we use NICP to align the previous point clouds with respect to a reference point cloud template.
-NICP iteratively deforms each point cloud until its points match the ones on the shape template and correspondences are established.
-However, because optical flow is a pixel-wise frame registration technique, we need to establish correspondences for all pixels on the reference frame rather than for sparse point clouds.
-To achieve this, we apply Thin Plate Spline (TPS) \cite{Bookstein1989} to find correspondences for all pixels in the reference frame given the point cloud correspondences provided by the previous NICP stage.
-Once dense correspondences have been established among all pixels, the so-called correspondence subspace is obtained by performing PCA the trajectory of all pixels.
-Note that incorporating the previous subspace as a low rank constrained in optical flow is consistent with its assumption of smooth motion.
+Instead of the \emph{motion} basis used in multiframe optical flow formulation of \cite{Garg:2013hu}, we build a \emph{correspondence} basis that introduces constraints on how points of different shapes are matched to each other.
+Every pixel of the reference SVS image is matched to its corresponding position at every training SVS image and in this way defines a \emph{correspondence vector}.
+This vector consists of the 2D locations of the specific point in all SVS images.
+To form this vector, the training images are arranged in an arbitrary order.
+Similarly to the order of training samples when Principal Component Analysis (PCA) is applied, this order does not affect the result of our method and any re-ordering would produce exactly the same results.
 
-% For all dense transformations $\bm{u_n}(\bm{x}), n \in \{1,...,F\}$, where $F$ is number of data and $\bm{x}$ is vector of pixels, Principle Component Analysis (PCA) is performed on trajectory to obtain low rank trajectory basis:
+Formally, let $F$ be the number of training SVS images and $n=1,\ldots,F$ be the training image index. Also, let $\boldsymbol{q}_1(n),\ldots,\boldsymbol{q}_R(n):
+\{1,\ldots,F\} \rightarrow \R^2$ be the $R$ orthonormal elements of the correspondence basis, where $\boldsymbol{q}_i(n)$ is the displacement vector that matches the points of the reference SVS image with the points of the $n$-th training SVS image, according to the variation described from the $i$-th correspondence basis element.
+Note that the basis elements $\boldsymbol{q}_i(n)$ are independent from the point location.
+Note also that the number of basis elements is typically much smaller than the full dimensionality ($2 F$) of correspondence vectors, therefore this basis plays a role of dimensionality reduction.
+
+In addition, let $\Omega \subset \R^2$ be the image domain of the SVS images and $\bx$ denote the point location. We denote the shape flow result as $\bm{u}_n(\bx):\Omega\times \{1,\ldots,F\}
+\rightarrow \R^2$,  where $\bm{u}_n(\bx)$ is the displacement vector that matches the point $\bx$ of the reference SVS image with its corresponding location at the $n$-th training SVS image.
+
+Using the constructed correspondence basis, the shape flow can be approximated as:
+\begin{equation}\label{eq:LinTrajModel}
+    \bm{u}_n(\bx) \approx
+    \sum_{i=1}^R\bm{q_i}(n)\bm{v_i}(\bx) \,\, ,
+\end{equation}
+where $\bm{v_i}(\bx)$ is the weight that needs to be applied on the $i$-th correspondence basis element, in order to get the correspondence vector for the point location $\bm{x}$.
+In other words, the shape flow for every point $\bm{x}$ is described as a linear combination of basis elements that is controlled by the coefficients $\bm{v_i}(\bm{x})$.
+The values of the $i$-th coefficient for all the points $\bm{v_i}(\bm{x})$ can be interpreted as an image defined on $\Omega$.
+Using the correspondence basis, the determination of the shape flow boils down to the determination of the set of coefficients $\bm{v_i}(\bm{x})$.
+The above representation of shape flow constrains the correspondence vectors to lie on a subspace and therefore acts as a low-rank prior that enforces coherency of the shape registration result over the whole training dataset of shapes.
+
+The next section describes the methodology of constructing the correspondence basis and estimating the shape flow robustly.
+
+% For all dense transformations $\bm{u}_n(\bm{x}), n \in \{1,...,F\}$, where $F$ is number of data and $\bm{x}$ is vector of pixels, Principle Component Analysis (PCA) is performed on trajectory to obtain low rank trajectory basis:
 % \begin{equation}
@@
 % \begin{equation}
-%     \bm{u_n}(\bm{x})=\sum_{i=1}^R\bm{q_i}(n)\bm{v_i}(x)+\bm{\varepsilon_n}(\bm{x})
+%     \bm{u}_n(\bm{x})=\sum_{i=1}^R\bm{q_i}(n)\bm{v_i}(x)+\bm{\varepsilon_n}(\bm{x})
 % \end{equation}
@@
 
-Using the SVS functions built from training data, the next step of our pipeline is to establish dense correspondences between all these functions.
-We propose to do this procedure jointly, by using the correspondence basis.
-This procedure shares similarities with multiframe optical flow and we call it Shape flow.
-We build upon robust methods for  optical flow estimation.
-Optical flow estimation typically works based on the assumptions of brightness or colour constancy and motion smoothness.
-However, in terms of shapes, neither constant illumination nor continuous motion exists in sequence of shapes as all training data are independent.
-For this reason, we propose to modify the formulation of multiframe optical flow by using the correspondence basis that we introduced in conjunction with the SVS functions, rather than actual images.
+Using the SVS functions built from training data, one of the main steps of our pipeline is to estimate dense correspondences between all these functions.
+We propose to perform this estimation simultaneously for all training data, by using the correspondence basis.
+This procedure, which we call \emph{shape flow}, builds upon robust methods for multiframe optical flow estimation \cite{Garg:2013hu}.
+However, optical flow estimation typically works based on the assumptions of brightness or colour constancy and motion smoothness, whereas in our setting the input training data correspond to shapes.
+For this reason, we propose to modify the formulation of \cite{Garg:2013hu} by using the correspondence basis that we introduced in conjunction with the SVS representation of shapes.
+
+%
+%In order to learn the such a subspace, we first transform the original annotation to point clouds.
+Then, we use NICP to align the previous point clouds with respect to a reference point cloud template.
+NICP iteratively deforms each point cloud until its points match the ones on the shape template and correspondences are established.
+However, because optical flow is a pixel-wise frame registration technique, we need to establish correspondences for all pixels on the reference frame rather than for sparse point clouds.
+To achieve this, we apply Thin Plate Spline (TPS) \cite{Bookstein1989} to find correspondences for all pixels in the reference frame given the point cloud correspondences provided by the previous NICP stage.
+Once dense correspondences have been established among all pixels, the so-called correspondence subspace is obtained by performing PCA the trajectory of all pixels.
+Note that incorporating the previous subspace as a low rank constrained in optical flow is consistent with its assumption of smooth motion.
 
 \subsubsection{Non-rigid ICP and Correspondence Basis Creation} \label{sec:trabasis}
-Since shapes from training data set having completely no motion smoothness, it is of importance to contain constraints in optimization on how pixels moves from one shape frame to another.
-We constrain the optimization on correspondence subspace.
-We supervise trajectories from sparse landmarks.
-To begin with, Non-rigid Iterative Closest Point (NICP)\cite{Amber2007} applied on sparse annotated points.
-NICP deforms target points to fit the template iteratively until all points on target deformed to match points on template.
-Performs the algorithm for all training data will get an implicit point correlation between sparse shapes.
 
-Since optical flow pixel-wise frame registration, the trajectory basis build should also match the dimension, which is dense on shapes with trajectory length depends on number of training data.
+To effectively build the correspondence basis, we first transform the original annotations to sparse point clouds.
+Then, we apply Non-rigid Iterative Closest Point (NICP)\cite{Amber2007} between the point cloud of annotations in the reference shape and the one of every shape of the training set.
+NICP iteratively deforms the cloud of points of every shape to match the points of the reference shape.
+This yields an initial estimation of the correspondence vectors on the sparse locations of annotated landmarks on the reference shape.
+To make this correspondence vectors estimation dense (i.e.~for every pixel of the reference SVS image), we apply Thin-Plate Splines (TPS)\cite{Bookstein1989} interpolation.
+Finally, the correspondence basis is found by applying PCA on the result of TPS interpolation and keeping only the first $R$ principal components.
+
+%
+%
+%Since optical flow pixel-wise frame registration, the trajectory basis build should also match the dimension, which is dense on shapes with trajectory length depends on number of training data.
 With correspondences produced after applying NICP, Thin-Plate Spline (TPS)\cite{Bookstein1989} transformations are utilized to warp every shape planes to template plane thereby generates an implicit dense shape registering.
-For all dense transformations $\bm{u_n}(\bm{x}), n \in \{1,...,F\}$, where $F$ is number of data and $\bm{x}$ is vector of pixels, Principle Component Analysis (PCA) is performed on trajectory to obtain low rank trajectory basis:
-\begin{equation}
-    \begin{bmatrix}
-        \bm{u_1}(\bm{x}) \\
-        \vdots \\
-        \bm{u_F}(\bm{x})
-    \end{bmatrix}
-    =
-    \begin{bmatrix}
-        \bm{q_1}(1) & \cdots & \bm{q_R}(1) \\
-        \vdots      & \ddots & \vdots  \\
-        \bm{q_1}(F) & \cdots & \bm{q_R}(F)
-    \end{bmatrix}
-    \times
-    \begin{bmatrix}
-        \bm{v_1}(x) \\
-        \vdots \\
-        \bm{v_R}(x)
-    \end{bmatrix}
-\end{equation}
-where $\bm{q_i}(n)$ are low rank components with $R \ll 2F$ and $\bm{v_i}(x)$ weighted each component with dependencies on $x$. Simpler expression shown below:
-\begin{equation}
-    \bm{u_n}(\bm{x})=\sum_{i=1}^R\bm{q_i}(n)\bm{v_i}(x)+\bm{\varepsilon_n}(\bm{x})
-\end{equation}
-Although optical flow on shapes made under the assumption that objects motion are smooth, the low rank constrain on trajectory basis recovered the hypothesis.
+For all dense transformations $\bm{u}_n(\bm{x}), n \in \{1,...,F\}$, where $F$ is number of data and $\bm{x}$ is vector of pixels, Principle Component Analysis (PCA) is performed on trajectory to obtain low rank trajectory basis:
+%\begin{equation}
+%    \begin{bmatrix}
+%        \bm{u_1}(\bm{x}) \\
+%        \vdots \\
+%        \bm{u_F}(\bm{x})
+%    \end{bmatrix}
+%    =
+%    \begin{bmatrix}
+%        \bm{q_1}(1) & \cdots & \bm{q_R}(1) \\
+%        \vdots      & \ddots & \vdots  \\
+%        \bm{q_1}(F) & \cdots & \bm{q_R}(F)
+%    \end{bmatrix}
+%    \times
+%    \begin{bmatrix}
+%        \bm{v_1}(x) \\
+%        \vdots \\
+%        \bm{v_R}(x)
+%    \end{bmatrix}
+%\end{equation}
+%where $\bm{q_i}(n)$ are low rank components with $R \ll 2F$ and $\bm{v_i}(x)$ weighted each component with dependencies on $x$. Simpler expression shown below:
+%\begin{equation}
+%    \bm{u}_n(\bm{x})=\sum_{i=1}^R\bm{q_i}(n)\bm{v_i}(\bm{x})+\bm{\varepsilon_n}(\bm{x})
+%\end{equation}
+%Although optical flow on shapes made under the assumption that objects motion are smooth, the low rank constrain on trajectory basis recovered the hypothesis.
 
-\subsubsection{Multi-image Subspace Flow}
-To register all decision functions to template shape, decision function $d_i(\bm{x}), i \in {1,...,F}$ are grouped into one sequence before applying flow algorithm.
+\subsubsection{Variational Shape Flow Estimation}%{Multi-image Subspace Flow}
+
+Following \cite{Garg:2013hu}, we propose to estimate the shape flow over all training SVS images $\bm{d_n}(\bx)$ by minimizing the following energy:
+\begin{align}
+E_{sf} & =\alpha
+\int_{\Omega}\sum_{n=1}^F \|\bm{d_n}(\bx+\bm{u}_n(x))-\bm{d_0}(x)\| \ud \bx \label{eq:costfunc}\\
+    &+ \beta \int_{\Omega}\sum_{n=1}^F\|\bm{u}_n(\bx)-\sum_{i=1}^R\bm{q_i}(n)\bm{v_i}(\bx)\|^2 \ud \bx \label{eq:lowrank}\\
+    &+
+\int_\Omega  \sum_{i=1}^R \,\, \left \|    \nabla \bm{v_i}(\bx)    \right \|  \,\ud \bx \label{eq:TVterm}
+\end{align}
+This energy consists of two sets of unknown shape flows that are relatively close to each other: (i) $\bm{u}_n(x)$, which tries to explain the data from the input SVS images, and (ii) the shape flow determined by the correspondence basis coefficients $\bm{v_i}(\bx)$ that are spatially regularised and enforce a low-rank prior.
+We minimize this energy jointly with respect to $\bm{u}_n(\bx)$ and $\bm{v_i}(\bx)$.
+The positive parameters $\alpha$ and $\beta$ weigh the balance between the terms of the energy.
+
+The \textbf{first term} of the above energy (term \eqref{eq:costfunc}) is a data attachment term
+that uses the robust $\Lone$-norm.
+It is based on the assumption that the values of the reference SVS image $\bm{d_0}(\bx)$ at every pixel $\bx$ are preserved at its corresponding locations on all training SVS images $\bm{d_n}(\bx)$.
+The use of an $\Lone$-norm improves the robustness of the method since it allows deviations from this assumption, which might occur in practice.
+The \textbf{second term} of the energy (term \eqref{eq:lowrank}) penalizes the difference between the two sets  of shape flows and acts as a coupling term between them.
+The \textbf{third term} of the energy (term \eqref{eq:TVterm}) corresponds to the spatial Total Variation regularization \cite{rudin92} of
+the correspondence basis coefficients $\bm{v_i}(\bx)$.
+This term penalizes spatial oscillations of each coefficient caused by distortions of the SVS images but not strong discontinuities that are desirable in the borders of different object regions.
+In addition, this term allows to fill in information into regions where the shape information in the SVS images is missing, due to e.g.~regions with no annotations.
+
+We implement the minimization of the energy $E_{sf}$ by using the optimization algorithm described in \cite{Garg:2013hu}.
+In every coarse-to-fine and warping iteration, we use an initialization that comes from the previous iteration and for the very beginning, we initialize with the shape flow result of the TPS interpolation described in Sec.~\ref{sec:trabasis}.
+We approximate the data term \eqref{eq:costfunc} by linearizing the SVS images around the initialization.
+After that, the energy becomes convex and we optimize it using an alternating optimization w.r.t.~$\bm{v_i}(\bx)$ and $\bm{u}_n(\bx)$.
+The minimization w.r.t.~
+$\bm{v_i}(\bx)$ is decoupled for every coefficient $i$ and corresponds to Rudin-Osher-Fatemi Total Variation denoising \cite{rudin92}, which we solve efficiently by applying the first order primal-dual algorithm of \cite{Chambolle:Pock:JMIV2011}.
+The minimization w.r.t.~
+$\bm{u}_n(x)$ is decoupled for every pixel $\bx$ and every shape index $i$. This minimization is also implemented by applying the efficient primal-dual algorithm of \cite{Chambolle:Pock:JMIV2011}.
+
+Figure~\ref{fig:deformationfield} demonstrates some examples of the deformation fields derived by the estimated shape flow using the aforementioned method.
+These results correspond to some of the training shapes, in the case of a face dataset.
+
+%
+%
+%To register all decision functions to template shape, decision function $d_i(\bm{x}), i \in {1,...,F}$ are grouped into one sequence before applying flow algorithm.
 The objective cost function we would like to minimise is:
-\begin{align}
-    \operatorname*{arg\,min}_{\bm{u_n}(\bm{x}), \bm{v}}&=\alpha \int_{\Omega}\sum_{n=1}^F|\bm{d_n}(x+\bm{u_n}(x))-\bm{d_0}(x)\| dx  \label{eq:costfunc}\\
-    &+ \beta \int_{\Omega}\sum_{n=1}^F\|\bm{u_n}(x)-\sum_{i=1}^R\bm{q_i}(n)\bm{v_i}(x)\|^2 dx \label{eq:lowrank}\\
-    &+ \sum[\bm{TV}(Qv)] + v^T.L.V
-\end{align}
-where $d_n(x)$ is the decision function from~\eqref{eq:decisionfunc}, which returns possibilities of given coordinate classified as shape component where coordinates are from set $\Omega \in \Re^2$.
-$TV(Qv)$ is total variation as regularization on low rank subspace, $Q$ is trajectory basis and $v^T.L.v$ is low rank spacial constraints.
-
-Term~\eqref{eq:costfunc} state the shape constancy where points having similar classification probability are from same object.
-Part~\eqref{eq:lowrank} applies constrain on low rank trajectory basis states in section~\ref{sec:trabasis}.
-The objective cost function has two free parameters $u$ and $v$, so we perform alternating minimisation.
+%\begin{align}
+%    \operatorname*{arg\,min}_{\bm{u}_n(\bm{x}), \bm{v}}&=\alpha \int_{\Omega}\sum_{n=1}^F|\bm{d_n}(x+\bm{u}_n(x))-\bm{d_0}(x)\| dx  \label{eq:costfunc}\\
+%    &+ \beta \int_{\Omega}\sum_{n=1}^F\|\bm{u}_n(x)-\sum_{i=1}^R\bm{q_i}(n)\bm{v_i}(x)\|^2 dx \label{eq:lowrank}\\
+%    &+ \sum[\bm{TV}(Qv)]
+%\end{align}
+%where $d_n(x)$ is the decision function from~\eqref{eq:decisionfunc}, which returns possibilities of given coordinate classified as shape component where coordinates are from set $\Omega \in \Re^2$.
+$TV(Qv)$ is total variation as regularization on low rank subspace, $Q$ is trajectory basis and $v^T.L.v$ is low rank spacial constrains.
+%
+%Term~\eqref{eq:costfunc} state the shape constancy where points having similar classification probability are from same object.
+%Part~\eqref{eq:lowrank} applies constrain on low rank trajectory basis states in section~\ref{sec:trabasis}.
+%The objective cost function has two free parameters $u$ and $v$, so we perform alternating minimisation.
 The equation can be solved using a thresholding scheme after linearisation of image functions.
 The minimisation can be speed up by paralleling the minimisation for every spatial-temporal point $(x;n), x \in \Omega, n \in \{1,...F\}$ independently.
-
-After solving the equation, $\bm{u_n}(\bm{x}), x \in \Omega$ gives a group of deformation fields that registering every decision functions in the shape sequence to reference frame e.g.
+%
+%
+%
+%
+%
+%
+%After solving the equation, $\bm{u}_n(\bm{x}), x \in \Omega$ gives a group of deformation fields that registering every decision functions in the shape sequence to reference frame e.g.
 $\bm{u_1}(\bm{x})$ registers decision function $\bm{d_1}(\bm{x})$ to the reference frame.

### 2015-07-17 contents/implementation.tex
reference fix

@@
 %
-%To register all decision functions to template shape, decision function $d_i(\bm{x}), i \in {1,...,F}$ are grouped into one sequence before applying flow algorithm.
+%To register all decision functions to temp`late shape, decision function $d_i(\bm{x}), i \in {1,...,F}$ are grouped into one sequence before applying flow algorithm.
 The objective cost function we would like to minimise is:

### 2015-07-17 contents/conclusion.tex
Final Rebuttal

@@
-We proposed the first, to the best of our knowledge, methodology that can build a dense deformable model "in-the-wild".
-This methodology does not require a consistent set of landmarks, avoiding the tedious task of careful manual annotations.
-We have exploited state-of-the-art multiframe optical flow methodologies to establish accurate and robust dense correspondences among shapes, when represented in a landmarks-free fashion.
-The experimental evaluations and comparisons revealed that dense AAMs that are built on top of our methodology achieve very good performance and can work effectively even in cases of objects that cannot have consistent landmarks.
+In this paper, we propose the first, to the best of our knowledge, methodology for building dense deformable models "in-the-wild".
+Our approach does not require objects to be annotated with consistent sets of landmarks and can make use of highly-efficient (in terms of required annotation time) curve line annotations, easing the tedious task of careful manual annotation.
+We have exploited state-of-the-art multiframe optical flow techniques to establish accurate and robust dense correspondences among shapes, when represented in a landmarks-free fashion via the use of the SVS representation.
+The experimental evaluation and comparison revealed that dense AAMs that are built on top of our methodology achieve good performance and can work effectively even for objects for which is difficult to define a consistent set of landmarks (e.g.
+human ears).

### 2015-07-17 contents/evaluation.tex
Final Rebuttal

@@
 The Cumulative Error Distribution (CED) for this experiment is shown in Figure \ref{fig:svs_ced} while fitting statistics are reported in Table \ref{tab:svs_stats}.
-Looking at the results it can be clearly seen that using SVS results in a constant $\approx$5\% improvement over the simple binary shape representation for almost all CED graph and on the reported fitting statistics.
+Looking at the results it can be clearly seen that using SVS results in an almost constant $\approx$10\% improvement over the simple binary shape representation for most of the CED graph and reported fitting statistics.
 
@@
 
-\subsection{Constrained Basis}
+\subsection{Correspondence Bases}
 \label{exp:basis}
+This experiment investigates the importance of applying subspace constraints to the shape flow estimation stage.
+To this end, we build and compare the performance of two different dense AAMs.
+The first one (SVS-AAMs) is built from deformation fields obtained by minimizing the variational shape flow energy proposed in section \ref{varshapeflow}, \ie constraining the shape flow with the correspondence bases described in section \ref{sec:trabasis}.
+The second dense AAM (SVS-AAMs-unconstrained) is built using deformation fields obtained by replacing the correspondence bases by identity bases so that term \ref{eq:lowrank} in the proposed variational shape flow energy becomes:
+\begin{equation}
+\beta \int_{\Omega}\sum_{n=1}^F\|\bm{u}_n(\bx)-\bm{v}_n(\bx)\|^2 \ud \bx \label{}
+\end{equation}
+with the rest of terms (\ref{eq:costfunc} and \ref{eq:TVterm}) remaining the same.
+Note that this corresponds to a degenerate case where shape flow becomes equivalent to classical frame-to-frame optical flow using TV regularization on the flow $\bm{u}_n$ \cite{Garg:2013hu}.
 
-This experiment investigate the impact of introducing subspace constrains for shape flow.
-The shape representations of training data are independence, thus simply applying flows on shapes breaks the fundamental assumption of motion smoothness.
-The hypothesis is able to be maintained for shapes as described in section~\ref{sec:trabasis}.
-To be specific, we take measures of point-to-point error for fitting same data with our pipeline with same configuration, but only alter the low rank basis.
-
-The experiment results are manifested by constructing two dense AAMs, Basis-dAAMs and no-Basis-dAAMs,among 811 training images from Labelled Faces Parts in-the-Wild (LFPW)\cite{Belhumeur2011} database with 224 testing images using same annotation scheme by iBUG\footnoteref{ibug_300}.
-Cumulative error distributions are shown in Figure~\ref{fig:basis_ced} and corresponding statistics are listed in Table~\ref{tab:basis_stats}. 
-It shows shape flow with constrained basis outperforms, constantly, standard flow technique by an unavoidable amount, which significantly supported the necessities of our low rank basis introduced in~\ref{sec:trabasis}.
+As before, both dense AAM are build using the 811 training images of LFPW database and tested on the 224 testing images of the same database.
+The cumulative error distributions graph for this experiment is shown in Figure~\ref{fig:basis_ced} and the fitting statistics reported in Table~\ref{tab:basis_stats}.
+Both Figure~\ref{fig:basis_ced} and Table~\ref{tab:basis_stats} show that the incorporation of the correspondence bases leads to considerably better performant dense AAMs.
+This large difference in performance fully justifies the incorporation of these bases to our shape flow algorithm.
 
@@
 
-In the following set of experiments we use the proposed methodology to build dense AAMs of various object classes (faces, ears, bottles and body pose) and quantitatively assess their respective fitting accuracy when fitted to novel in-the-wild images of the previous objects.
+In the following set of experiments we use the proposed methodology to build dense AAMs of 2 different object classes (faces and ears) and quantitatively assess their respective fitting accuracy when fitted to novel in-the-wild images of the previous objects.
 

### 2015-07-17 contents/implementation.tex
Final Rebuttal

@@
     \centering
-        \includegraphics[width=\textwidth]{resources/architecture}
-    \caption{Proposed pipeline.}
+        \includegraphics[width=\textwidth]{resources/architecture2}
+    \caption{Schematic description of the proposed pipeline. Figure best viewed by zooming in.}
     \label{fig:archi}
@@
 
-The proposed pipeline is depicted in Figure~\ref{fig:archi}.
-It takes as input a set of training images of a particular object class, along with (possibly inconsistent) point and/or curve line annotations.
-As a first step, the shapes that correspond to the training data are consistently represented using multichannel SVS.
+The proposed pipeline is depicted in Figure~\ref{fig:archi}. It takes as input a set of training images of a particular object class, along with inconsistent point and/or curve line shape annotations.
+As a first step, the all shape annotations are consistently represented using multichannel SVS.
 The next step is the application of ICP to achieve an initial simple alignment of the SVS images.
-The similarity-aligned SVS images are then fed into a multi-image subspace flow estimation that establishes dense correspondences between all shapes of the training set.
-In order for the flow estimation to be accurate and exploit the correlation across the different training shapes, it utilises a correspondence basis that is built on sparse correspondences given by Nonrigid ICP alignment of the annotated data.
-Finally, the dense correspondences that are yielded by the optical flow serve as automatic dense landmarks and are used to define a novel dense version of Active Appearance Models.
-The following sections discuss the different stages of the proposed pipeline in further detail.
+The multichannel similarity-aligned SVS images are then fed into a multi-image subspace flow estimation that establishes dense correspondences between all the shapes in the training set.
+In order for the flow estimation to be accurate and exploit the existent correlation among all training shapes, it utilises a correspondence bases built from sparse correspondences obtained by applying Nonrigid ICP on the annotated data.
+Finally, the dense correspondences yield by optical flow serve as automatically generated dense landmark annotations and are used to define a novel dense version of Active Appearance Models.
+The upcoming sections discuss each of the previous stages in further detail.
 
@@
 In order to fully capture the variability among most deformable object shapes annotations, we use a representation based on Support Vector Shapes (SVS) \cite{Nguyen2013}.
-An SVS is a decision function trained on shapes using Support Vector Machines (SVMs) with  Radial Basis Function (RBF) kernels.
-In this way, a shape is represented as a classifier function, which has several advantages: (a) The representation is completely general, \eg it can be applied to sparse landmark points, curves lines or a combination of the two and (b) It fuses inconsistent landmarks into consistent and directly comparable decision functions.
-Furthermore, this representations is also robust against noise, missing data and outliers.
+A SVS is a decision function trained on shapes using Support Vector Machines (SVMs) with Radial Basis Function (RBF) kernels.
+In this way, a shape is represented as a classifier function, which has several advantages: (a) the representation is completely general, \eg it can be applied to sparse landmark points, curves lines or a combination of the two and (b) it fuses inconsistent landmarks into consistent and directly comparable decision functions.
+Furthermore, this representations is also robust against noise, missing data and outliers \cite{Nguyen2013}.
 
@@
 Initially, negative points get randomly sampled around sparse landmarks while annotated landmarks are positive points.
-Since the number of positive points is far smaller that the number of negative ones, landmarks are assigned considerably larger weights so that $N_p \times W_p=N_n \times W_n$ where $N_p, N_n$ are number of positive/negative samples and $W_p, W_n$ are their corresponding weights.
+Since the number of positive points is far smaller that the number of negative ones, landmarks are assigned considerably larger weights so that $N_p \times W_p=N_n \times W_n$ where $N_p, N_n$ are the number of positive/negative samples and $W_p, W_n$ are their corresponding weights.
 
-SVMs with RBF kernel function map any numbers of data points onto an infinite-dimensional space where positive and negative points are linearly separable, hence the classification boundary on 2D space represents the actual shape of the object.
+SVMs with RBF kernel function map any number of data points onto an infinite-dimensional space where positive and negative points are linearly separable, hence the classification boundary on 2D space represents the actual shape of the object.
 Note that the decision function for SVMs can be mathematically expressed as:
 \begin{equation} \label{eq:decisionfunc}
-    d(\mathbf{x})=\sum_i\alpha_i \, k(\mathbf{x}_i^*,\mathbf{x})
+    d(\bm{x})=\sum_i\alpha_i \, k(\bm{x}_i^*,\bm{x})
 \end{equation}
-where $\mathbf{x}_i^*$ are support vectors and \mbox{$k(\mathbf{x}_i^*, \mathbf{x}) = exp(-\lambda \|\mathbf{x}_i^* -\mathbf{x}\|^2)$} is the RBF kernel .
+where $\bm{x}_i^*$ are the so-called support vectors and \mbox{$k(\bm{x}, \bm{y}) = \exp\left(-\frac{\|\bm{x} -\bm{y}\|^2}{2 \sigma^2}\right)$} is the RBF kernel .
 
@@
     \bm{u}_n(\bx) \approx
-    \sum_{i=1}^R\bm{q_i}(n)\bm{v_i}(\bx) \,\, ,
+    \sum_{i=1}^R\bm{q}_i(n)\bm{v}_i(\bx) \,\, ,
 \end{equation}
-where $\bm{v_i}(\bx)$ is the weight that needs to be applied on the $i$-th correspondence basis element, in order to get the correspondence vector for the point location $\bm{x}$.
-In other words, the shape flow for every point $\bm{x}$ is described as a linear combination of basis elements that is controlled by the coefficients $\bm{v_i}(\bm{x})$.
-The values of the $i$-th coefficient for all the points $\bm{v_i}(\bm{x})$ can be interpreted as an image defined on $\Omega$.
-Using the correspondence basis, the determination of the shape flow boils down to the determination of the set of coefficients $\bm{v_i}(\bm{x})$.
-The above representation of shape flow constrains the correspondence vectors to lie on a subspace and therefore acts as a low-rank prior that enforces coherency of the shape registration result over the whole training dataset of shapes.
+where $\bm{v}_i(\bx)$ is the weight that needs to be applied on the $i$-th correspondence basis element, in order to get the correspondence vector for the point location $\bm{x}$.
+In other words, the shape flow for every point $\bm{x}$ is described as a linear combination of basis elements that is controlled by the coefficients $\bm{v}_i(\bm{x})$.
+The values of the $i$-th coefficient for all the points $\bm{v}_i(\bm{x})$ can be interpreted as an image defined on $\Omega$.
+Using the correspondence basis, the determination of the shape flow boils down to the determination of the set of coefficients $\bm{v}_i(\bm{x})$.
+The above representation of shape flow, constrains the correspondence vectors to lie on a subspace and, therefore, acts as a low-rank prior that enforces coherency of the shape registration result over the whole training dataset of shapes.
 
@@
     \end{subfigure}
-    \caption{Deformation field built}
+    \caption{Exemplar deformation fields obtained using the proposed pipeline. Figure best viewed by zooming in.}
     \label{fig:deformationfield}
@@
 \subsubsection{Variational Shape Flow Estimation}%{Multi-image Subspace Flow}
+\label{varshapeflow}
 
-Following \cite{Garg:2013hu}, we propose to estimate the shape flow over all training SVS images $\bm{d_n}(\bx)$ by minimizing the following energy:
+Following \cite{Garg:2013hu}, we propose to estimate the shape flow over all training SVS images $\bm{d}_n(\bx)$ by minimizing the following energy:
 \begin{align}
 E_{sf} & =\alpha
-\int_{\Omega}\sum_{n=1}^F \|\bm{d_n}(\bx+\bm{u}_n(x))-\bm{d_0}(x)\| \ud \bx \label{eq:costfunc}\\
-    &+ \beta \int_{\Omega}\sum_{n=1}^F\|\bm{u}_n(\bx)-\sum_{i=1}^R\bm{q_i}(n)\bm{v_i}(\bx)\|^2 \ud \bx \label{eq:lowrank}\\
+\int_{\Omega}\sum_{n=1}^F \|\bm{d}_n(\bx+\bm{u}_n(x))-\bm{d}_0(x)\| \ud \bx \label{eq:costfunc}\\
+    &+ \beta \int_{\Omega}\sum_{n=1}^F\|\bm{u}_n(\bx)-\sum_{i=1}^R\bm{q}_i(n)\bm{v}_i(\bx)\|^2 \ud \bx \label{eq:lowrank}\\
     &+
-\int_\Omega  \sum_{i=1}^R \,\, \left \|    \nabla \bm{v_i}(\bx)    \right \|  \,\ud \bx \label{eq:TVterm}
+\int_\Omega  \sum_{i=1}^R \,\, \left \|    \nabla \bm{v}_i(\bx)    \right \|  \,\ud \bx \label{eq:TVterm}
 \end{align}
-This energy consists of two sets of unknown shape flows that are relatively close to each other: (i) $\bm{u}_n(x)$, which tries to explain the data from the input SVS images, and (ii) the shape flow determined by the correspondence basis coefficients $\bm{v_i}(\bx)$ that are spatially regularised and enforce a low-rank prior.
-We minimize this energy jointly with respect to $\bm{u}_n(\bx)$ and $\bm{v_i}(\bx)$.
+This energy consists of two sets of unknown shape flows that are relatively close to each other: (i) $\bm{u}_n(x)$ which tries to explain the data from the input SVS images, and (ii) the shape flow determined by the correspondence basis coefficients $\bm{v}_i(\bx)$ that are spatially regularised and enforce a low-rank prior.
+We minimize this energy jointly with respect to $\bm{u}_n(\bx)$ and $\bm{v}_i(\bx)$.
 The positive parameters $\alpha$ and $\beta$ weigh the balance between the terms of the energy.
 
-The \textbf{first term} of the above energy (term \eqref{eq:costfunc}) is a data attachment term
+The \textbf{first term} of the above energy \eqref{eq:costfunc} is a data attachment term
 that uses the robust $\Lone$-norm.
-It is based on the assumption that the values of the reference SVS image $\bm{d_0}(\bx)$ at every pixel $\bx$ are preserved at its corresponding locations on all training SVS images $\bm{d_n}(\bx)$.
+It is based on the assumption that the values of the reference SVS image $\bm{d}_0(\bx)$ at every pixel $\bx$ are preserved at its corresponding locations on all training SVS images $\bm{d}_n(\bx)$.
 The use of an $\Lone$-norm improves the robustness of the method since it allows deviations from this assumption, which might occur in practice.
-The \textbf{second term} of the energy (term \eqref{eq:lowrank}) penalizes the difference between the two sets  of shape flows and acts as a coupling term between them.
-The \textbf{third term} of the energy (term \eqref{eq:TVterm}) corresponds to the spatial Total Variation regularization \cite{rudin92} of
-the correspondence basis coefficients $\bm{v_i}(\bx)$.
+The \textbf{second term} of the energy \eqref{eq:lowrank} penalizes the difference between the two sets  of shape flows and acts as a coupling term between them.
+The \textbf{third term} of the energy \eqref{eq:TVterm} corresponds to the spatial Total Variation regularization \cite{rudin92} of
+the correspondence basis coefficients $\bm{v}_i(\bx)$.
 This term penalizes spatial oscillations of each coefficient caused by distortions of the SVS images but not strong discontinuities that are desirable in the borders of different object regions.
@@
 We approximate the data term \eqref{eq:costfunc} by linearizing the SVS images around the initialization.
-After that, the energy becomes convex and we optimize it using an alternating optimization w.r.t.~$\bm{v_i}(\bx)$ and $\bm{u}_n(\bx)$.
+After that, the energy becomes convex and we optimize it using alternating optimization w.r.t.~$\bm{v}_i(\bx)$ and $\bm{u}_n(\bx)$.
 The minimization w.r.t.~
-$\bm{v_i}(\bx)$ is decoupled for every coefficient $i$ and corresponds to Rudin-Osher-Fatemi Total Variation denoising \cite{rudin92}, which we solve efficiently by applying the first order primal-dual algorithm of \cite{Chambolle:Pock:JMIV2011}.
+$\bm{v}_i(\bx)$ is decoupled for every coefficient $i$ and corresponds to Rudin-Osher-Fatemi Total Variation denoising \cite{rudin92}, which we solve efficiently by applying the first order primal-dual algorithm of \cite{Chambolle:Pock:JMIV2011}.
 The minimization w.r.t.~
@@
 
-Figure~\ref{fig:deformationfield} demonstrates some examples of the deformation fields derived by the estimated shape flow using the aforementioned method.
-These results correspond to some of the training shapes, in the case of a face dataset.
+Figure~\ref{fig:deformationfield} shows some examples of deformation fields derived from the estimated shape flow computed by the aforementioned method.
+These results correspond to exemplar training shapes in the case of a face dataset.
 
@@
 
-Applying PCA on deformations trains dense deformable shape model:
-\begin{equation*}
-    \bm{s_p}=\bm{\bar{s}} + \bm{U}_s\bm{p}
-\end{equation*}
-where $\bm{s_p}$ is deformed shape instance.
+% Applying PCA on deformations trains dense deformable shape model:
+% \begin{equation*}
+%     \bm{s_p}=\bm{\bar{s}} + \bm{U}_s\bm{p}
+% \end{equation*}
+% where $\bm{s_p}$ is deformed shape instance.
 $\bm{\bar{s}}$ is mean shape and $\bm{U}_s\bm{p}$ are eigenvectors with corresponding parameters $p$.
 Figure~\ref{fig:models} shows an instance of deformed shape and appearance model.
-\begin{figure}[h!]
-    \centering
-    \begin{subfigure}[b]{0.22\textwidth}
-            \includegraphics[width=\textwidth]{resources/Fig_dAAM/of_shape}
-    \end{subfigure}
-  	\hfill
-    \begin{subfigure}[b]{0.22\textwidth}
-            \includegraphics[width=\textwidth]{resources/Fig_dAAM/of_app}
-    \end{subfigure}
-    \caption{Dense Deformable Model}
-    \label{fig:models}
-\end{figure}
+% \begin{figure}[h!]
+%     \centering
+%     \begin{subfigure}[b]{0.22\textwidth}
+%             \includegraphics[width=\textwidth]{resources/Fig_dAAM/of_shape}
+%     \end{subfigure}
+%   	\hfill
+%     \begin{subfigure}[b]{0.22\textwidth}
+%             \includegraphics[width=\textwidth]{resources/Fig_dAAM/of_app}
+%     \end{subfigure}
+%     \caption{Dense Deformable Model}
+%     \label{fig:models}
+% \end{figure}
 
@@
 
-The deformation fields obtained in section \ref{sec:shapeflow} can be effectively used to learn a naturally dense version of Active Appearance Models \cite{Cootes2001, Matthews2004}.
-Because all deformation fields contain the same number of pixels (the same as on the reference frame) the spatial positions $\mathbf{x}_i=(x_i, y_i)$ of these pixels can be treated as point landmarks and the deformation field themselves as dense annotations of the object's shape.
+The deformation fields obtained from section \ref{sec:shapeflow} can be effectively used to learn a naturally dense version of Active Appearance Models \cite{Cootes2001, Matthews2004}.
+Because all deformation fields contain the same number of pixels (the same as on the reference frame) the spatial positions $\bm{x}_i=(x_i, y_i)$ of these pixels can be treated as point landmarks and the deformation field themselves as dense annotations of the object's shape.
 Consequently, building a dense shape model reduces to normalizing these dense annotations with respect to a global similarity transform (typically using Procrustes Analysis) and applying Principal Component Analysis (PCA).
@@
     \begin{aligned}
-        \mathbf{s} & = \mathbf{\bar{s}} + \mathbf{S} \mathbf{p}
+        \bm{s} & = \bm{\bar{s}} + \bm{S} \bm{p}
     \end{aligned}
@@
 \end{equation}
-where $\mathbf{\bar{s}}$ is mean shape and $\mathbf{S}$ and $\mathbf{p}$ are the shape bases and parameters respectively.
+where $\bm{\bar{s}}$ is mean shape and $\bm{S}$ and $\bm{p}$ are the shape bases and shape parameters respectively.
 
@@
     \begin{aligned}
-        \mathbf{a} = \mathbf{\bar{a}} + \mathbf{A} \mathbf{c}
+        \bm{t} = \bm{\bar{t}} + \bm{T} \bm{c}
     \end{aligned}
@@
 \end{equation}
-where $\mathbf{a}$ is the mean texture, and $\mathbf{A}$ and $\mathbf{c}$ are the texture bases and parameters respectively.
+where $\bm{t}$ is the mean texture, and $\bm{T}$ and $\bm{c}$ are the texture bases and texture parameters respectively.
 
@@
 frame.
-Therefore, in clear contrast to classic AAMs formulations \cite{Cootes2001, Matthews2004}, no motion model (piece-wise affine, thin-plates splines \cite{Bookstein1989}) is required to relate the previous shape and texture models in our dense formulation.
+Therefore, in clear contrast to classic AAMs formulations \cite{Cootes2001, Matthews2004}, in our dense formulation no motion model (piece-wise affine, thin-plates splines \cite{Bookstein1989}) is required to relate the previous shape and texture models .
 As noted by other authors \cite{Amberg2009, Tzimiropoulos2014}, this has the advantage that all efficient compositional gradient descent algorithms for fitting AAMs \cite{Papandreou2008, Matthews2004, Amberg2009, Tzimiropoulos2013, Alabort2014} become exact under our formulation.

### 2015-07-17 contents/introduction.tex
Updates from ShareLaTeX
Final Rebuttal

@@
 Hence, a second pass on the annotated data is, in many cases, necessary.
-Due to the fact that manual annotation is a costly and labour-intensive procedure, unsupervised learning of deformable models for the tasks of object alignment has recently attracted some attention \cite{kokkinos2007unsupervised, jojic2006escaping, jiang2009learning, liu2009simultaneous, baker2004automatic, cox2008least, cootes2004groupwise, frey2003learning}.
-Nevertheless, the method of \cite{antonakos2014automatic} requires a consistent set of shapes annotated with landmarks to perform deformable face congealing.
-Finally, because the problem of fully unsupervised discovery of the deformations of arbitrary objects is difficult and ill-posed the limited number of methods that have been applied for the task cannot be applied for arbitrary collection of images collected "in-the-wild".
+Due to the fact that manual annotation is a costly and labour-intensive procedure, unsupervised learning of deformable models for the tasks of object alignment has recently attracted some attention \cite{frey2003learning, baker2004automatic, cootes2004groupwise, jojic2006escaping, Huang2006, kokkinos2007unsupervised, cox2008least, jiang2009learning, liu2009simultaneous, Zhang2012}.
+However, because the problem of fully unsupervised discovery of the deformations of arbitrary objects is difficult and ill-posed the limited number of methods that have been applied to the task cannot be directly applied to arbitrary collection of images collected "in-the-wild".
+On the other hand, the method of \cite{antonakos2014automatic}, which can deal with "in-the-wild" images, requires a set of consistently annotated sparse shapes to perform deformable face congealing.
 
 In this paper, we provide a solution for annotating an object with regards to its deformations that requires considerable less effort and in the same time can be used to define statistical deformations for objects without consistent set of landmarks.
-That is, we argue that it is better to annotate an object with regards to a set of continues lines that describe the shape of the object.
+That is, we argue that it is better to annotate an object with regards to a set of continuous lines that describe the shape of the object.
 An example is provided in Figure \ref{fig:intro} where the shape of the facial parts is annotated with continuous lines instead of a number of discrete landmarks.

### 2015-07-17 contents/evaluation.tex
layout fix

@@
 \centering
-\includegraphics[width=0.42\textwidth]{resources/Fig_SVS/svs_ced}
+\includegraphics[width=0.38\textwidth]{resources/Fig_SVS/svs_ced}
 \caption{CED over 68 landmarks on the LFPW database for experiment \ref{exp:svs}}
@@
 \centering
-\includegraphics[width=0.42\textwidth]{resources/basis_ced}
+\includegraphics[width=0.38\textwidth]{resources/basis_ced}
 \caption{CED over 68 landmarks on the LFPW database for experiment \ref{exp:basis}}
@@
 \centering
-\includegraphics[width=0.42\textwidth]{resources/Fig_Alignment/face_ced}
+\includegraphics[width=0.38\textwidth]{resources/Fig_Alignment/face_ced}
 \caption{CED over 68 landmarks on the LFPW database for experiment \ref{exp:face}}
@@
 \centering
-\includegraphics[width=0.42\textwidth]{resources/Fig_Alignment/ear_ced}
+\includegraphics[width=0.38\textwidth]{resources/Fig_Alignment/ear_ced}
 \caption{CED over 55 landmarks on the collected ear database for experiment \ref{exp:ear}}

### 2015-07-17 contents/introduction.tex
layout fix

@@
     \hfill
-    \begin{subfigure}[b]{0.075\textwidth}
+    \begin{subfigure}[b]{0.07\textwidth}
             \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_1_3}
@@
     \hfill
-    \begin{subfigure}[b]{0.075\textwidth}
+    \begin{subfigure}[b]{0.07\textwidth}
             \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_1_4}
@@
    	\hfill
-    \begin{subfigure}[b]{0.075\textwidth}
+    \begin{subfigure}[b]{0.07\textwidth}
             \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_1_5}
@@
     \\
-    \begin{subfigure}[b]{0.07\textwidth}
+    \begin{subfigure}[b]{0.06\textwidth}
             \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_2_0}
@@
     \hfill
-    \begin{subfigure}[b]{0.07\textwidth}
+    \begin{subfigure}[b]{0.06\textwidth}
             \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_2_1}
@@
    	\hfill
-    \begin{subfigure}[b]{0.07\textwidth}
+    \begin{subfigure}[b]{0.06\textwidth}
             \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_2_2}
@@
     \hfill
-    \begin{subfigure}[b]{0.07\textwidth}
+    \begin{subfigure}[b]{0.06\textwidth}
             \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_2_3}
@@
     \hfill
-    \begin{subfigure}[b]{0.07\textwidth}
+    \begin{subfigure}[b]{0.06\textwidth}
             \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_2_4}
@@
    	\hfill
-    \begin{subfigure}[b]{0.07\textwidth}
+    \begin{subfigure}[b]{0.06\textwidth}
             \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_2_5}
@@
 Hence, a second pass on the annotated data is, in many cases, necessary.
-Due to the fact that manual annotation is a costly and labour-intensive procedure, unsupervised learning of deformable models for the tasks of object alignment has recently attracted some attention \cite{frey2003learning, baker2004automatic, cootes2004groupwise, jojic2006escaping, Huang2006, kokkinos2007unsupervised, cox2008least, jiang2009learning, liu2009simultaneous, Zhang2012}.
+Due to the fact that manual annotation is a costly and labour-intensive procedure, unsupervised learning of deformable models for the tasks of object alignment has recently attracted some attention \cite{frey2003learning, baker2004automatic, cootes2004groupwise, jojic2006escaping, Huang2006, kokkinos2007unsupervised, jiang2009learning, liu2009simultaneous, Zhang2012}.
 However, because the problem of fully unsupervised discovery of the deformations of arbitrary objects is difficult and ill-posed the limited number of methods that have been applied to the task cannot be directly applied to arbitrary collection of images collected "in-the-wild".

### 2015-07-17 contents/evaluation.tex
Changes for Rebuttal Highlighted

@@
 The Cumulative Error Distribution (CED) for this experiment is shown in Figure \ref{fig:svs_ced} while fitting statistics are reported in Table \ref{tab:svs_stats}.
-Looking at the results it can be clearly seen that using SVS results in an almost constant $\approx$10\% improvement over the simple binary shape representation for most of the CED graph and reported fitting statistics.
+\textcolor{red}{Looking at the results it can be clearly seen that using SVS results in an almost constant $\approx$10\% improvement over the simple binary shape representation for most of the CED graph and reported fitting statistics.}
 
@@
 
-\subsection{Correspondence Bases}
+\subsection{\textcolor{red}{Correspondence Bases}}
 \label{exp:basis}
+\textcolor{red}{
 This experiment investigates the importance of applying subspace constraints to the shape flow estimation stage.
@@
 with the rest of terms (\ref{eq:costfunc} and \ref{eq:TVterm}) remaining the same.
-Note that this corresponds to a degenerate case where shape flow becomes equivalent to classical frame-to-frame optical flow using TV regularization on the flow $\bm{u}_n$ \cite{Garg:2013hu}.
+Note that this corresponds to a degenerate case where shape flow becomes equivalent to classical frame-to-frame optical flow using TV regularization on the flow $\bm{u}_n$ \cite{Garg:2013hu}.}
 
-As before, both dense AAM are build using the 811 training images of LFPW database and tested on the 224 testing images of the same database.
+\textcolor{red}{As before, both dense AAM are build using the 811 training images of LFPW database and tested on the 224 testing images of the same database.
 The cumulative error distributions graph for this experiment is shown in Figure~\ref{fig:basis_ced} and the fitting statistics reported in Table~\ref{tab:basis_stats}.
 Both Figure~\ref{fig:basis_ced} and Table~\ref{tab:basis_stats} show that the incorporation of the correspondence bases leads to considerably better performant dense AAMs.
-This large difference in performance fully justifies the incorporation of these bases to our shape flow algorithm.
+This large difference in performance fully justifies the incorporation of these bases to our shape flow algorithm.}
 
@@
 
-In the following set of experiments we use the proposed methodology to build dense AAMs of 2 different object classes (faces and ears) and quantitatively assess their respective fitting accuracy when fitted to novel in-the-wild images of the previous objects.
+\textcolor{red}{In the following set of experiments we use the proposed methodology to build dense AAMs of 2 different object classes (faces and ears) and quantitatively assess their respective fitting accuracy when fitted to novel in-the-wild images of the previous objects.}
 

### 2015-07-17 contents/implementation.tex
layout fix
Fix eq 6, 7
Changes for Rebuttal Highlighted

@@
     \centering
-        \includegraphics[width=\textwidth]{resources/architecture2}
-    \caption{Schematic description of the proposed pipeline. Figure best viewed by zooming in.}
+        \includegraphics[width=\textwidth]{resources/architecture3}
+    \caption{\textcolor{red}{Schematic description of the proposed pipeline. Figure best viewed by zooming in.}}
     \label{fig:archi}
@@
 
-The proposed pipeline is depicted in Figure~\ref{fig:archi}. It takes as input a set of training images of a particular object class, along with inconsistent point and/or curve line shape annotations.
+\textcolor{red}{The proposed pipeline is depicted in Figure~\ref{fig:archi}.
+It takes as input a set of training images of a particular object class, along with inconsistent point and/or curve line shape annotations.
 As a first step, the all shape annotations are consistently represented using multichannel SVS.
@@
 Finally, the dense correspondences yield by optical flow serve as automatically generated dense landmark annotations and are used to define a novel dense version of Active Appearance Models.
-The upcoming sections discuss each of the previous stages in further detail.
+The upcoming sections discuss each of the previous stages in further detail.}
 
@@
 In this way, a shape is represented as a classifier function, which has several advantages: (a) the representation is completely general, \eg it can be applied to sparse landmark points, curves lines or a combination of the two and (b) it fuses inconsistent landmarks into consistent and directly comparable decision functions.
-Furthermore, this representations is also robust against noise, missing data and outliers \cite{Nguyen2013}.
+\textcolor{red}{Furthermore, this representations is also robust against noise, missing data and outliers \cite{Nguyen2013}.}
 
@@
 
-SVMs with RBF kernel function map any number of data points onto an infinite-dimensional space where positive and negative points are linearly separable, hence the classification boundary on 2D space represents the actual shape of the object.
+\textcolor{red}{SVMs with RBF kernel function map any number of data points onto an infinite-dimensional space where positive and negative points are linearly separable, hence the classification boundary on 2D space represents the actual shape of the object.
 Note that the decision function for SVMs can be mathematically expressed as:
@@
 \end{equation}
-where $\bm{x}_i^*$ are the so-called support vectors and \mbox{$k(\bm{x}, \bm{y}) = \exp\left(-\frac{\|\bm{x} -\bm{y}\|^2}{2 \sigma^2}\right)$} is the RBF kernel .
+where $\bm{x}_i^*$ are the so-called support vectors and \mbox{$k(\bm{x}, \bm{y}) = \exp\left(-\frac{\|\bm{x} -\bm{y}\|^2}{2 \sigma^2}\right)$} is the RBF kernel .}
 
@@
 
+% \begin{figure}[b!]
+%     \centering
+%     \begin{subfigure}[b]{0.2\textwidth}
+%             \includegraphics[width=\textwidth]{resources/landmark}
+%         \caption{Spare landmarks}
+%     \end{subfigure}
+%     \qquad
+%     \begin{subfigure}[b]{0.2\textwidth}
+%             \includegraphics[width=\textwidth]{resources/svs}
+%         \caption{Decision function}
+%         \label{fig:svs}
+%     \end{subfigure}
+%     \caption{Exemplar SVS shape representation.
+The decision function is trained on the set of sparse landmarks.
+In (b), brighter colour represents higher probability of a pixels belonging to the original shape.}
+%     \label{fig:build_svs}
+% \end{figure}
+
 \begin{figure}[b!]
     \centering
-    \begin{subfigure}[b]{0.2\textwidth}
-            \includegraphics[width=\textwidth]{resources/landmark}
-        \caption{Spare landmarks}
-    \end{subfigure}
-    \qquad
-    \begin{subfigure}[b]{0.2\textwidth}
-            \includegraphics[width=\textwidth]{resources/svs}
-        \caption{Decision function}
-        \label{fig:svs}
-    \end{subfigure}
-    \caption{Exemplar SVS shape representation.
-The decision function is trained on the set of sparse landmarks.
-In (b), brighter colour represents higher probability of a pixels belonging to the original shape.}
+    \includegraphics[width=0.4\textwidth]{resources/svs2}
+    \caption{\textcolor{red}{Exemplar SVS shape representation. A similar SVS image is obtained from different annotations of the same shape.}}
     \label{fig:build_svs}
@@
 
-We consider the problem of dense correspondences across SVS images as a joint estimation of optical flow fields between a reference SVS image and every SVS image of the training dataset.
+\textcolor{red}{We consider the problem of dense correspondences across SVS images as a joint estimation of optical flow fields between a reference SVS image and every SVS image of the training dataset.
 The estimation of such a ``shape flow'' defines for every training SVS image a warping function that registers it with the reference SVS image.
-To establish the dense correspondences robustly, we are inspired by the idea of subspace constraints in the estimation of multiframe optical flow \cite{Garg:2013hu}.
+To establish the dense correspondences robustly, we are inspired by the idea of subspace constraints in the estimation of multiframe optical flow \cite{Garg:2013hu}.}
 
-Instead of the \emph{motion} basis used in multiframe optical flow formulation of \cite{Garg:2013hu}, we build a \emph{correspondence} basis that introduces constraints on how points of different shapes are matched to each other.
+\textcolor{red}{Instead of the \emph{motion} basis used in multiframe optical flow formulation of \cite{Garg:2013hu}, we build a \emph{correspondence} basis that introduces constraints on how points of different shapes are matched to each other.
 Every pixel of the reference SVS image is matched to its corresponding position at every training SVS image and in this way defines a \emph{correspondence vector}.
@@
 To form this vector, the training images are arranged in an arbitrary order.
-Similarly to the order of training samples when Principal Component Analysis (PCA) is applied, this order does not affect the result of our method and any re-ordering would produce exactly the same results.
+Similarly to the order of training samples when Principal Component Analysis (PCA) is applied, this order does not affect the result of our method and any re-ordering would produce exactly the same results.}
 
-Formally, let $F$ be the number of training SVS images and $n=1,\ldots,F$ be the training image index. Also, let $\boldsymbol{q}_1(n),\ldots,\boldsymbol{q}_R(n):
+\textcolor{red}{Formally, let $F$ be the number of training SVS images and $n=1,\ldots,F$ be the training image index. Also, let $\boldsymbol{q}_1(n),\ldots,\boldsymbol{q}_R(n):
 \{1,\ldots,F\} \rightarrow \R^2$ be the $R$ orthonormal elements of the correspondence basis, where $\boldsymbol{q}_i(n)$ is the displacement vector that matches the points of the reference SVS image with the points of the $n$-th training SVS image, according to the variation described from the $i$-th correspondence basis element.
 Note that the basis elements $\boldsymbol{q}_i(n)$ are independent from the point location.
-Note also that the number of basis elements is typically much smaller than the full dimensionality ($2 F$) of correspondence vectors, therefore this basis plays a role of dimensionality reduction.
+Note also that the number of basis elements is typically much smaller than the full dimensionality ($2 F$) of correspondence vectors, therefore this basis plays a role of dimensionality reduction.}
 
-In addition, let $\Omega \subset \R^2$ be the image domain of the SVS images and $\bx$ denote the point location. We denote the shape flow result as $\bm{u}_n(\bx):\Omega\times \{1,\ldots,F\}
-\rightarrow \R^2$,  where $\bm{u}_n(\bx)$ is the displacement vector that matches the point $\bx$ of the reference SVS image with its corresponding location at the $n$-th training SVS image.
+\textcolor{red}{In addition, let $\Omega \subset \R^2$ be the image domain of the SVS images and $\bx$ denote the point location.
+We denote the shape flow result as $\bm{u}_n(\bx):\Omega\times \{1,\ldots,F\}
+\rightarrow \R^2$,  where $\bm{u}_n(\bx)$ is the displacement vector that matches the point $\bx$ of the reference SVS image with its corresponding location at the $n$-th training SVS image.}
 
-Using the constructed correspondence basis, the shape flow can be approximated as:
+\textcolor{red}{Using the constructed correspondence basis, the shape flow can be approximated as:
 \begin{equation}\label{eq:LinTrajModel}
@@
 Using the correspondence basis, the determination of the shape flow boils down to the determination of the set of coefficients $\bm{v}_i(\bm{x})$.
-The above representation of shape flow, constrains the correspondence vectors to lie on a subspace and, therefore, acts as a low-rank prior that enforces coherency of the shape registration result over the whole training dataset of shapes.
+The above representation of shape flow, constrains the correspondence vectors to lie on a subspace and, therefore, acts as a low-rank prior that enforces coherency of the shape registration result over the whole training dataset of shapes.}
 
@@
     \centering
-    \begin{subfigure}[b]{0.15\textwidth}
+    \begin{subfigure}[b]{0.1\textwidth}
             \includegraphics[width=\textwidth]{resources/Fig_Flows/0}
@@
     \hfill
-    \begin{subfigure}[b]{0.15\textwidth}
+    \begin{subfigure}[b]{0.1\textwidth}
             \includegraphics[width=\textwidth]{resources/Fig_Flows/1}
@@
    	\hfill
-    \begin{subfigure}[b]{0.15\textwidth}
+    \begin{subfigure}[b]{0.1\textwidth}
             \includegraphics[width=\textwidth]{resources/Fig_Flows/2}
@@
     \\
-    \begin{subfigure}[b]{0.15\textwidth}
+    \begin{subfigure}[b]{0.1\textwidth}
             \includegraphics[width=\textwidth]{resources/Fig_Flows/3}
@@
     \hfill
-    \begin{subfigure}[b]{0.15\textwidth}
+    \begin{subfigure}[b]{0.1\textwidth}
             \includegraphics[width=\textwidth]{resources/Fig_Flows/4}
@@
    	\hfill
-    \begin{subfigure}[b]{0.15\textwidth}
+    \begin{subfigure}[b]{0.1\textwidth}
             \includegraphics[width=\textwidth]{resources/Fig_Flows/5}
@@
     \\
-    \begin{subfigure}[b]{0.15\textwidth}
+    \begin{subfigure}[b]{0.1\textwidth}
             \includegraphics[width=\textwidth]{resources/Fig_Flows/6}
@@
     \hfill
-    \begin{subfigure}[b]{0.15\textwidth}
+    \begin{subfigure}[b]{0.1\textwidth}
             \includegraphics[width=\textwidth]{resources/Fig_Flows/7}
@@
    	\hfill
-    \begin{subfigure}[b]{0.15\textwidth}
+    \begin{subfigure}[b]{0.1\textwidth}
             \includegraphics[width=\textwidth]{resources/Fig_Flows/8}
     \end{subfigure}
-    \caption{Exemplar deformation fields obtained using the proposed pipeline. Figure best viewed by zooming in.}
+    \caption{\textcolor{red}{Exemplar deformation fields obtained using the proposed pipeline. Figure best viewed by zooming in.}}
     \label{fig:deformationfield}
@@
 
-Using the SVS functions built from training data, one of the main steps of our pipeline is to estimate dense correspondences between all these functions.
+\textcolor{red}{Using the SVS functions built from training data, one of the main steps of our pipeline is to estimate dense correspondences between all these functions.
 We propose to perform this estimation simultaneously for all training data, by using the correspondence basis.
@@
 However, optical flow estimation typically works based on the assumptions of brightness or colour constancy and motion smoothness, whereas in our setting the input training data correspond to shapes.
-For this reason, we propose to modify the formulation of \cite{Garg:2013hu} by using the correspondence basis that we introduced in conjunction with the SVS representation of shapes.
+For this reason, we propose to modify the formulation of \cite{Garg:2013hu} by using the correspondence basis that we introduced in conjunction with the SVS representation of shapes.}
 
@@
 
-To effectively build the correspondence basis, we first transform the original annotations to sparse point clouds.
+\textcolor{red}{To effectively build the correspondence basis, we first transform the original annotations to sparse point clouds.
 Then, we apply Non-rigid Iterative Closest Point (NICP)\cite{Amber2007} between the point cloud of annotations in the reference shape and the one of every shape of the training set.
@@
 To make this correspondence vectors estimation dense (i.e.~for every pixel of the reference SVS image), we apply Thin-Plate Splines (TPS)\cite{Bookstein1989} interpolation.
-Finally, the correspondence basis is found by applying PCA on the result of TPS interpolation and keeping only the first $R$ principal components.
+Finally, the correspondence basis is found by applying PCA on the result of TPS interpolation and keeping only the first $R$ principal components.}
 
@@
 
-Following \cite{Garg:2013hu}, we propose to estimate the shape flow over all training SVS images $\bm{d}_n(\bx)$ by minimizing the following energy:
+\textcolor{red}{Following \cite{Garg:2013hu}, we propose to estimate the shape flow over all training SVS images $\bm{d}_n(\bx)$ by minimizing the following energy:
 \begin{align}
@@
 We minimize this energy jointly with respect to $\bm{u}_n(\bx)$ and $\bm{v}_i(\bx)$.
-The positive parameters $\alpha$ and $\beta$ weigh the balance between the terms of the energy.
+The positive parameters $\alpha$ and $\beta$ weigh the balance between the terms of the energy.}
 
-The \textbf{first term} of the above energy \eqref{eq:costfunc} is a data attachment term
+\textcolor{red}{The \textbf{first term} of the above energy \eqref{eq:costfunc} is a data attachment term
 that uses the robust $\Lone$-norm.
@@
 This term penalizes spatial oscillations of each coefficient caused by distortions of the SVS images but not strong discontinuities that are desirable in the borders of different object regions.
-In addition, this term allows to fill in information into regions where the shape information in the SVS images is missing, due to e.g.~regions with no annotations.
+In addition, this term allows to fill in information into regions where the shape information in the SVS images is missing, due to e.g.~regions with no annotations.}
 
-We implement the minimization of the energy $E_{sf}$ by using the optimization algorithm described in \cite{Garg:2013hu}.
+\textcolor{red}{We implement the minimization of the energy $E_{sf}$ by using the optimization algorithm described in \cite{Garg:2013hu}.
 In every coarse-to-fine and warping iteration, we use an initialization that comes from the previous iteration and for the very beginning, we initialize with the shape flow result of the TPS interpolation described in Sec.~\ref{sec:trabasis}.
@@
 The minimization w.r.t.~
-$\bm{u}_n(x)$ is decoupled for every pixel $\bx$ and every shape index $i$. This minimization is also implemented by applying the efficient primal-dual algorithm of \cite{Chambolle:Pock:JMIV2011}.
+$\bm{u}_n(x)$ is decoupled for every pixel $\bx$ and every shape index $i$. This minimization is also implemented by applying the efficient primal-dual algorithm of \cite{Chambolle:Pock:JMIV2011}.}
 
-Figure~\ref{fig:deformationfield} shows some examples of deformation fields derived from the estimated shape flow computed by the aforementioned method.
-These results correspond to exemplar training shapes in the case of a face dataset.
+\textcolor{red}{Figure~\ref{fig:deformationfield} shows some examples of deformation fields derived from the estimated shape flow computed by the aforementioned method.
+These results correspond to exemplar training shapes in the case of a face dataset.}
 
@@
 frame.
-Therefore, in clear contrast to classic AAMs formulations \cite{Cootes2001, Matthews2004}, in our dense formulation no motion model (piece-wise affine, thin-plates splines \cite{Bookstein1989}) is required to relate the previous shape and texture models .
-As noted by other authors \cite{Amberg2009, Tzimiropoulos2014}, this has the advantage that all efficient compositional gradient descent algorithms for fitting AAMs \cite{Papandreou2008, Matthews2004, Amberg2009, Tzimiropoulos2013, Alabort2014} become exact under our formulation.
+\textcolor{red}{Therefore, in clear contrast to classic AAMs formulations \cite{Cootes2001, Matthews2004}, in our dense formulation no motion model (piece-wise affine, thin-plates splines \cite{Bookstein1989}) is required to relate the previous shape and texture models .
+As noted by other authors \cite{Amberg2009, Tzimiropoulos2014}, this has the advantage that all efficient compositional gradient descent algorithms for fitting AAMs \cite{Papandreou2008, Matthews2004, Amberg2009, Tzimiropoulos2013, Alabort2014} become exact under our formulation.}
 

### 2015-07-17 contents/introduction.tex
Changes for Rebuttal Highlighted

@@
 Furthermore,  training and fatigue largely influence the annotation accuracy.
-Hence, a second pass on the annotated data is, in many cases, necessary.
-Due to the fact that manual annotation is a costly and labour-intensive procedure, unsupervised learning of deformable models for the tasks of object alignment has recently attracted some attention \cite{frey2003learning, baker2004automatic, cootes2004groupwise, jojic2006escaping, Huang2006, kokkinos2007unsupervised, jiang2009learning, liu2009simultaneous, Zhang2012}.
+\textcolor{red}{Hence, a second pass on the annotated data is, in many cases, necessary.
+Due to the fact that manual annotation is a costly and labour-intensive procedure, unsupervised learning of deformable models for the tasks of object alignment has recently attracted some attention \cite{frey2003learning, baker2004automatic, cootes2004groupwise, jojic2006escaping, Huang2006, kokkinos2007unsupervised, jiang2009learning, liu2009simultaneous, Zhang2012}}.
 However, because the problem of fully unsupervised discovery of the deformations of arbitrary objects is difficult and ill-posed the limited number of methods that have been applied to the task cannot be directly applied to arbitrary collection of images collected "in-the-wild".
